### 2014-07-14 paper.tex
Initial paper and Some draft outline

\documentclass[conference]{IEEEtran}
\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfigure,paralist,graphicx}
%\usepackage{flushend}

\usepackage[font=small,labelfont=bf]{caption}

\usepackage{xspace}
\usepackage{color}
\usepackage{ifthen}
\usepackage{url}
\usepackage{fancybox}

\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Title}

\maketitle
\newboolean{showcomments}
\setboolean{showcomments}{true} % toggle to show or hide comments
\ifthenelse{\boolean{showcomments}}
{\newcommand{\nbnote}[2]{
  % \fbox{\bfseries\sffamily\scriptsize#1}
  \fcolorbox{blue}{yellow}{\bfseries\sffamily\scriptsize#1}
  {\sf\small\textit{#2}}
  % \marginpar{\fbox{\bfseries\sffamily#1}}
 }
}
{\newcommand{\nbnote}[2]{}
 \newcommand{\version}{}
}
\newcommand\pick[1]{\nbnote{Pick}{\textcolor{magenta}{#1}}}
\newcommand\thai[1]{\nbnote{Yoshida}{\textcolor{blue}{#1}}}

\begin{abstract}

\begin{IEEEkeywords}
Peer Code Review, Software Inspection, Reviewer Recommendation, Reviewer Assignment
\end{IEEEkeywords}
\end{abstract}

\section{Introduction}
Motivation Example.
\begin{description}
\item[RQ1:] Can we identify useful and useless discussions in code review?
\item[RQ2:] How impact of useless discussion impact to the software quality?
\end{description}
\section{Background}
\subsection{Modern Code Review}
\subsection{Text Mining Techniques}
\subsubsection{TF-IDF}
\subsubsection{Euclidian Distance}
\subsection{Evaluation Techniques}
\subsubsection{Precision and Recall}
\subsubsection{F-measure}
\section{Classification Method}
%— Overview (No need for subsection)
%\subsection{Data Preparation}
%\subsection{Classifying useful discussion using text similarity and dissimilarity}
%Need a better section name - -.
%\subsection{Validation}
% (10-fold cross validation)
\section{Results}
\subsection{Studied Project and Data set}
\subsection{RQ1: Can we identify useful and useless discussion in code review?}
\subsection{RQ2: How impact of useless discussion impact to the software quality?}
\section{Threat to Validity}
\section{Conclusion and Future Work}

\IEEEpeerreviewmaketitle

\bibliographystyle{IEEEtran}

%\bibliography{references}

% that's all folks
\end{document}

### 2014-07-14 fast.tex
add fast abstract

\documentclass[conference]{IEEEtran}
\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfigure,paralist,graphicx}
%\usepackage{flushend}

\usepackage[font=small,labelfont=bf]{caption}

\usepackage{xspace}
\usepackage{color}
\usepackage{ifthen}
\usepackage{url}
\usepackage{fancybox}

\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
\title{Title..?}

\maketitle
\newboolean{showcomments}
\setboolean{showcomments}{true} % toggle to show or hide comments
\ifthenelse{\boolean{showcomments}}
{\newcommand{\nbnote}[2]{
  % \fbox{\bfseries\sffamily\scriptsize#1}
  \fcolorbox{blue}{yellow}{\bfseries\sffamily\scriptsize#1}
  {\sf\small\textit{#2}}
  % \marginpar{\fbox{\bfseries\sffamily#1}}
 }
}
{\newcommand{\nbnote}[2]{}
 \newcommand{\version}{}
}
\newcommand\pick[1]{\nbnote{Pick sez}{\textcolor{magenta}{#1}}}
\newcommand\thai[1]{\nbnote{Thai sez}{\textcolor{blue}{#1}}}

\begin{IEEEkeywords}
Code review, Software inspection, Text mining
\end{IEEEkeywords}

\section{Introduction}

Modern, lightweight code reviews are widely-used due to its low process overhead,
when compared to formal software inspections, which involves many participants and tedious processes.

In prior works, it has been shown
that the coverage of formal \thai{cite from the citation found in McIntosh's paper}
and informal \thai{cite McIntosh} code review tend to affect the software quality.
However, the free-form nature of informal code reviews makes it harder to evaluate the review's quality and coverage.

In this paper,
we try to find out whether the similarity of code review text correlates with the resulting software quality,
by analyzing the historical reviews and defects records of open-source projects.

\section{Approach}

We sampled 320 comments from the historical data of code reviews in the Qt project.
We then classified the samples as either useful (that is, technically contributing to the code) or not useful.
This task is carried out by three people who worked independently.
We then discarded the samples where people don't agree on its usefulness.

The comment texts,
along with the description of the change that is being reviewed,
are pre-processed by removing stop words and by stemming,
and then converted into pairs of vectors using tf--idf algorithm.
These pairs of vectors are then compared using cosine similarity and euclidean distance measures.

The threshold value for these measures can be found
by trying every possible combination
and searching for a set of value that gives the highest score (we used $F_1$ score).
This is possible because there is a finite number of values in each measure.

\IEEEpeerreviewmaketitle

\bibliographystyle{IEEEtran}

%\bibliography{references}

% that's all folks
\end{document}

### 2014-07-17 paper.tex
add fast abstract
begin work on the methods

@@
 }
-\newcommand\pick[1]{\nbnote{Pick}{\textcolor{magenta}{#1}}}
-\newcommand\thai[1]{\nbnote{Yoshida}{\textcolor{blue}{#1}}}
+\newcommand\pick[1]{\nbnote{Pick sez}{\textcolor{magenta}{#1}}}
+\newcommand\thai[1]{\nbnote{Thai sez}{\textcolor{blue}{#1}}}
 
 \begin{abstract}
+
+% the freeform style of modern code review
+
+% some comments are not technically contributing
 
@@
 \section{Introduction}
-Motivation Example.
+Motivation Example.\thai{Wow}
 \begin{description}
@@
 \end{description}
+
 \section{Background}
@@
 \subsection{Text Mining Techniques}
-\subsubsection{TF-IDF}
-\subsubsection{Euclidian Distance}
+\subsubsection{tf--idf}
+\subsubsection{Similarity Measure}
 \subsection{Evaluation Techniques}
@@
 \subsubsection{F-measure}
+
 \section{Classification Method}
-%— Overview (No need for subsection)
-%\subsection{Data Preparation}
+
+Blah.
+
+\subsection{Data Preparation}
+
+% where we got the data
+We used the review data sets of the Qt project collected by Hamasaki et al.
+Only reviews in the master branch of \texttt{qtbase} project are considered,
+as it is the most active branch.
+
+% quick structure
+Each change includes a \emph{commit message}, which describes what is changed.
+After a change is submitted to Gerrit, reviewers can give scores to it, which will decide if the change will be accepted or not.
+Reviewers can also add comments to the change.
+Comments may optionally be added to a specific line of code inside a changed file.
+
+% conversion into vector, wow
+The commit messages and all comment texts are converted into vectors as follows.
+Firstly, we extracted words from the text, removed the stop words, and put the remaining words through Porter stemming algorithm.
+Secondly, we combined all the remaining tokens to form a corpus of all words from all documents.
+Finally, we used tf--idf to convert each document into a vector.
+
+\subsection{Training Data}
+
+We sampled 320 comments from the historical data of code reviews in the Qt project.
+We then classified the samples as either useful (that is, technically contributing to the code) or not useful.
+This task is carried out by three people who worked independently.
+
+%€” Overview (No need for subsection)
 %\subsection{Classifying useful discussion using text similarity and dissimilarity}

### 2014-07-17 paper.tex
model generation

@@
 
-We sampled 320 comments from the historical data of code reviews in the Qt project.
-We then classified the samples as either useful (that is, technically contributing to the code) or not useful.
+We sampled 320 comments from the data set.
+These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
 This task is carried out by three people who worked independently.
+
+Each comment is then scored based on the number of positive answers.
+For example, a comment with a score of 3 means that all three people said that it is useful,
+while a comment with a score of 0 means that none of us marked it as useful.
+
+%The score of a comment can be defined as:
+
+%\begin{align*}
+%Score_i & = \sum_{\text{reviewer } r} Review(r, i). \\
+%Review(r, i) & = \begin{cases}
+%	1 & \text{if } r \text{ says that the comment } i \text{ is useful,} \\
+%	0 & \text{otherwise.}
+%\end{cases}
+%\end{align*}
+
+\subsection{Model Generation}
+
+% the metrics
+For each comment, we computed a similarity and dissimilarity metrics
+between the comment text and the corresponding commit message.
+We chose cosine similarity and euclidean distance as the metrics to use in model generation.
+
+% assumptions in categorization
+The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
+and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
+where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also have tried using the `or' operator. We found that using `and' produces better result.}
+
+% finding parameters
+To find these parameters, we used a brute-force approach.
 

### 2014-07-18 paper.tex
describe the methods

@@
 
-Blah.
+Wow. This is just a placeholder text. Since this data is a great contribution to our research, I will cite their paper three times: [1][1][1].
+TODO(get rid of this joke and this paragraph altogether, and replace with the actual overview of the method).
 
-\subsection{Data Preparation}
+\subsection{The Data Set}
 
@@
 % quick structure
-Each change includes a \emph{commit message}, which describes what is changed.
-After a change is submitted to Gerrit, reviewers can give scores to it, which will decide if the change will be accepted or not.
-Reviewers can also add comments to the change.
-Comments may optionally be added to a specific line of code inside a changed file.
+Each change includes a \emph{commit message} which describes what is changed.
+After a change is submitted to Gerrit, reviewers can give scores to it.
+The scores will determine whether the change will be accepted or not.
+Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
+Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
+
+\subsection{Data Preprocessing}
+
+The commit messages and all comment texts are converted into vectors as part of the preprocessing step.
+We wrote scripts in Ruby language to perform these tasks.
+
+\subsubsection{Removal of automatically generated text}
+
+First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.
 
 % conversion into vector, wow
-The commit messages and all comment texts are converted into vectors as follows.
-Firstly, we extracted words from the text, removed the stop words, and put the remaining words through Porter stemming algorithm.
-Secondly, we combined all the remaining tokens to form a corpus of all words from all documents.
-Finally, we used tf--idf to convert each document into a vector.
+Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
+This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
+This effectively removed the ID numbers and other non-generic terms.
+
+Next, the lines that appears most frequently are identified.
+From these lines, we then constructed the regular expression patterns,
+and finally, these patterns are used to filter out automatically generated text from our data.
+
+\subsubsection{Stop word removal and stemming}
+
+After the automatically generated messages are removed, we extracted the words by searching for alphanumeric characters and apostrophe, removed the stop words by using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}, and put the remaining words through Porter stemming algorithm.
+The remaining words are then combined to form a corpus of all used words.
+
+\subsubsection{Conversion into vector}
+
+Finally, the tf--idf algorithm is used to convert each document into a vector.
 
@@
 
-\subsection{Model Generation}
+\subsection{Model Generation and Validation}
 
 % the metrics
-For each comment, we computed a similarity and dissimilarity metrics
+For each comment, we computed similarity and dissimilarity metrics
 between the comment text and the corresponding commit message.
@@
 and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
-where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also have tried using the `or' operator. We found that using `and' produces better result.}
+where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}
 
 % finding parameters
-To find these parameters, we used a brute-force approach.
+To find these parameters, a brute-force approach is used.
+This is possible because the set of $similarity$ and $distance$ values are discrete.
+Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.
 
-%€” Overview (No need for subsection)
-%\subsection{Classifying useful discussion using text similarity and dissimilarity}
-%Need a better section name - -.
-%\subsection{Validation}
-% (10-fold cross validation)
+% validation
+To validate our model, 10-fold cross validation is used.
+The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged.
+
 \section{Results}
+
+\subsection{Common Patterns}
+
+The common patterns are found such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
+
+% corpus size and other statistics
+
 \subsection{Studied Project and Data set}
@@
 \subsection{RQ2: How impact of useless discussion impact to the software quality?}
+
+\section{Discussion}
+
 \section{Threat to Validity}
+
 \section{Conclusion and Future Work}

### 2014-07-18 paper.tex
add results

@@
 
-\subsection{Data Preprocessing}
+\subsection{Data Preparation}
 
-The commit messages and all comment texts are converted into vectors as part of the preprocessing step.
+The commit messages and all comment texts are converted into vectors as part of the preparation step.
 We wrote scripts in Ruby language to perform these tasks.
@@
 
-\subsubsection{Stop word removal and stemming}
+\subsubsection{Tokenizing, stop word removal and stemming}
 
-After the automatically generated messages are removed, we extracted the words by searching for alphanumeric characters and apostrophe, removed the stop words by using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}, and put the remaining words through Porter stemming algorithm.
+After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
+Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
+The stemming is performed on remaining tokens using Porter stemming algorithm.
 The remaining words are then combined to form a corpus of all used words.
@@
 % validation
-To validate our model, 10-fold cross validation is used.
-The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged.
+To validate our model, 10-fold cross validation is performed.
+The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
+to give the overall performance of our model.
 
@@
 
-\subsection{Common Patterns}
+\subsection{Data Preparation}
 
-The common patterns are found such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
+In total, there are 6,605 changes and 72,484 comments. 25,076 comments are by the system or one of the bots.
+
+\subsubsection{Common pattern removal}
+
+Many common patterns are found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
+The occurrences of these patterns are removed from our data set.
+This leaves 36,738 comments empty, which probably means that the whole comment is automatically generated.
+Only 17,275 comments and commit messages are left.
+
+\subsubsection{Tokenizing}
+
+After preprocessing, 393,238 tokens are generated in total. They are composed of 20,025 different words.
+This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
 

### 2014-07-18 paper.tex
added 図

@@
 
-\graphicspath{{figures/}}
+\graphicspath{{zu/}}
 \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
@@
 
-Wow. This is just a placeholder text. Since this data is a great contribution to our research, I will cite their paper three times: [1][1][1].
-TODO(get rid of this joke and this paragraph altogether, and replace with the actual overview of the method).
-
-\subsection{The Data Set}
-
 % where we got the data
@@
 Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
+In this paper, we use the term \emph{document} to refer to a single commit message or comment.
+Fig. \ref{fig:hierarchy} shows the relation between documents.
+
+\begin{figure}
+\centering
+\includegraphics[width=2.5in]{hierarchy}
+\caption{Relationship between documents.
+Each rectangle represents a document, which may either be a commit message or a comment.}
+\label{fig:hierarchy}
+\end{figure}
 
@@
 The commit messages and all comment texts are converted into vectors as part of the preparation step.
+Fig. \ref{fig:preprocess} illustrates the overview of this step.
 We wrote scripts in Ruby language to perform these tasks.
+
+\begin{figure}
+\centering
+\includegraphics[width=2.5in]{preprocess}
+\caption{The data preparation process.
+Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
+and are converted into a vector.}
+\label{fig:preprocess}
+\end{figure}
 

### 2014-07-18 paper.tex
move 図s around
write write write - result: training data

@@
 % where we got the data
-We used the review data sets of the Qt project collected by Hamasaki et al.
+We used the review data sets of the Qt project collected by Hamasaki et al TODO(cite properly).
 Only reviews in the master branch of \texttt{qtbase} project are considered,
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[h]
 \centering
-\includegraphics[width=2.5in]{preprocess}
+\includegraphics[width=3in]{preprocess}
 \caption{The data preparation process.
@@
 
+\subsection{Training Data}
+
+After the 320 sample comments have been labeled,
+they are scored based on the number of ``yes'' given to the sample.
+The table below shows the distribution of scores for the training data.
+
+\begin{center}
+\begin{tabular}{|r|r|}
+\hline
+\bfseries Score & \bfseries Count \\
+\hline
+0 & 87 \\ 1 & 60 \\ 2 & 51 \\ 3 & 122 \\
+\hline
+\end{tabular}
+\end{center}
+
 % corpus size and other statistics

### 2014-07-22 paper.tex
add some scatter plot

@@
 
-% corpus size and other statistics
+After the similarity and distance metrics have been calculated,
+these metrics appear to be able to separate the useful comments from the non-useful ones,
+as can be seen in Fig.\ref{fig:scatter}.
+Note that many comments have a cosine similarity metric of 0.
+This is because the comment text and the corresponding commit message has no word in comment.
 
-\subsection{Studied Project and Data set}
-\subsection{RQ1: Can we identify useful and useless discussion in code review?}
-\subsection{RQ2: How impact of useless discussion impact to the software quality?}
+\begin{figure}[h]
+\centering
+\includegraphics[width=3in]{scatter}
+\caption{The similarity and distance plot of the training data.
+The symbol represents the score, which ranges from 0 to 3.}
+\label{fig:scatter}
+\end{figure}
+
+\subsection{Model Generation and Validation}
+
+From our training data,
+the following criteria have been found:
+
+For ``yes'' result:
+\begin{gather*} similarity \geq 0.015528969196702956 \text{ and}\\ distance \leq 2.4949438168165483 \end{gather*}
+
+For ``no'' result:
+\begin{gather*} similarity \leq 0.08752176628812282 \text{ and}\\ distance \geq 2.26567908457803 \end{gather*}
 

### 2014-07-22 paper.tex
Working on Introduction section

--- 2014-07-18 paper.tex
@@
 \section{Introduction}
-Motivation Example.\thai{Wow}
-\begin{description}
-\item[RQ1:] Can we identify useful and useless discussions in code review?
-\item[RQ2:] How impact of useless discussion impact to the software quality?
-\end{description}
+Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
+This method mainly intend to early identify defect before integrating changes.
+The formal inspection\cite{Fagan:1976:DCI:1661010.1661012} is a traditional technique for code review with well-defined structure.
+However, with cumbersome process mandating a well-preparation and in-person meetings of formal inspection, Modern Code Review (MCR)\cite{Bacchelli2013a}, tool-based code reviews have received much attention nowadays and  put into software development regularly in both industrial and OSS projects.
+A major difference between MCR and inspection is the in-person meeting is not required in MCR.
+Reviewers can discuss to find defects through comments on code review tool.
+Then, developers will fix their changes following those comments.
+
+As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in both formal inspection\cite{Porter1998} \pick{and other papers}and MCR\cite{Mcintosh,Beller,Rigby,Hamasaki2013,Baysal2001}.
+This would in
+
+%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.
+
+%Motivation Example.\thai{Wow}
+%\begin{description}
+%\item[RQ1:] Can we identify useful and useless discussions in code review?
+%\item[RQ2:] How impact of useless discussion impact to the software quality?
+%\end{description}
 
@@
 
-%\bibliography{references}
+\bibliography{references}
 

### 2014-07-22 paper.tex
Intro and add title (just for length estimation)

@@
 \title{Title}
+
+\author{
+\IEEEauthorblockN{Thai Pangsakulyanont\IEEEauthorrefmark{1}, Patanamon Thongtanunam\IEEEauthorrefmark{2},  Daniel Port\IEEEauthorrefmark{3}, Hajimu Iida\IEEEauthorrefmark{2}}
+\\
+\IEEEauthorblockA{
+\IEEEauthorrefmark{1} Kasetsart University, Thailand\\
+@ku.ac.th
+}
+
+\IEEEauthorblockA{
+\IEEEauthorrefmark{2} Nara Institute of Science and Technology, Japan\\
+patanamon-t@is.naist.jp, iida@itc.naist.jp\\
+}
+
+\IEEEauthorblockA{
+\IEEEauthorrefmark{3} University of Hawaii at Manoa, USA\\
+dport@hawaii.edu \\
+}
+}
 
@@
 The formal inspection\cite{Fagan:1976:DCI:1661010.1661012} is a traditional technique for code review with well-defined structure.
-However, with cumbersome process mandating a well-preparation and in-person meetings of formal inspection, Modern Code Review (MCR)\cite{Bacchelli2013a}, tool-based code reviews have received much attention nowadays and  put into software development regularly in both industrial and OSS projects.
+Due to cumbersome process mandating a well-preparation and in-person meetings of the formal inspection, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention nowadays and  put into software development regularly in both industrial and OSS projects.
 A major difference between MCR and inspection is the in-person meeting is not required in MCR.
-Reviewers can discuss to find defects through comments on code review tool.
+Reviewers can discuss to find defects by comments through code review tool or mailing list.
 Then, developers will fix their changes following those comments.
 
-As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in both formal inspection\cite{Porter1998} \pick{and other papers}and MCR\cite{Mcintosh,Beller,Rigby,Hamasaki2013,Baysal2001}.
-This would in
+As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in both formal inspection\cite{Porter1998,Kemerer2009} and MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
+However, very little research investigate that in MCR, how does a discussion for a change impact to the quality.
+Since MCR is a lightweight code review, reviewers are not required to strictly examine the proposed code changes as in the formal inspection.
+As studies found that reviewers of MCR in Microsoft only focus on minor logic error rather than discussing deeper \cite{Bacchelli2013a}.
+McIntosh et.
+al.
+\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
 

### 2014-07-23 paper.tex
more on the result

--- 2014-07-22 paper.tex
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=3in]{vector}
+\caption{The similarity and distance metric that is being used.}
+\label{fig:vector}
+\end{figure}
+
 % assumptions in categorization
@@
 they are scored based on the number of ``yes'' given to the sample.
-The table below shows the distribution of scores for the training data.
-
-\begin{center}
-\begin{tabular}{|r|r|}
-\hline
-\bfseries Score & \bfseries Count \\
-\hline
-0 & 87 \\ 1 & 60 \\ 2 & 51 \\ 3 & 122 \\
-\hline
-\end{tabular}
-\end{center}
+There were 87, 60, 51, and 122 comments with scores of 0, 1, 2, and 3, respectively.
 
@@
 
+% the criteria that were found
 From our training data,
-the following criteria have been found:
+the following criteria have been obtained that maximizes the F$_1$ score:
 
-For ``yes'' result:
-\begin{gather*} similarity \geq 0.015528969196702956 \text{ and}\\ distance \leq 2.4949438168165483 \end{gather*}
+Criteria to find samples with score of 3 (``positive''):
+\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
+\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
 
-For ``no'' result:
-\begin{gather*} similarity \leq 0.08752176628812282 \text{ and}\\ distance \geq 2.26567908457803 \end{gather*}
+Criteria to find samples with score of 0 (``negative''):
+\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
+\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
+
+Note that these constant values can vary from project to project, and thus is not a universal constant.
+
+% run result
+
+Running our model against the training data gives us the result displayed in the following table.
+In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
+
+\begin{center}
+\begin{tabular}{|r|rrrr|}
+\hline
+& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
+\hline
+Negative & 69 & 23 & 7 & 6 \\
+Neither & 12 & 24 & 20 & 20 \\
+Overlap & 1 & 1 & 0 & 1 \\
+Positive & 4 & 13 & 24 & 95 \\
+\hline
+\end{tabular}
+\end{center}
+
+As expected, most comments classified as \emph{negative} have score of 0 and 1,
+while most \emph{positive} comments have score of 2 and 3.
+However, some comments in every score were lost and classified as \emph{neither}.
+
+% cross validation result
 

### 2014-07-23 paper.tex
First draft of Intro

--- 2014-07-22 paper.tex
@@
 \begin{IEEEkeywords}
-Peer Code Review, Software Inspection, Reviewer Recommendation, Reviewer Assignment
+Modern Code Review, Software Quality, Text Mining
 \end{IEEEkeywords}
@@
 As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in both formal inspection\cite{Porter1998,Kemerer2009} and MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
-However, very little research investigate that in MCR, how does a discussion for a change impact to the quality.
-Since MCR is a lightweight code review, reviewers are not required to strictly examine the proposed code changes as in the formal inspection.
-As studies found that reviewers of MCR in Microsoft only focus on minor logic error rather than discussing deeper \cite{Bacchelli2013a}.
+However, very little research investigate that in MCR, how does a discussion for a proposed change impact to the software quality.
+Since most of the proposed change improvements are triggered from reviewer comments \cite{Beller}.
 McIntosh et.
@@
 \cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
+However, there is a study found that reviewers of MCR in Microsoft only focus on minor logic error rather than discussing deeper \cite{Bacchelli2013a}.
+As MCR is a lightweight code review, reviewers are not required to strictly examine the proposed code changes as in the formal inspection.
+From prior works, we conjecture that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
 
+To understand the impact of discussion in MCR, a manual classification is required as study of Beller et.
+al.
+\cite{Beller}.
+As a massive amount of changes and comments in MCR history\cite{Balachandran2013}, it is painstaking and time consuming to classify data sets to perform quantitative analysis.
+Moreover, the comments in MCR is unstructured natural text unlike a checklist in the formal inspection.
+%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
+
+In this paper, we present an approach to automatically classify the usefulness of comments.
+We define that the usefulness is a comment that contribute to improve the proposed changes.
+In our approach, we analyze the similarity between commit message of the proposed changes and their comments.
+Our key idea is that useful comments are likely to contain similar topic as the proposed changes.
+To do so, we use text mining techniques, Vector Space Model (VSM) to calculate similarity and use euclidian distance to calculate dissimilarity.
+We create our predictive model by estimating a set of similarity and dissimilarity values that best discriminate between a useful and useless comments using the prediction evaluations: Precision, Recall and F-measure.
+
+For our empirical study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process.
+Our case study project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
+To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy.
+We also used our predictive model for the all set of comments to preliminary estimate quality of reviews.
+According to this, we address the following two research questions:
+
+\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
+\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?
+
+\noindent The main contribution of this paper are:
+\begin{itemize}
+\item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
+\item The experimental results show that our approach can classify comments with XX of F-measure.
+\item We found that XX\% of comments for each review are classified as useful comments, while XX \% of comments are classified as useless comments.
+\end{itemize} 
 %Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.
@@
 %Motivation Example.\thai{Wow}
-%\begin{description}
-%\item[RQ1:] Can we identify useful and useless discussions in code review?
-%\item[RQ2:] How impact of useless discussion impact to the software quality?
-%\end{description}
 

### 2014-07-23 paper.tex

@@
 they are scored based on the number of ``yes'' given to the sample.
-The table below shows the distribution of scores for the training data.
+There were 87, 60, 51, and 122 comments with scores of 0, 1, 2, and 3, respectively.
+
+After the similarity and distance metrics have been calculated,
+these metrics appear to be able to separate the useful comments from the non-useful ones,
+as can be seen in Fig.\ref{fig:scatter}.
+Note that many comments have a cosine similarity metric of 0.
+This is because the comment text and the corresponding commit message has no word in comment.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=3in]{scatter}
+\caption{The similarity and distance plot of the training data.
+The symbol represents the score, which ranges from 0 to 3.}
+\label{fig:scatter}
+\end{figure}
+
+\subsection{Model Generation and Validation}
+
+% the criteria that were found
+From our training data,
+the following criteria have been obtained that maximizes the F$_1$ score:
+
+Criteria to find samples with score of 3 (``positive''):
+\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
+\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
+
+Criteria to find samples with score of 0 (``negative''):
+\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
+\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
+
+Note that these constant values can vary from project to project, and thus is not a universal constant.
+
+% run result
+
+Running our model against the training data gives us the result displayed in the following table.
+In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
 
 \begin{center}
-\begin{tabular}{|r|r|}
+\begin{tabular}{|r|rrrr|}
 \hline
-\bfseries Score & \bfseries Count \\
+& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
 \hline
-0 & 87 \\ 1 & 60 \\ 2 & 51 \\ 3 & 122 \\
+Negative & 69 & 23 & 7 & 6 \\
+Neither & 12 & 24 & 20 & 20 \\
+Overlap & 1 & 1 & 0 & 1 \\
+Positive & 4 & 13 & 24 & 95 \\
 \hline
@@
 
-% corpus size and other statistics
+As expected, most comments classified as \emph{negative} have score of 0 and 1,
+while most \emph{positive} comments have score of 2 and 3.
+However, some comments in every score were lost and classified as \emph{neither}.
 
-\subsection{Studied Project and Data set}
-\subsection{RQ1: Can we identify useful and useless discussion in code review?}
-\subsection{RQ2: How impact of useless discussion impact to the software quality?}
+% cross validation result
 

### 2014-07-23 paper.tex
more colors

--- 2014-07-23 paper.tex
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=6in]{overview}
+\caption{Overview of our classification method.}
+\label{fig:overview}
+\end{figure*}
+
 % where we got the data
@@
 Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
-In this paper, we use the term \emph{document} to refer to a single commit message or comment.
-Fig. \ref{fig:hierarchy} shows the relation between documents.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=2.5in]{hierarchy}
-\caption{Relationship between documents.
-Each rectangle represents a document, which may either be a commit message or a comment.}
-\label{fig:hierarchy}
-\end{figure}
+% overview
+In our classification method,
+all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
+Few comments are sampled and then classified manually for use in training and validation.
+A model is created from these training data, from which useful comments can automatically be identified.
+This process is illustrated in Fig.\ref{fig:overview}.
 
@@
 
-\subsubsection{Tokenizing, stop word removal and stemming}
+\subsubsection{Tokenization, stop word removal and stemming}
 

### 2014-07-23 paper.tex
Background: Section A.

--- 2014-07-23 paper.tex
@@
 \documentclass[conference]{IEEEtran}
-\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfigure,paralist,graphicx}
+\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfig,paralist,graphicx}
 %\usepackage{flushend}
@@
 This method mainly intend to early identify defect before integrating changes.
-The formal inspection\cite{Fagan:1976:DCI:1661010.1661012} is a traditional technique for code review with well-defined structure.
-Due to cumbersome process mandating a well-preparation and in-person meetings of the formal inspection, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention nowadays and  put into software development regularly in both industrial and OSS projects.
-A major difference between MCR and inspection is the in-person meeting is not required in MCR.
+Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and  put into software development regularly in both industrial and OSS projects.
+A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
 Reviewers can discuss to find defects by comments through code review tool or mailing list.
@@
 
-As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in both formal inspection\cite{Porter1998,Kemerer2009} and MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
+As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
 However, very little research investigate that in MCR, how does a discussion for a proposed change impact to the software quality.
 Since most of the proposed change improvements are triggered from reviewer comments \cite{Beller}.
-McIntosh et.
-al.
-\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
-However, there is a study found that reviewers of MCR in Microsoft only focus on minor logic error rather than discussing deeper \cite{Bacchelli2013a}.
-As MCR is a lightweight code review, reviewers are not required to strictly examine the proposed code changes as in the formal inspection.
-From prior works, we conjecture that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
-
-To understand the impact of discussion in MCR, a manual classification is required as study of Beller et.
+It is possible that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
+To determine the impact of discussion in MCR, a manual classification is required as study of Beller et.
 al.
 \cite{Beller}.
-As a massive amount of changes and comments in MCR history\cite{Balachandran2013}, it is painstaking and time consuming to classify data sets to perform quantitative analysis.
+As a massive amount of changes and comments in MCR history\cite{Balachandran2013,Thongtanunam2014}, it is painstaking and time consuming to classify data sets to perform quantitative analysis.
 Moreover, the comments in MCR is unstructured natural text unlike a checklist in the formal inspection.
@@
 \section{Background}
-\subsection{Modern Code Review}
+In this section, we describe MCR process based on Gerrit system.
+Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
+\subsection{Modern Code Review Process}
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
+\caption{An simplified version of MCR Process based on Gerrit system}
+\label{fig:process}
+\end{figure}
+Figure \ref{fig:process} shows an overview of MCR process based on Gerrit system.
+The grey box shows the review process of the system which composed of four main steps.
+(1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
+(2) reviewers examine the proposed code changes whether it contains defects or not.
+(3) reviewers will give comments where should the author improve the code change.
+The author will create a new change according to the comments then re-submit a new patch again.
+Then, reviewers will examine the new change.
+If there is still a needed improvement, reviewers will give comments to fix again.
+The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).
+
+According to this process, reviewers' comment is the most important for the software quality.
+McIntosh et.
+al.
+\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
+However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective.
+Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}.
+Our observation in Qt project also correspond this finding.
+We found some comments is superficial as shown in Fig.
+\ref{fig:example}(a), some comments only discuss about Version Control System (e.g.
+Git) used in the project.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
+\caption{Examples of comment in code reviews of Qt project.}
+\label{fig:example}
+\end{figure}
+
 \subsection{Text Mining Techniques}

### 2014-07-23 paper.tex
write text mining section

@@
 \begin{abstract}
-
+Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
+This method mainly intend to early identify defect before integrating changes.
+Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and  put into software development regularly in both industrial and OSS projects.
+A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
+Reviewers can discuss to find defects by comments through code review tool or mailing list.
+Then, developers will fix their changes following those comments.
 % the freeform style of modern code review
@@
 Our observation in Qt project also correspond this finding.
-We found some comments is superficial as shown in Fig.
-\ref{fig:example}(a), some comments only discuss about Version Control System (e.g.
-Git) used in the project.
+We found some comments are superficial and unrelated to the proposed changes.
+For example, a superficial and unconfident reviewer as shown in Fig.
+\ref{fig:example}(a), a comment for rule of using Version Control System (e.g.
+Git) in the project Fig.
+\ref{fig:example}(b).
 
@@
 
-\subsection{Text Mining Techniques}
-\subsubsection{tf--idf}
-\subsubsection{Similarity Measure}
-\subsection{Evaluation Techniques}
+\subsection{Text Mining Technique: Vector Space Model}
+Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language.
+In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
+
+\noindent\textbf{VSM} is a model for representing text documents as vectors.
+Thus, for a set of documents ($D$), each document ($d$) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in the set of documents; and $w_{t,d}$ is TF-IDF weighting of term $t$ calculated from term occurrence frequency.
+The weight of $w_{t,d}$   can be calculated following Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
+
+\begin{equation}
+w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
+\label{eq:tf-idf}
+\end{equation}
+\pick{Equation need to be check.}
+
+To calculate the similarity between two document vectors $\overrightarrow{V_c}$ and $\overrightarrow{V_d}$, we use Cosine similarity and Euclidian distance. 
+\pick{Why we need two measurements?}
+
+\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product as described in Equation \ref{eq:cosine}.
+The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.
+
+\begin{equation}
+\cos\theta(\overrightarrow{V_c},\overrightarrow{V_d}) = \frac{\sum_{i=1}^{|D|} w_{i,c} \times w_{i,d}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,c} \times \sum_{i=1}^{|D|} w^2_{i,d}}}
+\label{eq:cosine}
+\end{equation}
+
+\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}.
+The distance value is ranging $[0,\infty)$ where 0 means these vectors is same vector and a more distance means less similar vectors.
+This can be used to determine how dissimilarity between two vectors.
+
+\begin{equation}
+d(\overrightarrow{V_c},\overrightarrow{V_d}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,c} - w_{i,d})^2}
+\label{eq:euclid}
+\end{equation}
+
+\subsection{Estimating Similarity and Dissimilarity Criteria}
+In our approach, we build our classification model by selecting similarity and dissimilarity that best discriminate comments.
+To do so, we use three traditional measurements: Precision, Recall, and F-measure.
 \subsubsection{Precision and Recall}

### 2014-07-23 paper.tex
Working on approach section

--- 2014-07-23 paper.tex
@@
 %\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
+\caption{An simplified version of MCR Process based on Gerrit system}
+\label{fig:process}
+\end{figure}
 
@@
 
-\section{Background}
-In this section, we describe MCR process based on Gerrit system.
+%\section{Background}
+%In this section, we describe MCR process based on Gerrit system.
 Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
-\subsection{Modern Code Review Process}
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
-\caption{An simplified version of MCR Process based on Gerrit system}
-\label{fig:process}
-\end{figure}
-Figure \ref{fig:process} shows an overview of MCR process based on Gerrit system.
-The grey box shows the review process of the system which composed of four main steps.
+\section{Modern Code Review Process}
+
+An overview of MCR process based on Gerrit system is shown in Figure \ref{fig:process}.
+The grey area shows the review process of the system which composed of four main steps.
 (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
@@
 
-\subsection{Text Mining Techniques}
-\subsubsection{tf--idf}
-\subsubsection{Similarity Measure}
-\subsection{Evaluation Techniques}
-\subsubsection{Precision and Recall}
-\subsubsection{F-measure}
+\section{Reviewers' Comments Classification Approach}
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.35, trim = 50 90 0 30, clip=true]{overview2}
+\caption{Overview of our classification approach.}
+\label{fig:overview}
+\end{figure}
 
-\section{Classification Method}
+Figure \ref{fig:overview} shows the overview of our proposed approach.
+We classify usefulness of comments by measuring similarity between commit message of proposed change and its comments.
+To calculate similarity in Fig.
+\ref{fig:overview}(a), we use Vector Space Model (VSM) which is well-known technique for retrieving similar documents written in unstructured natural language.
+We also use euclidian distance to calculate dissimilarity.
+For our training dataset, we manually identify every pair of comment and commit messages in Fig.
+\ref{fig:overview}(b).
+Then, we use the results from Fig.
+\ref{fig:overview}(a) and from Fig.
+\ref{fig:overview}(b) to estimate similarity and dissimilarity threshold that can best discriminate useful/useless comments.
+Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.
 
-\begin{figure*}
-\centering
-\includegraphics[width=6in]{overview}
-\caption{Overview of our classification method.}
-\label{fig:overview}
-\end{figure*}
+To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
+\begin{itemize}
+\item \textbf{useful}$(c,S_T,D_T)= \mathrm{TRUE}$ if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
+\item \textbf{useless}$(c,S'_T,D'_T)= \mathrm{TRUE}$  if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
+\end{itemize}
+where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.
+The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review.
+The details our approach is described in the following subsections.
+
+\subsection{Similarity and Dissimilarity Calculation based on VSM}
+%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language.
+In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
+For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
+To do so, we use VSM which is a model for representing text documents as vectors.
+For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
+The $w_{t,d}$ value is TF-IDF weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
+
+\begin{equation}
+w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
+\label{eq:tf-idf}
+\end{equation}
+\pick{Equation need to be check.}
+
+After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance. 
+\pick{Why we need two measurements?}
+
+\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product.
+Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}.
+The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.
+
+\begin{equation}
+\mathrm{sim}(m,c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
+\label{eq:cosine}
+\end{equation}
+
+\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}.
+We can use this distance as an dissimilarity.
+Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Euclidian distance using Equation \ref{eq:cosine}.
+The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.
+
+\begin{equation}
+\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
+\label{eq:euclid}
+\end{equation}
+\subsection{Manual useful comments identification}
+
+\subsection{Estimating Similarity and Dissimilarity Threshold}
+To find similarity and dissimilarity thresholds, we iteratively measure an accuracy for values of $S_T$ and $S'_T$ raging $[0,1]$; and values of $D_T$ and $D'_T$ ranging $[0,\infty)$.
+We define that the best similarity and dissimilarity thresholds are the set of define values can maximize accuracy value.
+In this study, we use F-measure score for an accuracy measure.
+The F-measure value can be calculated using Equation \ref{}
+
+\begin{equation}
+\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
+\label{eq:precision}
+\end{equation}
+where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
+%According to this, we can formalize as follows:
+
+%\begin{equation}
+%(S_T,D_T) = \max(\{\mathrm{F\text{-}measure} \text{ of \textbf{useful}}(c,s_T,d_T) | s_T\in[0,1] \text{ and } d_T\in [0,\infty) \})
+%\end{equation}
+
+\section{Empirical Study}
 

### 2014-07-24 paper.tex
minor change

--- 2014-07-23 paper.tex
@@
 \documentclass[conference]{IEEEtran}
-\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfig,paralist,graphicx}
+\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfigure,paralist,graphicx}
 %\usepackage{flushend}
@@
 \title{Title}
-
-\author{
-\IEEEauthorblockN{Thai Pangsakulyanont\IEEEauthorrefmark{1}, Patanamon Thongtanunam\IEEEauthorrefmark{2},  Daniel Port\IEEEauthorrefmark{3}, Hajimu Iida\IEEEauthorrefmark{2}}
-\\
-\IEEEauthorblockA{
-\IEEEauthorrefmark{1} Kasetsart University, Thailand\\
-@ku.ac.th
-}
-
-\IEEEauthorblockA{
-\IEEEauthorrefmark{2} Nara Institute of Science and Technology, Japan\\
-patanamon-t@is.naist.jp, iida@itc.naist.jp\\
-}
-
-\IEEEauthorblockA{
-\IEEEauthorrefmark{3} University of Hawaii at Manoa, USA\\
-dport@hawaii.edu \\
-}
-}
 
@@
 \begin{IEEEkeywords}
-Modern Code Review, Software Quality, Text Mining
+Peer Code Review, Software Inspection, Reviewer Recommendation, Reviewer Assignment
 \end{IEEEkeywords}
@@
 \section{Introduction}
-Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-This method mainly intend to early identify defect before integrating changes.
-Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and  put into software development regularly in both industrial and OSS projects.
-A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can discuss to find defects by comments through code review tool or mailing list.
-Then, developers will fix their changes following those comments.
-
-As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
-However, very little research investigate that in MCR, how does a discussion for a proposed change impact to the software quality.
-Since most of the proposed change improvements are triggered from reviewer comments \cite{Beller}.
-It is possible that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
-To determine the impact of discussion in MCR, a manual classification is required as study of Beller et.
-al.
-\cite{Beller}.
-As a massive amount of changes and comments in MCR history\cite{Balachandran2013,Thongtanunam2014}, it is painstaking and time consuming to classify data sets to perform quantitative analysis.
-Moreover, the comments in MCR is unstructured natural text unlike a checklist in the formal inspection.
-%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
-
-In this paper, we present an approach to automatically classify the usefulness of comments.
-We define that the usefulness is a comment that contribute to improve the proposed changes.
-In our approach, we analyze the similarity between commit message of the proposed changes and their comments.
-Our key idea is that useful comments are likely to contain similar topic as the proposed changes.
-To do so, we use text mining techniques, Vector Space Model (VSM) to calculate similarity and use euclidian distance to calculate dissimilarity.
-We create our predictive model by estimating a set of similarity and dissimilarity values that best discriminate between a useful and useless comments using the prediction evaluations: Precision, Recall and F-measure.
-
-For our empirical study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process.
-Our case study project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
-To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy.
-We also used our predictive model for the all set of comments to preliminary estimate quality of reviews.
-According to this, we address the following two research questions:
-
-\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
-\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?
-
-\noindent The main contribution of this paper are:
-\begin{itemize}
-\item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
-\item The experimental results show that our approach can classify comments with XX of F-measure.
-\item We found that XX\% of comments for each review are classified as useful comments, while XX \% of comments are classified as useless comments.
-\end{itemize} 
-%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.
-
-%Motivation Example.\thai{Wow}
+Motivation Example.\thai{Wow}
+\begin{description}
+\item[RQ1:] Can we identify useful and useless discussions in code review?
+\item[RQ2:] How impact of useless discussion impact to the software quality?
+\end{description}
 
 \section{Background}
-In this section, we describe MCR process based on Gerrit system.
-Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
-\subsection{Modern Code Review Process}
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
-\caption{An simplified version of MCR Process based on Gerrit system}
-\label{fig:process}
-\end{figure}
-Figure \ref{fig:process} shows an overview of MCR process based on Gerrit system.
-The grey box shows the review process of the system which composed of four main steps.
-(1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
-(2) reviewers examine the proposed code changes whether it contains defects or not.
-(3) reviewers will give comments where should the author improve the code change.
-The author will create a new change according to the comments then re-submit a new patch again.
-Then, reviewers will examine the new change.
-If there is still a needed improvement, reviewers will give comments to fix again.
-The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).
-
-According to this process, reviewers' comment is the most important for the software quality.
-McIntosh et.
-al.
-\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
-However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective.
-Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}.
-Our observation in Qt project also correspond this finding.
-We found some comments is superficial as shown in Fig.
-\ref{fig:example}(a), some comments only discuss about Version Control System (e.g.
-Git) used in the project.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
-\caption{Examples of comment in code reviews of Qt project.}
-\label{fig:example}
-\end{figure}
-
+\subsection{Modern Code Review}
 \subsection{Text Mining Techniques}
@@
 
+% stuff
+
 \section{Threat to Validity}
@@
 
-\bibliography{references}
+%\bibliography{references}
 

### 2014-07-24 paper.tex
add more spaces

--- 2014-07-23 paper.tex
@@
 \IEEEauthorrefmark{1} Kasetsart University, Thailand\\
-@ku.ac.th
+b5410545036@ku.ac.th
 }
@@
 \newcommand\thai[1]{\nbnote{Thai sez}{\textcolor{blue}{#1}}}
+\newcommand\TODO[1]{\textcolor{red}{\textbf{TODO} #1}}
 
@@
 % where we got the data
-We used the review data sets of the Qt project collected by Hamasaki et al TODO(cite properly).
+We used the review data sets of the Qt project collected by Hamasaki et al \TODO{cite properly}.
 Only reviews in the master branch of \texttt{qtbase} project are considered,

### 2014-07-24 paper.tex
added cross validation result and outline for discussion

@@
 % validation
-To validate our model, 10-fold cross validation is performed.
+To validate our model, we randomly split the data into 10 parts.
+9 parts are used for training, and 1 part for validation.
+This process is repeated 300 times. % while I sleep
 The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
@@
 
-\subsection{Model Generation and Validation}
+\subsection{Model Generation}
 
@@
 while most \emph{positive} comments have score of 2 and 3.
-However, some comments in every score were lost and classified as \emph{neither}.
+However, some comments in every score type were classified as \emph{neither}.
 
@@
 
+\subsection{Cross Validation}
+
+After we performed cross validation, we obtained the following result:
+for positive and negative classifications,
+we obtained an average F$_1$ score of 0.693 and 0.681,
+with standard deviation of 0.090 and 0.118, respectively.
+
 \section{Discussion}
 
-% stuff
+% noisy data, and binary classification
+
+% tuning the F score for precision and recall
+
+% reasons for classification as useful or not useful
+
+% example of false positive and false negatives
 

### 2014-07-24 paper.tex
added more discussion

@@
 \noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
-\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?
+\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
+\noindent \textbf{RQ3:} Is this a cost-efficient way to identify useful and useless comments?
 
@@
 
-\section{Empirical Study}
+\section{Case Study}
 
@@
 
-In total, there are 6,605 changes and 72,484 comments. 25,076 comments are by the system or one of the bots.
+\begin{figure}[h]
+\centering
+\includegraphics[width=3.2in]{filter}
+\caption{The filtering process.}
+\label{fig:filter}
+\end{figure}
+
+\subsubsection{Data extraction}
+
+6,605 changes and 72,484 comments have been extracted from the raw dataset.
+35\% of the comments are by the system or one of the bots, and are thus discarded.
 
@@
 
-Many common patterns are found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
-The occurrences of these patterns are removed from our data set.
-This leaves 36,738 comments empty, which probably means that the whole comment is automatically generated.
-Only 17,275 comments and commit messages are left.
+By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
+
+Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
+This probably means these comments solely contain automatically-generated text, and are thus discarded.
+This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.
 
@@
 
-After preprocessing, 393,238 tokens are generated in total. They are composed of 20,025 different words.
+After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
 This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
@@
 % noisy data, and binary classification
+Our training data is very noisy because there are disagreements between our judgment of ``usefulness.''
+These samples cannot be classified as either useful or not useful.
+This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
+
+By removing the samples with scores of 1 and 2, leaving with 209 samples without disagreements, and performing 10-fold cross-validation, we received a much better average F$_1$ score of 0.896.
 
 % tuning the F score for precision and recall
+Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
+For instance, if we wanted to measure the amount of useful comments within a large dataset, we can give more weight to precision, sacrificing some good comments.
+If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.
 
 % reasons for classification as useful or not useful
+During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
+
+\begin{itemize}
+	\item they contain new information;
+	\item they contain constructive suggestions;
+	\item they discuss directly about the change; and
+	\item they discuss technical matters.
+\end{itemize}
+
+Examples of reasons for negative comments include:
+
+\begin{itemize}
+	\item chatting (i.e. no new information, just communication);
+	\item not discussing directly about the change;
+	\item discussing about the process workflow; and
+	\item discussing about Git or Gerrit itself.
+\end{itemize}
 

### 2014-07-24 scripts_for_thaipang/scatter_graph.R
R scripts for generate graph

@@ -1,0 +1,31 @@
+dat <- read.csv("scatter_value.csv")
+dat$Similarity[which(dat$Similarity == 0)] = 0.000000001 
+St1 = 0.015528
+Dt1 = 2.494944
+St2 = 0.087522
+Dt2 = 2.265679 
+
+colors = c("red","darkorange","blue","darkgreen")
+pch = c(4,2,3,16)
+
+#Print Graph with Log
+pdf("scatter_log.pdf")
+plot(dat$Distance,dat$Similarity,xlim=c(0.8,8),pch=16,col=NA,log="xy",xlab="Distance",ylab="Similarity",yaxt="n")
+rect(0.0000001,St1,Dt1,3,col=rgb(0,0.8,0,0.3),border=NA)
+rect(Dt2,0.0000000001,10,St2,col=rgb(0.8,0,0,0.3),border=NA)
+axis(2,at=c(0.000000001,0.0000001,0.00001,0.001,0.1,0.5,0.8,1),labels=c(0,0.0000001,0.00001,0.001,0.1,"","","1"))
+for(i in seq(0,3)){
+	points(dat$Distance[which(dat$Vote == i)],dat$Similarity[which(dat$Vote == i)],pch=pch[i+1],col=colors[i+1])
+}
+legend("topright", title="Comments Class", legend = c("Useless (YES = 0)","Unclear (YES = 1)","Unclear (YES = 2)","Useful (YES = 3)"), pch=pch, col=colors,bg=rgb(1,1,1,0.8))
+
+dev.off()
+
+# pdf("scatter.pdf")
+# plot(dat$Distance,dat$Similarity,xlim=c(0.8,8),pch=16,col=NA,xlab="Distance",ylab="Similarity")
+# rect(0.0000001,St1,Dt1,3,col=rgb(0,0.8,0,0.3),border=NA)
+# rect(Dt2,-1,10,St2,col=rgb(0.8,0,0,0.3),border=NA)
+# for(i in seq(0,3)){
+# 	points(dat$Distance[which(dat$Vote == i)],dat$Similarity[which(dat$Vote == i)],pch=pch[i+1],col=colors[i+1])
+# }
+# dev.off()

### 2014-07-24 paper.tex
Result: RQ1 (roughly done)

@@
 \documentclass[conference]{IEEEtran}
-\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,makecell,algorithm,algorithmic,subfig,paralist,graphicx}
+\usepackage{microtype,mathtools,amsmath,multibib,amsfonts,multicol,array,multirow,place ins,cite,balance,makecell,algorithm,algorithmic,subfigure,paralist}
 %\usepackage{flushend}
-
+\usepackage{graphicx}
+\usepackage{listings}
+\usepackage{url}
 \usepackage[font=small,labelfont=bf]{caption}
@@
 \usepackage{ifthen}
-\usepackage{url}
 \usepackage{fancybox}
@@
 
-For our empirical study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process.
-Our case study project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
+For our case study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process.
+Our case studied project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
 To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy.
@@
 \begin{itemize}
-\item \textbf{useful}$(c,S_T,D_T)= \mathrm{TRUE}$ if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
-\item \textbf{useless}$(c,S'_T,D'_T)= \mathrm{TRUE}$  if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
+\item $\Theta(c,S_T,D_T)$ predict as \textbf{useful} if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
+\item $\Omega(c,S'_T,D'_T)$ predict as \textbf{useles} if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
 \end{itemize}
@@
 The details our approach is described in the following subsections.
+\pick{Why we need two measurements?}
+\pick{What happen in model for otherwise?}
 
@@
 \end{equation}
-\pick{Equation need to be check.}
 
 After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.
-\pick{Why we need two measurements?}
 
@@
 \end{equation}
-\subsection{Manual useful comments identification}
 
 \subsection{Estimating Similarity and Dissimilarity Threshold}
-To find similarity and dissimilarity thresholds, we iteratively measure an accuracy for values of $S_T$ and $S'_T$ raging $[0,1]$; and values of $D_T$ and $D'_T$ ranging $[0,\infty)$.
-We define that the best similarity and dissimilarity thresholds are the set of define values can maximize accuracy value.
-In this study, we use F-measure score for an accuracy measure.
-The F-measure value can be calculated using Equation \ref{}
+We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$.
+This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall).
+This can be calculated using Equation \ref{eq:fmeasure}.
 
 \begin{equation}
-\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
-\label{eq:precision}
+\begin{split}
+\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
+\\
+\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
+\\
+\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
+\end{split}
+\label{eq:fmeasure}
 \end{equation}
-where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
+
+Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful.
+To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments.
+For the correctness of prediction, we determine from the useful/useless defined dataset.
+
+%Using this method, we iteratively measure an accuracy for values of $s_t$ and $s'_t$ ranging $[0,1]$; and values of $d_t$ and $d'_t$ ranging $[0,\infty)$.
+
+%\begin{equation}
+%\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
+%\label{eq:precision}
+%\end{equation}
+
+%where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
 %According to this, we can formalize as follows:
@@
 
-\section{Case Study}
+\section{Case Study Design}
+
+We used the review history of Qt project from Gerrit code review tool provided by Hamasaki et.
+al.
+\cite{Hamasaki2013}.
+Qt project is a large open source project composed of small subsystems.
+For our case study, we selected the most active subproject \texttt{qtbase} project.
+From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.
 
 % where we got the data
-We used the review data sets of the Qt project collected by Hamasaki et al \TODO{cite properly}.
-Only reviews in the master branch of \texttt{qtbase} project are considered,
-as it is the most active branch.
+%We used the review data sets of the Qt project collected by Hamasaki et al\cite{Hamasaki2013}.
+%Only reviews in the master branch of \texttt{qtbase} project are considered,
+%as it is the most active branch.
 
 % quick structure
-Each change includes a \emph{commit message} which describes what is changed.
-After a change is submitted to Gerrit, reviewers can give scores to it.
-The scores will determine whether the change will be accepted or not.
-Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
-Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
+%\pick{This already explain in background :D}
+%Each change includes a \emph{commit message} which describes what is changed.
+%After a change is submitted to Gerrit, reviewers can give scores to it.
+%The scores will determine whether the change will be accepted or not.
+%Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
+%Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
 
 % overview
-In our classification method,
-all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
-Few comments are sampled and then classified manually for use in training and validation.
-A model is created from these training data, from which useful comments can automatically be identified.
-This process is illustrated in Fig.\ref{fig:overview}.
+%In our classification method,
+%all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
+%Few comments are sampled and then classified manually for use in training and validation.
+%A model is created from these training data, from which useful comments can automatically be identified.
+%This process is illustrated in Fig.\ref{fig:overview}.
+%
 
 \subsection{Data Preparation}
+We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we firstly processed the commit message and comments as follows:
 
-The commit messages and all comment texts are converted into vectors as part of the preparation step.
-Fig. \ref{fig:preprocess} illustrates the overview of this step.
-We wrote scripts in Ruby language to perform these tasks.
+\subsubsection{Automatically generated messages removal}
+In Gerrit, the comments are composed of comment messages from reviewers and automated messages.
+These automatic messages are generated by Gerrit and integration system to record activities, for example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}.
+Since these messages are not impact to software quality\cite{Mcintosh}, we removed them from our data set.
+We identified these automatic messages using regular expression and selecting frequently appeared pattern of messages.
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=3in]{preprocess}
-\caption{The data preparation process.
-Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
-and are converted into a vector.}
-\label{fig:preprocess}
-\end{figure}
+%The commit messages and all comment texts are converted into vectors as part of the preparation step.
+%Fig. \ref{fig:preprocess} illustrates the overview of this step.
+%We wrote scripts in Ruby language to perform these tasks.
 
-\subsubsection{Removal of automatically generated text}
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=3in]{preprocess}
+%\caption{The data preparation process.
+%Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
+%and are converted into a vector.}
+%\label{fig:preprocess}
+%\end{figure}
 
-First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.
+%\subsubsection{Removal of automatically generated text}
+%
+%First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.
+%
+%% conversion into vector, wow
+%Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
+%This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
+%This effectively removed the ID numbers and other non-generic terms.
+%
+%Next, the lines that appears most frequently are identified.
+%From these lines, we then constructed the regular expression patterns,
+%and finally, these patterns are used to filter out automatically generated text from our data.
 
-% conversion into vector, wow
-Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
-This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
-This effectively removed the ID numbers and other non-generic terms.
+\subsubsection{Data Preprocessing}
+ we extracted semantic words commit messages and comment messages before converting to vector.
+For each message, we removed all punctuation signs, digits, and common words (e.g.
+a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}.
+We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.
 
-Next, the lines that appears most frequently are identified.
-From these lines, we then constructed the regular expression patterns,
-and finally, these patterns are used to filter out automatically generated text from our data.
+%After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
+%Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
+%The stemming is performed on remaining tokens using Porter stemming algorithm.
+%The remaining words are then combined to form a corpus of all used words.
 
-\subsubsection{Tokenization, stop word removal and stemming}
+%\subsubsection{Conversion into vector}
+%
+%Finally, the tf--idf algorithm is used to convert each document into a vector.
 
-After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
-Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
-The stemming is performed on remaining tokens using Porter stemming algorithm.
-The remaining words are then combined to form a corpus of all used words.
+\subsubsection{Ground-Truth Data Preparation}
+To prepare ground-truth data, we read comments and manually identified useful and useless comments.
+In this study, we use three people (the first two authors and one student) independently classify comments by giving a question that ``Does this comment technically contribute to its change or not?''.
+Then, the readers gave a vote for \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.
+From the voting scores, we regarded that the comments with three \texttt{YES} votes are \textbf{useful} comments and the comments with no \texttt{YES} votes (i.e.
+three \texttt{NO} votes) are \textbf{useless} comments.
+For the comments with one and two \texttt{YES}' votes, we remained them as \textbf{unclear} comments which we cannot confidently defined.
 
-\subsubsection{Conversion into vector}
+\subsection{Research Questions}
+To validate our approach, we addressed the following research questions:
 
-Finally, the tf--idf algorithm is used to convert each document into a vector.
+\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}\\
+\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
+Then, we used these comments for both training and test data set for our approach to determine an effectiveness of our approach.
+We also determined the robustness of our approach using cross validation.
+We randomly selected 90\% of 320 comments for training set and 10\% for test set.
+The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.
 
-\subsection{Training Data}
+Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
 
-We sampled 320 comments from the data set.
-These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
-This task is carried out by three people who worked independently.
+%We sampled 320 comments from the data set.
+%These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
+%This task is carried out by three people who worked independently.
+%
+%Each comment is then scored based on the number of positive answers.
+%For example, a comment with a score of 3 means that all three people said that it is useful,
+%while a comment with a score of 0 means that none of us marked it as useful.
 
-Each comment is then scored based on the number of positive answers.
-For example, a comment with a score of 3 means that all three people said that it is useful,
-while a comment with a score of 0 means that none of us marked it as useful.
+\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
+\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set.
+We then used these thresholds to classify the rest of comments.
+A statical analysis was performed to understand the impact of useful discussion to software quality.
+
+\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
+\indent
+
+%\subsection{Training Data}
 
@@
 
-\subsection{Model Generation and Validation}
+%\pick{I re-wrote of these, hope I don't miss something ;)}
+%\subsection{Model Generation and Validation}
+%
+%% the metrics
+%For each comment, we computed similarity and dissimilarity metrics
+%between the comment text and the corresponding commit message.
+%We chose cosine similarity and euclidean distance as the metrics to use in model generation.
+%
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=3in]{vector}
+%\caption{The similarity and distance metric that is being used.}
+%\label{fig:vector}
+%\end{figure}
+%
+%% assumptions in categorization
+%The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
+%and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
+%where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}
+%
+%% finding parameters
+%To find these parameters, a brute-force approach is used.
+%This is possible because the set of $similarity$ and $distance$ values are discrete.
+%Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.
+%
+%% validation
+%To validate our model, we randomly split the data into 10 parts.
+%9 parts are used for training, and 1 part for validation.
+%This process is repeated 300 times. % while I sleep
+%The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
+%to give the overall performance of our model.
 
-% the metrics
-For each comment, we computed similarity and dissimilarity metrics
-between the comment text and the corresponding commit message.
-We chose cosine similarity and euclidean distance as the metrics to use in model generation.
+\section{Case Study Results}
+\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
+Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.
+From 72,484 comments of 6,605 reviews with its commit messages extracted from raw data set, there are 10,670 (15\%) of comments are written by reviewers while 85\% of comments are automatically generated by Gerrit system and integration bots.
 
-\begin{figure}[h]
+\begin{table}[!h]
+\caption{A summary data sets and some statistics.}
 \centering
-\includegraphics[width=3in]{vector}
-\caption{The similarity and distance metric that is being used.}
-\label{fig:vector}
-\end{figure}
+\small
+\begin{tabular}{ccc}
+\hline
+& Total Number & Percentage \\ \hline \hline
+Commit Messages & 6,605 &  -  \\ \hline
+All Comments & 72,484& - \\ \hline
+Reviewers Messages & 10,670 & 15\% \\ \hline
+Automated Messages. & 61,814 & 85\% \\ \hline
 
-% assumptions in categorization
-The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
-and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
-where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}
+\end{tabular}
+\label{tb:datastatistic}
+\end{table}
 
-% finding parameters
-To find these parameters, a brute-force approach is used.
-This is possible because the set of $similarity$ and $distance$ values are discrete.
-Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.
+%\pick{I realize that your figure is better for the presentation :)}
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=3.2in]{filter}
+%\caption{The filtering process.}
+%\label{fig:filter}
+%\end{figure}
+%\subsection{Data Preparation}
+%\subsubsection{Data extraction}
+%
+%6,605 changes and 72,484 comments have been extracted from the raw dataset.
+%35\% of the comments are by the system or one of the bots, and are thus discarded.
+%
+%\subsubsection{Common pattern removal}
+%
+%By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
+%
+%Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
+%This probably means these comments solely contain automatically-generated text, and are thus discarded.
+%This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.
+%
+%\subsubsection{Tokenizing}
+%
+%After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
+%This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
+%
 
-% validation
-To validate our model, we randomly split the data into 10 parts.
-9 parts are used for training, and 1 part for validation.
-This process is repeated 300 times. % while I sleep
-The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
-to give the overall performance of our model.
+\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}
 
-\section{Results}
+From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
+To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}.
+\pick{We cannot brute force for every floating number.
+How did we calculate this?} Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
+\pick{I used dummy results.
+Please change it} \pick{What we got from this table?
+What information can we interpret?
+The threshold is slightly different?
+Is it good or bad?
+Please describes.}
 
-\subsection{Data Preparation}
+\textbf{Model Effectiveness.} Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
+The green area represents useful model $\Theta(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$ and the red area represents useless classification model $\Omega(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$.
+This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
+As shown in the figure, most of comments fall in green area is useful comments and very few useless comments fall in this area.
+Similarly, most of comments fall in red area is useless comments.
+However, some comments were not determined (in white area).
+From the example comment, it shows that these comments discussed on .....
+which did not contains any similar words.
+Moreover, the areas of these two models are overlap.
+Table \ref{tb:classify_number} summarizes the number of classification from this results.
+Interestingly, 87\% useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
+This is same as the results of useful class that most of them have \texttt{YES} = 2 and 3 voting scores
+This finding suggests that these unclear comments have something.....
 
-\begin{figure}[h]
+\begin{table}[h]
 \centering
-\includegraphics[width=3.2in]{filter}
-\caption{The filtering process.}
-\label{fig:filter}
-\end{figure}
+\small
+\caption{Number of comments classified by our approach against ground truth data }
+\begin{tabular}{ccccc}
+\hline
+& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
+Our&  Useless  & Unclear  & Unclear & Useful \\
+Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
+\hline \hline
+Useless & 69 & 23 & 7 & 6 \\
+Useful & 4 & 13 & 24 & 95 \\
+Overlap & 1 & 1 & 0 & 1 \\
+Undetermined & 12 & 24 & 20 & 20 \\
+\hline
+\end{tabular}
+\label{tb:classify_number}
+\end{table}
 
-\subsubsection{Data extraction}
+\begin{table*}[!t]
+\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{ccccccc}
+\hline
+Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
+\multirow{7}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
+& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
+& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline \hline
+\multirow{7}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
+& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
+& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline
+\end{tabular}
+\label{tb:thresholds}
+\end{table*}
 
-6,605 changes and 72,484 comments have been extracted from the raw dataset.
-35\% of the comments are by the system or one of the bots, and are thus discarded.
+\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
+for useful and useless classifications,
+we obtained an average F$_1$ score of 0.693 and 0.681,
+with standard deviation of 0.090 and 0.118, respectively.
+This indicates that we can use our approach to classify with confident of 69.8\%.
+\pick{Precision? Recall?}
 
-\subsubsection{Common pattern removal}
+According to the results, we can answer  RQ1 that \textit{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}
 
-By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
+%After we performed cross validation, we obtained the following result:
+%for positive and negative classifications,
+%we obtained an average F$_1$ score of 0.693 and 0.681,
+%with standard deviation of 0.090 and 0.118, respectively.
+%This indicates that we can use our approach to classify with confident of 69.8\%.
 
-Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
-This probably means these comments solely contain automatically-generated text, and are thus discarded.
-This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.
+%After the similarity and distance metrics have been calculated,
+%these metrics appear to be able to separate the useful comments from the non-useful ones,
+%as can be seen in Fig.\ref{fig:scatter}.
+%Note that many comments have a cosine similarity metric of 0.
+%This is because the comment text and the corresponding commit message has no word in comment.
 
-\subsubsection{Tokenizing}
-
-After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
-This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
-
-\subsection{Training Data}
-
-After the 320 sample comments have been labeled,
-they are scored based on the number of ``yes'' given to the sample.
-There were 87, 60, 51, and 122 comments with scores of 0, 1, 2, and 3, respectively.
-
-After the similarity and distance metrics have been calculated,
-these metrics appear to be able to separate the useful comments from the non-useful ones,
-as can be seen in Fig.\ref{fig:scatter}.
-Note that many comments have a cosine similarity metric of 0.
-This is because the comment text and the corresponding commit message has no word in comment.
-
-\begin{figure}[h]
+\begin{figure}[!t]
 \centering
-\includegraphics[width=3in]{scatter}
+\includegraphics[scale=0.55, trim=0 0 30 50, clip=true]{scatter_log}
 \caption{The similarity and distance plot of the training data.
@@
 
-\subsection{Model Generation}
+\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
+\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}
 
-% the criteria that were found
-From our training data,
-the following criteria have been obtained that maximizes the F$_1$ score:
+\pick{If there is high \% of useless messages, it means ineffective review, isn't it?}
 
-Criteria to find samples with score of 3 (``positive''):
-\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
-\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
+\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
 
-Criteria to find samples with score of 0 (``negative''):
-\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
-\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
+%\subsection{Model Generation}
 
-Note that these constant values can vary from project to project, and thus is not a universal constant.
-
-% run result
-
-Running our model against the training data gives us the result displayed in the following table.
-In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
-
-\begin{center}
-\begin{tabular}{|r|rrrr|}
-\hline
-& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
-\hline
-Negative & 69 & 23 & 7 & 6 \\
-Neither & 12 & 24 & 20 & 20 \\
-Overlap & 1 & 1 & 0 & 1 \\
-Positive & 4 & 13 & 24 & 95 \\
-\hline
-\end{tabular}
-\end{center}
-
-As expected, most comments classified as \emph{negative} have score of 0 and 1,
-while most \emph{positive} comments have score of 2 and 3.
-However, some comments in every score type were classified as \emph{neither}.
+%% the criteria that were found
+%From our training data,
+%the following criteria have been obtained that maximizes the F$_1$ score:
+%
+%Criteria to find samples with score of 3 (``positive''):
+%\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
+%\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
+%
+%Criteria to find samples with score of 0 (``negative''):
+%\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
+%\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
+%
+%Note that these constant values can vary from project to project, and thus is not a universal constant.
+%
+%% run result
+%
+%Running our model against the training data gives us the result displayed in the following table.
+%In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
+%
+%\begin{center}
+%\begin{tabular}{|r|rrrr|}
+%\hline
+%& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
+%\hline
+%Negative & 69 & 23 & 7 & 6 \\
+%Neither & 12 & 24 & 20 & 20 \\
+%Overlap & 1 & 1 & 0 & 1 \\
+%Positive & 4 & 13 & 24 & 95 \\
+%\hline
+%\end{tabular}
+%\end{center}
+%
+%As expected, most comments classified as \emph{negative} have score of 0 and 1,
+%while most \emph{positive} comments have score of 2 and 3.
+%However, some comments in every score type were classified as \emph{neither}.
+%
+%
 
 % cross validation result
-
-\subsection{Cross Validation}
-
-After we performed cross validation, we obtained the following result:
-for positive and negative classifications,
-we obtained an average F$_1$ score of 0.693 and 0.681,
-with standard deviation of 0.090 and 0.118, respectively.
 

### 2014-07-25 paper.tex
add section about binary classification

@@
 \centering
-\includegraphics[scale=0.55, trim=0 0 30 50, clip=true]{scatter_log}
+\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
 \caption{The similarity and distance plot of the training data.
@@
 % noisy data, and binary classification
-Our training data is very noisy because there are disagreements between our judgment of ``usefulness.''
+Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear.
 These samples cannot be classified as either useful or not useful.
 This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
-
-By removing the samples with scores of 1 and 2, leaving with 209 samples without disagreements, and performing 10-fold cross-validation, we received a much better average F$_1$ score of 0.896.
 
@@
 If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.
-
+%\subsection{Reasons of Classification}
 % reasons for classification as useful or not useful
@@
 
-% example of false positive and false negatives
+%\subsection{Binary Classification}
+
+By removing the samples with scores of 1 and 2 from our data set, leaving with 209 samples without disagreements, we can perform a binary classification, in which all comments will receive either a positive or negative score.
+By cross-validation using only samples in total agreement, we obtained a much better F$_1$ score of 0.896.
+
+We could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
+However, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=3in]{binary}
+\caption{The amount of comments by score classified by the binary classifier.}
+\label{fig:binary}
+\end{figure}
 

### 2014-07-25 paper.tex
change wording of the introductions a bit

@@
 \begin{document}
-\title{Title}
+\title{ {\Large Less than a week left, still without a}\\ Title}
 
@@
 Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-This method mainly intend to early identify defect before integrating changes.
+Its main intention is to early identify defects before integrating changes.
 Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
-A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can discuss to find defects by comments through code review tool or mailing list.
-Then, developers will fix their changes following those comments.
+The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
+Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
+Developers will then fix their changes following those comments.
+
 % the freeform style of modern code review
+Even though Modern Code Review has less process overhead, it can be less effective if not done properly.
+\TODO{explain about our methods}
 
@@
 Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-This method mainly intend to early identify defect before integrating changes.
+Its main intention is to early identify defects before integrating changes.
 Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
-A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can discuss to find defects by comments through code review tool or mailing list.
-Then, developers will fix their changes following those comments.
+The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
+Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
+Developers will then fix their changes following those comments.
 

### 2014-07-25 paper.tex
moved sections to different files

--- 2014-07-24 paper.tex
@@
 
-\begin{abstract}
-Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-This method mainly intend to early identify defect before integrating changes.
-Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and  put into software development regularly in both industrial and OSS projects.
-A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can discuss to find defects by comments through code review tool or mailing list.
-Then, developers will fix their changes following those comments.
-% the freeform style of modern code review
-
-% some comments are not technically contributing
-
-\begin{IEEEkeywords}
-Modern Code Review, Software Quality, Text Mining
-\end{IEEEkeywords}
-\end{abstract}
-
-\section{Introduction}
-Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-This method mainly intend to early identify defect before integrating changes.
-Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and  put into software development regularly in both industrial and OSS projects.
-A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can discuss to find defects by comments through code review tool or mailing list.
-Then, developers will fix their changes following those comments.
-
-As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
-However, very little research investigate that in MCR, how does a discussion for a proposed change impact to the software quality.
-Since most of the proposed change improvements are triggered from reviewer comments \cite{Beller}.
-It is possible that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
-To determine the impact of discussion in MCR, a manual classification is required as study of Beller et.
-al.
-\cite{Beller}.
-As a massive amount of changes and comments in MCR history\cite{Balachandran2013,Thongtanunam2014}, it is painstaking and time consuming to classify data sets to perform quantitative analysis.
-Moreover, the comments in MCR is unstructured natural text unlike a checklist in the formal inspection.
-%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
-\caption{An simplified version of MCR Process based on Gerrit system}
-\label{fig:process}
-\end{figure}
-
-In this paper, we present an approach to automatically classify the usefulness of comments.
-We define that the usefulness is a comment that contribute to improve the proposed changes.
-In our approach, we analyze the similarity between commit message of the proposed changes and their comments.
-Our key idea is that useful comments are likely to contain similar topic as the proposed changes.
-To do so, we use text mining techniques, Vector Space Model (VSM) to calculate similarity and use euclidian distance to calculate dissimilarity.
-We create our predictive model by estimating a set of similarity and dissimilarity values that best discriminate between a useful and useless comments using the prediction evaluations: Precision, Recall and F-measure.
-
-For our case study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process.
-Our case studied project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
-To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy.
-We also used our predictive model for the all set of comments to preliminary estimate quality of reviews.
-According to this, we address the following two research questions:
-
-\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
-\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
-\noindent \textbf{RQ3:} Is this a cost-efficient way to identify useful and useless comments?
-
-\noindent The main contribution of this paper are:
-\begin{itemize}
-\item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
-\item The experimental results show that our approach can classify comments with XX of F-measure.
-\item We found that XX\% of comments for each review are classified as useful comments, while XX \% of comments are classified as useless comments.
-\end{itemize} 
-%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.
-
-%Motivation Example.\thai{Wow}
-
-%\section{Background}
-%In this section, we describe MCR process based on Gerrit system.
-Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
-\section{Modern Code Review Process}
-
-An overview of MCR process based on Gerrit system is shown in Figure \ref{fig:process}.
-The grey area shows the review process of the system which composed of four main steps.
-(1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
-(2) reviewers examine the proposed code changes whether it contains defects or not.
-(3) reviewers will give comments where should the author improve the code change.
-The author will create a new change according to the comments then re-submit a new patch again.
-Then, reviewers will examine the new change.
-If there is still a needed improvement, reviewers will give comments to fix again.
-The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).
-
-According to this process, reviewers' comment is the most important for the software quality.
-McIntosh et.
-al.
-\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
-However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective.
-Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}.
-Our observation in Qt project also correspond this finding.
-We found some comments are superficial and unrelated to the proposed changes.
-For example, a superficial and unconfident reviewer as shown in Fig.
-\ref{fig:example}(a), a comment for rule of using Version Control System (e.g.
-Git) in the project Fig.
-\ref{fig:example}(b).
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
-\caption{Examples of comment in code reviews of Qt project.}
-\label{fig:example}
-\end{figure}
-
-\section{Reviewers' Comments Classification Approach}
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.35, trim = 50 90 0 30, clip=true]{overview2}
-\caption{Overview of our classification approach.}
-\label{fig:overview}
-\end{figure}
-
-Figure \ref{fig:overview} shows the overview of our proposed approach.
-We classify usefulness of comments by measuring similarity between commit message of proposed change and its comments.
-To calculate similarity in Fig.
-\ref{fig:overview}(a), we use Vector Space Model (VSM) which is well-known technique for retrieving similar documents written in unstructured natural language.
-We also use euclidian distance to calculate dissimilarity.
-For our training dataset, we manually identify every pair of comment and commit messages in Fig.
-\ref{fig:overview}(b).
-Then, we use the results from Fig.
-\ref{fig:overview}(a) and from Fig.
-\ref{fig:overview}(b) to estimate similarity and dissimilarity threshold that can best discriminate useful/useless comments.
-Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.
-
-To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
-\begin{itemize}
-\item $\Theta(c,S_T,D_T)$ predict as \textbf{useful} if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
-\item $\Omega(c,S'_T,D'_T)$ predict as \textbf{useles} if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
-\end{itemize}
-where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.
-The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review.
-The details our approach is described in the following subsections.
-\pick{Why we need two measurements?}
-\pick{What happen in model for otherwise?}
-
-\subsection{Similarity and Dissimilarity Calculation based on VSM}
-%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language.
-In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
-For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
-To do so, we use VSM which is a model for representing text documents as vectors.
-For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
-The $w_{t,d}$ value is TF-IDF weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
-
-\begin{equation}
-w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
-\label{eq:tf-idf}
-\end{equation}
-
-After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.
-
-\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product.
-Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}.
-The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.
-
-\begin{equation}
-\mathrm{sim}(m,c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
-\label{eq:cosine}
-\end{equation}
-
-\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}.
-We can use this distance as an dissimilarity.
-Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Euclidian distance using Equation \ref{eq:cosine}.
-The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.
-
-\begin{equation}
-\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
-\label{eq:euclid}
-\end{equation}
-
-\subsection{Estimating Similarity and Dissimilarity Threshold}
-We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$.
-This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall).
-This can be calculated using Equation \ref{eq:fmeasure}.
-
-\begin{equation}
-\begin{split}
-\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
-\\
-\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
-\\
-\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
-\end{split}
-\label{eq:fmeasure}
-\end{equation}
-
-Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful.
-To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments.
-For the correctness of prediction, we determine from the useful/useless defined dataset.
-
-%Using this method, we iteratively measure an accuracy for values of $s_t$ and $s'_t$ ranging $[0,1]$; and values of $d_t$ and $d'_t$ ranging $[0,\infty)$.
-
-%\begin{equation}
-%\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
-%\label{eq:precision}
-%\end{equation}
-
-%where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
-%According to this, we can formalize as follows:
-
-%\begin{equation}
-%(S_T,D_T) = \max(\{\mathrm{F\text{-}measure} \text{ of \textbf{useful}}(c,s_T,d_T) | s_T\in[0,1] \text{ and } d_T\in [0,\infty) \})
-%\end{equation}
-
-\section{Case Study Design}
-
-We used the review history of Qt project from Gerrit code review tool provided by Hamasaki et.
-al.
-\cite{Hamasaki2013}.
-Qt project is a large open source project composed of small subsystems.
-For our case study, we selected the most active subproject \texttt{qtbase} project.
-From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.
-
-% where we got the data
-%We used the review data sets of the Qt project collected by Hamasaki et al\cite{Hamasaki2013}.
-%Only reviews in the master branch of \texttt{qtbase} project are considered,
-%as it is the most active branch.
-
-% quick structure
-%\pick{This already explain in background :D}
-%Each change includes a \emph{commit message} which describes what is changed.
-%After a change is submitted to Gerrit, reviewers can give scores to it.
-%The scores will determine whether the change will be accepted or not.
-%Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
-%Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.
-
-% overview
-%In our classification method,
-%all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
-%Few comments are sampled and then classified manually for use in training and validation.
-%A model is created from these training data, from which useful comments can automatically be identified.
-%This process is illustrated in Fig.\ref{fig:overview}.
-%
-
-\subsection{Data Preparation}
-We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we firstly processed the commit message and comments as follows:
-
-\subsubsection{Automatically generated messages removal}
-In Gerrit, the comments are composed of comment messages from reviewers and automated messages.
-These automatic messages are generated by Gerrit and integration system to record activities, for example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}.
-Since these messages are not impact to software quality\cite{Mcintosh}, we removed them from our data set.
-We identified these automatic messages using regular expression and selecting frequently appeared pattern of messages.
-
-%The commit messages and all comment texts are converted into vectors as part of the preparation step.
-%Fig. \ref{fig:preprocess} illustrates the overview of this step.
-%We wrote scripts in Ruby language to perform these tasks.
-
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=3in]{preprocess}
-%\caption{The data preparation process.
-%Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
-%and are converted into a vector.}
-%\label{fig:preprocess}
-%\end{figure}
-
-%\subsubsection{Removal of automatically generated text}
-%
-%First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.
-%
-%% conversion into vector, wow
-%Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
-%This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
-%This effectively removed the ID numbers and other non-generic terms.
-%
-%Next, the lines that appears most frequently are identified.
-%From these lines, we then constructed the regular expression patterns,
-%and finally, these patterns are used to filter out automatically generated text from our data.
-
-\subsubsection{Data Preprocessing}
- we extracted semantic words commit messages and comment messages before converting to vector.
-For each message, we removed all punctuation signs, digits, and common words (e.g.
-a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}.
-We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.
-
-%After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
-%Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
-%The stemming is performed on remaining tokens using Porter stemming algorithm.
-%The remaining words are then combined to form a corpus of all used words.
-
-%\subsubsection{Conversion into vector}
-%
-%Finally, the tf--idf algorithm is used to convert each document into a vector.
-
-\subsubsection{Ground-Truth Data Preparation}
-To prepare ground-truth data, we read comments and manually identified useful and useless comments.
-In this study, we use three people (the first two authors and one student) independently classify comments by giving a question that ``Does this comment technically contribute to its change or not?''.
-Then, the readers gave a vote for \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.
-From the voting scores, we regarded that the comments with three \texttt{YES} votes are \textbf{useful} comments and the comments with no \texttt{YES} votes (i.e.
-three \texttt{NO} votes) are \textbf{useless} comments.
-For the comments with one and two \texttt{YES}' votes, we remained them as \textbf{unclear} comments which we cannot confidently defined.
-
-\subsection{Research Questions}
-To validate our approach, we addressed the following research questions:
-
-\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}\\
-\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
-Then, we used these comments for both training and test data set for our approach to determine an effectiveness of our approach.
-We also determined the robustness of our approach using cross validation.
-We randomly selected 90\% of 320 comments for training set and 10\% for test set.
-The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.
-
-Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
-
-%We sampled 320 comments from the data set.
-%These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
-%This task is carried out by three people who worked independently.
-%
-%Each comment is then scored based on the number of positive answers.
-%For example, a comment with a score of 3 means that all three people said that it is useful,
-%while a comment with a score of 0 means that none of us marked it as useful.
-
-\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
-\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set.
-We then used these thresholds to classify the rest of comments.
-A statical analysis was performed to understand the impact of useful discussion to software quality.
-
-\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
-\indent
-
-%\subsection{Training Data}
-
-%The score of a comment can be defined as:
-
-%\begin{align*}
-%Score_i & = \sum_{\text{reviewer } r} Review(r, i). \\
-%Review(r, i) & = \begin{cases}
-%	1 & \text{if } r \text{ says that the comment } i \text{ is useful,} \\
-%	0 & \text{otherwise.}
-%\end{cases}
-%\end{align*}
-
-%\pick{I re-wrote of these, hope I don't miss something ;)}
-%\subsection{Model Generation and Validation}
-%
-%% the metrics
-%For each comment, we computed similarity and dissimilarity metrics
-%between the comment text and the corresponding commit message.
-%We chose cosine similarity and euclidean distance as the metrics to use in model generation.
-%
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=3in]{vector}
-%\caption{The similarity and distance metric that is being used.}
-%\label{fig:vector}
-%\end{figure}
-%
-%% assumptions in categorization
-%The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
-%and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
-%where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}
-%
-%% finding parameters
-%To find these parameters, a brute-force approach is used.
-%This is possible because the set of $similarity$ and $distance$ values are discrete.
-%Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.
-%
-%% validation
-%To validate our model, we randomly split the data into 10 parts.
-%9 parts are used for training, and 1 part for validation.
-%This process is repeated 300 times. % while I sleep
-%The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
-%to give the overall performance of our model.
-
-\section{Case Study Results}
-\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
-Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.
-From 72,484 comments of 6,605 reviews with its commit messages extracted from raw data set, there are 10,670 (15\%) of comments are written by reviewers while 85\% of comments are automatically generated by Gerrit system and integration bots.
-
-\begin{table}[!h]
-\caption{A summary data sets and some statistics.}
-\centering
-\small
-\begin{tabular}{ccc}
-\hline
-& Total Number & Percentage \\ \hline \hline
-Commit Messages & 6,605 &  -  \\ \hline
-All Comments & 72,484& - \\ \hline
-Reviewers Messages & 10,670 & 15\% \\ \hline
-Automated Messages. & 61,814 & 85\% \\ \hline
-
-\end{tabular}
-\label{tb:datastatistic}
-\end{table}
-
-%\pick{I realize that your figure is better for the presentation :)}
-%\begin{figure}[h]
-%\centering
-%\includegraphics[width=3.2in]{filter}
-%\caption{The filtering process.}
-%\label{fig:filter}
-%\end{figure}
-%\subsection{Data Preparation}
-%\subsubsection{Data extraction}
-%
-%6,605 changes and 72,484 comments have been extracted from the raw dataset.
-%35\% of the comments are by the system or one of the bots, and are thus discarded.
-%
-%\subsubsection{Common pattern removal}
-%
-%By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
-%
-%Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
-%This probably means these comments solely contain automatically-generated text, and are thus discarded.
-%This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.
-%
-%\subsubsection{Tokenizing}
-%
-%After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
-%This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
-%
-
-\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}
-
-From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}.
-\pick{We cannot brute force for every floating number.
-How did we calculate this?} Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
-\pick{I used dummy results.
-Please change it} \pick{What we got from this table?
-What information can we interpret?
-The threshold is slightly different?
-Is it good or bad?
-Please describes.}
-
-\textbf{Model Effectiveness.} Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
-The green area represents useful model $\Theta(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$ and the red area represents useless classification model $\Omega(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$.
-This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
-As shown in the figure, most of comments fall in green area is useful comments and very few useless comments fall in this area.
-Similarly, most of comments fall in red area is useless comments.
-However, some comments were not determined (in white area).
-From the example comment, it shows that these comments discussed on .....
-which did not contains any similar words.
-Moreover, the areas of these two models are overlap.
-Table \ref{tb:classify_number} summarizes the number of classification from this results.
-Interestingly, 87\% useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
-This is same as the results of useful class that most of them have \texttt{YES} = 2 and 3 voting scores
-This finding suggests that these unclear comments have something.....
-
-\begin{table}[h]
-\centering
-\small
-\caption{Number of comments classified by our approach against ground truth data }
-\begin{tabular}{ccccc}
-\hline
-& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
-Our&  Useless  & Unclear  & Unclear & Useful \\
-Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
-\hline \hline
-Useless & 69 & 23 & 7 & 6 \\
-Useful & 4 & 13 & 24 & 95 \\
-Overlap & 1 & 1 & 0 & 1 \\
-Undetermined & 12 & 24 & 20 & 20 \\
-\hline
-\end{tabular}
-\label{tb:classify_number}
-\end{table}
-
-\begin{table*}[!t]
-\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
-\hline
-Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
-\multirow{7}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
-& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
-& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline \hline
-\multirow{7}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
-& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
-& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline
-\end{tabular}
-\label{tb:thresholds}
-\end{table*}
-
-\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
-for useful and useless classifications,
-we obtained an average F$_1$ score of 0.693 and 0.681,
-with standard deviation of 0.090 and 0.118, respectively.
-This indicates that we can use our approach to classify with confident of 69.8\%.
-\pick{Precision? Recall?}
-
-According to the results, we can answer  RQ1 that \textit{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}
-
-%After we performed cross validation, we obtained the following result:
-%for positive and negative classifications,
-%we obtained an average F$_1$ score of 0.693 and 0.681,
-%with standard deviation of 0.090 and 0.118, respectively.
-%This indicates that we can use our approach to classify with confident of 69.8\%.
-
-%After the similarity and distance metrics have been calculated,
-%these metrics appear to be able to separate the useful comments from the non-useful ones,
-%as can be seen in Fig.\ref{fig:scatter}.
-%Note that many comments have a cosine similarity metric of 0.
-%This is because the comment text and the corresponding commit message has no word in comment.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.55, trim=0 0 30 50, clip=true]{scatter_log}
-\caption{The similarity and distance plot of the training data.
-The symbol represents the score, which ranges from 0 to 3.}
-\label{fig:scatter}
-\end{figure}
-
-\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
-\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}
-
-\pick{If there is high \% of useless messages, it means ineffective review, isn't it?}
-
-\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
-
-%\subsection{Model Generation}
-
-%% the criteria that were found
-%From our training data,
-%the following criteria have been obtained that maximizes the F$_1$ score:
-%
-%Criteria to find samples with score of 3 (``positive''):
-%\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
-%\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
-%
-%Criteria to find samples with score of 0 (``negative''):
-%\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
-%\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
-%
-%Note that these constant values can vary from project to project, and thus is not a universal constant.
-%
-%% run result
-%
-%Running our model against the training data gives us the result displayed in the following table.
-%In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
-%
-%\begin{center}
-%\begin{tabular}{|r|rrrr|}
-%\hline
-%& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
-%\hline
-%Negative & 69 & 23 & 7 & 6 \\
-%Neither & 12 & 24 & 20 & 20 \\
-%Overlap & 1 & 1 & 0 & 1 \\
-%Positive & 4 & 13 & 24 & 95 \\
-%\hline
-%\end{tabular}
-%\end{center}
-%
-%As expected, most comments classified as \emph{negative} have score of 0 and 1,
-%while most \emph{positive} comments have score of 2 and 3.
-%However, some comments in every score type were classified as \emph{neither}.
-%
-%
-
-% cross validation result
-
-\section{Discussion}
-
-% noisy data, and binary classification
-Our training data is very noisy because there are disagreements between our judgment of ``usefulness.''
-These samples cannot be classified as either useful or not useful.
-This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
-
-By removing the samples with scores of 1 and 2, leaving with 209 samples without disagreements, and performing 10-fold cross-validation, we received a much better average F$_1$ score of 0.896.
-
-% tuning the F score for precision and recall
-Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
-For instance, if we wanted to measure the amount of useful comments within a large dataset, we can give more weight to precision, sacrificing some good comments.
-If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.
-
-% reasons for classification as useful or not useful
-During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
-
-\begin{itemize}
-	\item they contain new information;
-	\item they contain constructive suggestions;
-	\item they discuss directly about the change; and
-	\item they discuss technical matters.
-\end{itemize}
-
-Examples of reasons for negative comments include:
-
-\begin{itemize}
-	\item chatting (i.e. no new information, just communication);
-	\item not discussing directly about the change;
-	\item discussing about the process workflow; and
-	\item discussing about Git or Gerrit itself.
-\end{itemize}
-
-% example of false positive and false negatives
+\input{sections/abstract}
+\input{sections/introduction}
+\input{sections/background}
+\input{sections/methods}
+\input{sections/results}
+\input{sections/discussion}
 

### 2014-07-25 sections/abstract.tex
moved sections to different files

% !TEX root = ../paper.tex

\begin{abstract}
Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
Its main intention is to early identify defects before integrating changes.
Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
Developers will then fix their changes following those comments.

% the freeform style of modern code review
Even though Modern Code Review has less process overhead, it can be less effective if not done properly.
\TODO{explain about our methods}

% some comments are not technically contributing

\begin{IEEEkeywords}
Modern Code Review, Software Quality, Text Mining
\end{IEEEkeywords}
\end{abstract}

### 2014-07-25 sections/background.tex
moved sections to different files

% !TEX root = ../paper.tex

%\section{Background}
%In this section, we describe MCR process based on Gerrit system. Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques. 
\section{Modern Code Review Process}

An overview of MCR process based on Gerrit system is shown in Figure \ref{fig:process}. The grey area shows the review process of the system which composed of four main steps. (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system. (2) reviewers examine the proposed code changes whether it contains defects or not. (3) reviewers will give comments where should the author improve the code change. The author will create a new change according to the comments then re-submit a new patch again. Then, reviewers will examine the new change. If there is still a needed improvement, reviewers will give comments to fix again. The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).

According to this process, reviewers' comment is the most important for the software quality. McIntosh et. al. \cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs. However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective. Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}. Our observation in Qt project also correspond this finding. We found some comments are superficial and unrelated to the proposed changes. For example, a superficial and unconfident reviewer as shown in Fig. \ref{fig:example}(a), a comment for rule of using Version Control System (e.g. Git) in the project Fig. \ref{fig:example}(b).

\begin{figure}[!t]
\centering
\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
\caption{Examples of comment in code reviews of Qt project.}
\label{fig:example}
\end{figure}

\section{Reviewers' Comments Classification Approach}
\begin{figure}[!t]
\centering
\includegraphics[scale=0.35, trim = 50 90 0 30, clip=true]{overview2}
\caption{Overview of our classification approach.}
\label{fig:overview}
\end{figure}

Figure \ref{fig:overview} shows the overview of our proposed approach. We classify usefulness of comments by measuring similarity between commit message of proposed change and its comments. To calculate similarity in Fig. \ref{fig:overview}(a), we use Vector Space Model (VSM) which is well-known technique for retrieving similar documents written in unstructured natural language. We also use euclidian distance to calculate dissimilarity. For our training dataset, we manually identify every pair of comment and commit messages in Fig. \ref{fig:overview}(b). Then, we use the results from Fig. \ref{fig:overview}(a) and from Fig. \ref{fig:overview}(b) to estimate similarity and dissimilarity threshold that can best discriminate useful/useless comments. Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.

To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
\begin{itemize}
\item $\Theta(c,S_T,D_T)$ predict as \textbf{useful} if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
\item $\Omega(c,S'_T,D'_T)$ predict as \textbf{useles} if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
\end{itemize}
where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification. The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review. The details our approach is described in the following subsections.
\pick{Why we need two measurements?}
\pick{What happen in model for otherwise?}

\subsection{Similarity and Dissimilarity Calculation based on VSM}
%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language. In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
To do so, we use VSM which is a model for representing text documents as vectors. For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$. The $w_{t,d}$ value is TF-IDF weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.

\begin{equation}
w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
\label{eq:tf-idf}
\end{equation}

After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.

\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product. Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}. The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.

\begin{equation}
\mathrm{sim}(m,c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
\label{eq:cosine}
\end{equation}

\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}. We can use this distance as an dissimilarity. Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Euclidian distance using Equation \ref{eq:cosine}. The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.

\begin{equation}
\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
\label{eq:euclid}
\end{equation}

\subsection{Estimating Similarity and Dissimilarity Threshold}
We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$. This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall). This can be calculated using Equation \ref{eq:fmeasure}.

\begin{equation}
\begin{split}
\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
\\
\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
\\
\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
\end{split}
\label{eq:fmeasure}
\end{equation}

Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful. To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments. For the correctness of prediction, we determine from the useful/useless defined dataset.

%Using this method, we iteratively measure an accuracy for values of $s_t$ and $s'_t$ ranging $[0,1]$; and values of $d_t$ and $d'_t$ ranging $[0,\infty)$.

%\begin{equation}
%\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
%\label{eq:precision}
%\end{equation}

%where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
%According to this, we can formalize as follows:

%\begin{equation}
%(S_T,D_T) = \max(\{\mathrm{F\text{-}measure} \text{ of \textbf{useful}}(c,s_T,d_T) | s_T\in[0,1] \text{ and } d_T\in [0,\infty) \})
%\end{equation}

### 2014-07-25 sections/introduction.tex
moved sections to different files

% !TEX root = ../paper.tex

\section{Introduction}
Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
Its main intention is to early identify defects before integrating changes.
Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
Developers will then fix their changes following those comments.

As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}. However, very little research investigate that in MCR, how does a discussion for a proposed change impact to the software quality. Since most of the proposed change improvements are triggered from reviewer comments \cite{Beller}. 
It is possible that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
To determine the impact of discussion in MCR, a manual classification is required as study of Beller et. al. \cite{Beller}. As a massive amount of changes and comments in MCR history\cite{Balachandran2013,Thongtanunam2014}, it is painstaking and time consuming to classify data sets to perform quantitative analysis. Moreover, the comments in MCR is unstructured natural text unlike a checklist in the formal inspection. 
%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
\begin{figure}[!t]
\centering
\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
\caption{An simplified version of MCR Process based on Gerrit system}
\label{fig:process}
\end{figure}

In this paper, we present an approach to automatically classify the usefulness of comments. We define that the usefulness is a comment that contribute to improve the proposed changes. In our approach, we analyze the similarity between commit message of the proposed changes and their comments. Our key idea is that useful comments are likely to contain similar topic as the proposed changes. To do so, we use text mining techniques, Vector Space Model (VSM) to calculate similarity and use euclidian distance to calculate dissimilarity. 
We create our predictive model by estimating a set of similarity and dissimilarity values that best discriminate between a useful and useless comments using the prediction evaluations: Precision, Recall and F-measure.

For our case study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process. Our case studied project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation. To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy. We also used our predictive model for the all set of comments to preliminary estimate quality of reviews. According to this, we address the following two research questions:

\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
\noindent \textbf{RQ3:} Is this a cost-efficient way to identify useful and useless comments?

\noindent The main contribution of this paper are:
\begin{itemize}
\item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
\item The experimental results show that our approach can classify comments with XX of F-measure.
\item We found that XX\% of comments for each review are classified as useful comments, while XX \% of comments are classified as useless comments.
\end{itemize} 
%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

### 2014-07-25 sections/methods.tex
moved sections to different files

% !TEX root = ../paper.tex

\section{Case Study Design}

We used the review history of Qt project from Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of small subsystems. For our case study, we selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

% where we got the data
%We used the review data sets of the Qt project collected by Hamasaki et al\cite{Hamasaki2013}.
%Only reviews in the master branch of \texttt{qtbase} project are considered,
%as it is the most active branch.

% quick structure
%\pick{This already explain in background :D}
%Each change includes a \emph{commit message} which describes what is changed.
%After a change is submitted to Gerrit, reviewers can give scores to it.
%The scores will determine whether the change will be accepted or not.
%Reviewers can also add comments to the change, which may optionally be added to a specific line of code inside a changed file.
%Majority of the comments are automatically generated by Gerrit and do not contain any user-written text.

% overview
%In our classification method,
%all commit messages and comments that are human-written are converted into vectors using tf--idf algorithm.
%Few comments are sampled and then classified manually for use in training and validation.
%A model is created from these training data, from which useful comments can automatically be identified.
%This process is illustrated in Fig.\ref{fig:overview}.
%

\subsection{Data Preparation}
We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we firstly processed the commit message and comments as follows:

\subsubsection{Automatically generated messages removal}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and integration system to record activities, for example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are not impact to software quality\cite{Mcintosh}, we removed them from our data set. We identified these automatic messages using regular expression and selecting frequently appeared pattern of messages.

%The commit messages and all comment texts are converted into vectors as part of the preparation step.
%Fig. \ref{fig:preprocess} illustrates the overview of this step.
%We wrote scripts in Ruby language to perform these tasks.

%\begin{figure}[h]
%\centering
%\includegraphics[width=3in]{preprocess}
%\caption{The data preparation process.
%Automatically generated texts are removed, remaining text is tokenized, stop words are removed, remaining tokens are stemmed,
%and are converted into a vector.}
%\label{fig:preprocess}
%\end{figure}

%\subsubsection{Removal of automatically generated text}
%
%First, all comments by the Gerrit system, \emph{Qt Sanity Bot}, and \emph{Qt Continuous Integration System} are skipped.
%
%% conversion into vector, wow
%Next, we looked for common patterns that appeared in the comments, because it is very likely that they are automatically generated.
%This is accomplished by splitting texts into lines, and for each line, searching for words that can be found in the English wordlist\footnote{The wordlist found in \texttt{/usr/share/dict/words} from Ubuntu Linux distribution is used.}.
%This effectively removed the ID numbers and other non-generic terms.
%
%Next, the lines that appears most frequently are identified.
%From these lines, we then constructed the regular expression patterns,
%and finally, these patterns are used to filter out automatically generated text from our data.

\subsubsection{Data Preprocessing}
 we extracted semantic words commit messages and comment messages before converting to vector. For each message, we removed all punctuation signs, digits, and common words (e.g. a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}. We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.

%After the automatically generated messages are removed, we extracted the words in each document into a list of tokens by searching for alphanumeric characters including apostrophes.
%Stop words from the Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}} are then removed.
%The stemming is performed on remaining tokens using Porter stemming algorithm.
%The remaining words are then combined to form a corpus of all used words.

%\subsubsection{Conversion into vector}
%
%Finally, the tf--idf algorithm is used to convert each document into a vector.

\subsubsection{Ground-Truth Data Preparation}
To prepare ground-truth data, we read comments and manually identified useful and useless comments. In this study, we use three people (the first two authors and one student) independently classify comments by giving a question that ``Does this comment technically contribute to its change or not?''. Then, the readers gave a vote for \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless. From the voting scores, we regarded that the comments with three \texttt{YES} votes are \textbf{useful} comments and the comments with no \texttt{YES} votes (i.e. three \texttt{NO} votes) are \textbf{useless} comments. For the comments with one and two \texttt{YES}' votes, we remained them as \textbf{unclear} comments which we cannot confidently defined.

\subsection{Research Questions}
To validate our approach, we addressed the following research questions:

\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}\\
\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection. Then, we used these comments for both training and test data set for our approach to determine an effectiveness of our approach. We also determined the robustness of our approach using cross validation. We randomly selected 90\% of 320 comments for training set and 10\% for test set.
The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.

Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).

%We sampled 320 comments from the data set.
%These samples are then classified as either useful (that is, technically contributing to the software) or not useful.
%This task is carried out by three people who worked independently.
%
%Each comment is then scored based on the number of positive answers.
%For example, a comment with a score of 3 means that all three people said that it is useful,
%while a comment with a score of 0 means that none of us marked it as useful.

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set. We then used these thresholds to classify the rest of comments. A statical analysis was performed to understand the impact of useful discussion to software quality.

\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
\indent

%\subsection{Training Data}

%The score of a comment can be defined as:

%\begin{align*}
%Score_i & = \sum_{\text{reviewer } r} Review(r, i). \\
%Review(r, i) & = \begin{cases}
%	1 & \text{if } r \text{ says that the comment } i \text{ is useful,} \\
%	0 & \text{otherwise.}
%\end{cases}
%\end{align*}

%\pick{I re-wrote of these, hope I don't miss something ;)}
%\subsection{Model Generation and Validation}
%
%% the metrics
%For each comment, we computed similarity and dissimilarity metrics
%between the comment text and the corresponding commit message.
%We chose cosine similarity and euclidean distance as the metrics to use in model generation.
%
%\begin{figure}[h]
%\centering
%\includegraphics[width=3in]{vector}
%\caption{The similarity and distance metric that is being used.}
%\label{fig:vector}
%\end{figure}
%
%% assumptions in categorization
%The model is based on two assumptions: that useful comments will have a $similarity \geq A \text{ and } distance \leq B$,
%and that comments that are not useful will have a $ similarity \leq C \text{ and } distance \geq D$,
%where $A$, $B$, $C$, and $D$ are some constant.\footnote{We also tried using the `or' operator, and found that using `and' produces better result.}
%
%% finding parameters
%To find these parameters, a brute-force approach is used.
%This is possible because the set of $similarity$ and $distance$ values are discrete.
%Each possible value of $A$, $B$, $C$, and $D$ are evaluated to find the constant that returns the maximum F$_1$ score.
%
%% validation
%To validate our model, we randomly split the data into 10 parts.
%9 parts are used for training, and 1 part for validation.
%This process is repeated 300 times. % while I sleep
%The values of precision, recall, F$_1$ score, and accuracy are recorded and then averaged
%to give the overall performance of our model.

### 2014-07-25 sections/results.tex
moved sections to different files

% !TEX root = ../paper.tex

\section{Case Study Results}
\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.
From 72,484 comments of 6,605 reviews with its commit messages extracted from raw data set, there are 10,670 (15\%) of comments are written by reviewers while 85\% of comments are automatically generated by Gerrit system and integration bots.

\begin{table}[!h]
\caption{A summary data sets and some statistics.}
\centering
\small
\begin{tabular}{ccc}
\hline
& Total Number & Percentage \\ \hline \hline
Commit Messages & 6,605 &  -  \\ \hline
All Comments & 72,484& - \\ \hline
Reviewers Messages & 10,670 & 15\% \\ \hline
Automated Messages. & 61,814 & 85\% \\ \hline

\end{tabular}
\label{tb:datastatistic}
\end{table}

%\pick{I realize that your figure is better for the presentation :)}
%\begin{figure}[h]
%\centering
%\includegraphics[width=3.2in]{filter}
%\caption{The filtering process.}
%\label{fig:filter}
%\end{figure}
%\subsection{Data Preparation}
%\subsubsection{Data extraction}
%
%6,605 changes and 72,484 comments have been extracted from the raw dataset.
%35\% of the comments are by the system or one of the bots, and are thus discarded.
%
%\subsubsection{Common pattern removal}
%
%By looking for most frequent lines, common patterns were found, such as \emph{`Uploaded patch set 2.'} and \emph{`Change has been successfully cherry-picked to the staging branch as \dots'}.
%
%Removing occurrences of these patterns leaves 77\% of the remaining comments empty.
%This probably means these comments solely contain automatically-generated text, and are thus discarded.
%This leaves us with 10,670 comments and 6,605 commit messages; a total of 17,275 documents.
%
%\subsubsection{Tokenizing}
%
%After the tokenization step, 393,238 tokens are generated in total. They are composed of 20,025 different words.
%This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
%

\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}

From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}. \pick{We cannot brute force for every floating number. How did we calculate this?} Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score. \pick{I used dummy results. Please change it} \pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

\textbf{Model Effectiveness.} Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds. The green area represents useful model $\Theta(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$ and the red area represents useless classification model $\Omega(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$. This figure also shows an example comment that fall in the different area\pick{Didn't put yet}. As shown in the figure, most of comments fall in green area is useful comments and very few useless comments fall in this area. Similarly, most of comments fall in red area is useless comments. However, some comments were not determined (in white area). From the example comment, it shows that these comments discussed on ..... which did not contains any similar words. Moreover, the areas of these two models are overlap. Table \ref{tb:classify_number} summarizes the number of classification from this results. Interestingly, 87\% useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores. This is same as the results of useful class that most of them have \texttt{YES} = 2 and 3 voting scores
This finding suggests that these unclear comments have something.....

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data }
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useless & 69 & 23 & 7 & 6 \\
Useful & 4 & 13 & 24 & 95 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 20 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

\begin{table*}[!t]
\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
\multirow{7}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline \hline
\multirow{7}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline
\end{tabular}
\label{tb:thresholds}
\end{table*}

\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
for useful and useless classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.
This indicates that we can use our approach to classify with confident of 69.8\%.
\pick{Precision? Recall?}

According to the results, we can answer  RQ1 that \textit{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}

%After we performed cross validation, we obtained the following result:
%for positive and negative classifications,
%we obtained an average F$_1$ score of 0.693 and 0.681,
%with standard deviation of 0.090 and 0.118, respectively.
%This indicates that we can use our approach to classify with confident of 69.8\%.

%After the similarity and distance metrics have been calculated,
%these metrics appear to be able to separate the useful comments from the non-useful ones,
%as can be seen in Fig.\ref{fig:scatter}.
%Note that many comments have a cosine similarity metric of 0.
%This is because the comment text and the corresponding commit message has no word in comment.

\begin{figure}[!t]
\centering
\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
\caption{The similarity and distance plot of the training data.
The symbol represents the score, which ranges from 0 to 3.}
\label{fig:scatter}
\end{figure}

\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}

\pick{If there is high \% of useless messages, it means ineffective review, isn't it?}

\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\

%\subsection{Model Generation}

%% the criteria that were found
%From our training data,
%the following criteria have been obtained that maximizes the F$_1$ score:
%
%Criteria to find samples with score of 3 (``positive''):
%\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
%\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
%
%Criteria to find samples with score of 0 (``negative''):
%\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
%\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
%
%Note that these constant values can vary from project to project, and thus is not a universal constant.
%
%% run result
%
%Running our model against the training data gives us the result displayed in the following table.
%In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
%
%\begin{center}
%\begin{tabular}{|r|rrrr|}
%\hline
%& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
%\hline
%Negative & 69 & 23 & 7 & 6 \\
%Neither & 12 & 24 & 20 & 20 \\
%Overlap & 1 & 1 & 0 & 1 \\
%Positive & 4 & 13 & 24 & 95 \\
%\hline
%\end{tabular}
%\end{center}
%
%As expected, most comments classified as \emph{negative} have score of 0 and 1,
%while most \emph{positive} comments have score of 2 and 3.
%However, some comments in every score type were classified as \emph{neither}.
%
%

% cross validation result

### 2014-07-25 sections/introduction.tex
add \url

@@
 
-For our case study, we used a review history of Gerrit\footnote{https://code.google.com/p/gerrit/} system which is tool for supporting MCR process.
-Our case studied project is Qt\footnote{http://qt-project.org/}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
+For our case study, we used a review history of Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system which is tool for supporting MCR process.
+Our case studied project is Qt\footnote{\url{http://qt-project.org/}}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
 To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy.

### 2014-07-25 sections/introduction.tex
added numbers of results

@@
 \item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
-\item The experimental results show that our approach can classify comments with XX of F-measure.
-\item We found that XX\% of comments for each review are classified as useful comments, while XX \% of comments are classified as useless comments.
+\item The experimental results show that our approach can classify comments with an F$_1$ score of 0.681 and 0.693.
+\item We found that 85\% of comments in Gerrit are automatically generated.
+In the remaining 15\%, about 43\% of them are classified as useful, while about 34\% are classified as not useful comments.
+The remaining 23\% cannot be clearly classified.
 \end{itemize} 

### 2014-07-25 sections/approach.tex
move out the approach section

--- 2014-07-25 sections/background.tex
@@
-% !TEX root = ../paper.tex
-
-%\section{Background}
-%In this section, we describe MCR process based on Gerrit system.
-Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
-\section{Modern Code Review Process}
-
-An overview of MCR process based on Gerrit system is shown in Figure \ref{fig:process}.
-The grey area shows the review process of the system which composed of four main steps.
-(1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
-(2) reviewers examine the proposed code changes whether it contains defects or not.
-(3) reviewers will give comments where should the author improve the code change.
-The author will create a new change according to the comments then re-submit a new patch again.
-Then, reviewers will examine the new change.
-If there is still a needed improvement, reviewers will give comments to fix again.
-The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).
-
-According to this process, reviewers' comment is the most important for the software quality.
-McIntosh et.
-al.
-\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
-However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective.
-Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}.
-Our observation in Qt project also correspond this finding.
-We found some comments are superficial and unrelated to the proposed changes.
-For example, a superficial and unconfident reviewer as shown in Fig.
-\ref{fig:example}(a), a comment for rule of using Version Control System (e.g.
-Git) in the project Fig.
-\ref{fig:example}(b).
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
-\caption{Examples of comment in code reviews of Qt project.}
-\label{fig:example}
-\end{figure}
-
 \section{Reviewers' Comments Classification Approach}
@@
 
-Figure \ref{fig:overview} shows the overview of our proposed approach.
+Fig.
+\ref{fig:overview} shows the overview of our proposed approach.
 We classify usefulness of comments by measuring similarity between commit message of proposed change and its comments.

### 2014-07-25 sections/background.tex
used Fig. instead of Figure, following IEEE conventions
move out the approach section

@@
 
-An overview of MCR process based on Gerrit system is shown in Figure \ref{fig:process}.
+An overview of MCR process based on Gerrit system is shown in Fig.
+\ref{fig:process}.
 The grey area shows the review process of the system which composed of four main steps.
@@
 \end{figure}
-
-\section{Reviewers' Comments Classification Approach}
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.35, trim = 50 90 0 30, clip=true]{overview2}
-\caption{Overview of our classification approach.}
-\label{fig:overview}
-\end{figure}
-
-Figure \ref{fig:overview} shows the overview of our proposed approach.
-We classify usefulness of comments by measuring similarity between commit message of proposed change and its comments.
-To calculate similarity in Fig.
-\ref{fig:overview}(a), we use Vector Space Model (VSM) which is well-known technique for retrieving similar documents written in unstructured natural language.
-We also use euclidian distance to calculate dissimilarity.
-For our training dataset, we manually identify every pair of comment and commit messages in Fig.
-\ref{fig:overview}(b).
-Then, we use the results from Fig.
-\ref{fig:overview}(a) and from Fig.
-\ref{fig:overview}(b) to estimate similarity and dissimilarity threshold that can best discriminate useful/useless comments.
-Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.
-
-To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
-\begin{itemize}
-\item $\Theta(c,S_T,D_T)$ predict as \textbf{useful} if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
-\item $\Omega(c,S'_T,D'_T)$ predict as \textbf{useles} if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
-\end{itemize}
-where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.
-The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review.
-The details our approach is described in the following subsections.
-\pick{Why we need two measurements?}
-\pick{What happen in model for otherwise?}
-
-\subsection{Similarity and Dissimilarity Calculation based on VSM}
-%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language.
-In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
-For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
-To do so, we use VSM which is a model for representing text documents as vectors.
-For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
-The $w_{t,d}$ value is TF-IDF weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
-
-\begin{equation}
-w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
-\label{eq:tf-idf}
-\end{equation}
-
-After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.
-
-\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product.
-Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}.
-The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.
-
-\begin{equation}
-\mathrm{sim}(m,c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
-\label{eq:cosine}
-\end{equation}
-
-\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}.
-We can use this distance as an dissimilarity.
-Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Euclidian distance using Equation \ref{eq:cosine}.
-The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.
-
-\begin{equation}
-\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
-\label{eq:euclid}
-\end{equation}
-
-\subsection{Estimating Similarity and Dissimilarity Threshold}
-We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$.
-This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall).
-This can be calculated using Equation \ref{eq:fmeasure}.
-
-\begin{equation}
-\begin{split}
-\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
-\\
-\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
-\\
-\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
-\end{split}
-\label{eq:fmeasure}
-\end{equation}
-
-Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful.
-To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments.
-For the correctness of prediction, we determine from the useful/useless defined dataset.
-
-%Using this method, we iteratively measure an accuracy for values of $s_t$ and $s'_t$ ranging $[0,1]$; and values of $d_t$ and $d'_t$ ranging $[0,\infty)$.
-
-%\begin{equation}
-%\mathrm{F\text{-}measure}_{S_T,D_T} = \frac{2\mathrm{TP}_{S_T,D_T}}{2\mathrm{TP}_{S_T,D_T}+\mathrm{FP}_{S_T,D_T}+\mathrm{FN}_{S_T,D_T}}
-%\label{eq:precision}
-%\end{equation}
-
-%where $\mathrm{TP}_{S_T,D_T}= |\{ c \in C |  \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{c \in C| \mathrm{vote}(c) = 2\}|$,  $\mathrm{FP}_{S_T,D_T} = |\{ c \in C | \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{FALSE} \}\cap \{\mathrm{vote}(c) = 2\} $, $\mathrm{FN}_{S_T,D_T} = |\{ c | c \in C, \text{\textbf{useful}}(c,S_T,D_T) = \mathrm{TRUE} \}\cap \{\mathrm{vote}(c) < 2\} $
-%According to this, we can formalize as follows:
-
-%\begin{equation}
-%(S_T,D_T) = \max(\{\mathrm{F\text{-}measure} \text{ of \textbf{useful}}(c,s_T,d_T) | s_T\in[0,1] \text{ and } d_T\in [0,\infty) \})
-%\end{equation}

### 2014-07-25 sections/approach.tex
refactors and modifications to the equations

@@
+% !TEX root = ../paper.tex
+
 \section{Reviewers' Comments Classification Approach}
@@
 
-Fig.
-\ref{fig:overview} shows the overview of our proposed approach.
-We classify usefulness of comments by measuring similarity between commit message of proposed change and its comments.
-To calculate similarity in Fig.
-\ref{fig:overview}(a), we use Vector Space Model (VSM) which is well-known technique for retrieving similar documents written in unstructured natural language.
-We also use euclidian distance to calculate dissimilarity.
-For our training dataset, we manually identify every pair of comment and commit messages in Fig.
+Fig. \ref{fig:overview} shows the overview of our proposed approach.
+We classified the usefulness of comments by measuring similarity between commit message of proposed change and its comments.
+To calculate similarity in Fig. \ref{fig:overview}(a), we used Vector Space Model (VSM) which is a well-known technique for retrieving similar documents written in unstructured natural language.
+Euclidian distance is also used to calculate dissimilarity.
+For our training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
 \ref{fig:overview}(b).
-Then, we use the results from Fig.
+\thai{The overview figure does not have (a) and (b)...}
+The results from Fig.
 \ref{fig:overview}(a) and from Fig.
-\ref{fig:overview}(b) to estimate similarity and dissimilarity threshold that can best discriminate useful/useless comments.
+\ref{fig:overview}(b) are then used to estimate the similarity and dissimilarity threshold that can best discriminate useful/useless comments.
 Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.
 
-To classify usefulness of comment using similarity and dissimilarity, we firstly formalize our classification model as follows:
+To classify usefulness of comment using similarity and dissimilarity, we first formalize our classification model as follows:
 \begin{itemize}
-\item $\Theta(c,S_T,D_T)$ predict as \textbf{useful} if $\mathrm{sim}(m,c) \geq S_T$ and $\mathrm{dist}(m,c) \leq D_T$.
-\item $\Omega(c,S'_T,D'_T)$ predict as \textbf{useles} if $\mathrm{sim}(m,c) \leq  S'_T$ and $\mathrm{dist}(m,c) \geq D'_T$.
+\item \textbf{useful}: $\Theta(c,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
+\item \textbf{useless}: $\Omega(c,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
 \end{itemize}
-where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; while $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.
-The functions $\mathrm{sim}(m,c)$ and $\mathrm{dist}(m,c)$ calculates similarity and dissimilarity of comment $c$ comparing with commit message of its review.
+where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; and $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.
+
+The functions $\Sim(m,c)$ and $\Dist(m,c)$ represents the similarity and dissimilarity of the text of the comment $c$, compared to the corresponding change's commit message $m$.
+Two metrics are used because they are independently generated and thus provides more dimensions for classification.
+We also found experimentally that using two metrics gives better performance than just one.
+
 The details our approach is described in the following subsections.
-\pick{Why we need two measurements?}
-\pick{What happen in model for otherwise?}
 
@@
 For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
-The $w_{t,d}$ value is TF-IDF weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
+The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
 
 \begin{equation}
-w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
+w_{t,d} = \operatorname{tf}_{t,d} \times \log\frac{|D|}{|\{d' \in D \:|\: t \in d'\}|}
 \label{eq:tf-idf}
@@
 \begin{equation}
-\mathrm{sim}(m,c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
+\Sim(c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
 \label{eq:cosine}
@@
 \begin{equation}
-\mathrm{dist}(m,c) = \mathrm{euclidian}(\overrightarrow{V_m},\overrightarrow{V_c}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
+\Dist(m,c) = \|\overrightarrow{V_m} - \overrightarrow{V_c}\| = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
 \label{eq:euclid}

### 2014-07-25 sections/introduction.tex
Subtantially edited the introduction. This section needs to be split into I. Introduction, II. Motivation

@@
 \section{Introduction}
-Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-Its main intention is to early identify defects before integrating changes.
-Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
-The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
-Developers will then fix their changes following those comments.
+Software code review is an established cost-effective software quality management practice.
+Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
+Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industrial and OSS projects.
+One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required,.
+Reviewers can find defects and hold discussions on them by adding comments through a code review tool or a mailing list.
+Developers then propose changes in response to these comments which in turn are reviewed for approval.  Fig. \ref{fig:process} illustrates a typical MCR process.
 
-As the performance of code review straight forward to the quality of software project, many studies investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
-However, very little research investigate that in MCR, how does a discussion for a proposed change impact to the software quality.
-Since most of the proposed change improvements are triggered from reviewer comments \cite{Beller}.
-It is possible that comments of reviewers can be either positively contribute the proposed changes or a discussion which is out of scope.
-To determine the impact of discussion in MCR, a manual classification is required as study of Beller et.
+Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
+However, little research exists investigating how the discussion for a proposed change impacts software quality.
+Given that most proposed changes are triggered from reviewer comments \cite{Beller},
+it is possible that reviewers comments can either positively contribute to the proposed changes (i.e.
+"useful"), or be a discussion which is out of scope (i.e.
+"useless" relative to the proposed changes).
+Not surprisingly the amount of useless comments appears to increase with project size.
+Yet notably so too does the ratio of useless to useful comments.
+%\dan{Do you think we can find a reference for this?}
+This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
+Current research has focused mostly on the relation between number of comments and quality.
+To the best of our knowledge the connection between degree of useful and useless comments and quality has not been studied.
+One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et.
 al.
 \cite{Beller}.
-As a massive amount of changes and comments in MCR history\cite{Balachandran2013,Thongtanunam2014}, it is painstaking and time consuming to classify data sets to perform quantitative analysis.
-Moreover, the comments in MCR is unstructured natural text unlike a checklist in the formal inspection.
+MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify the comments to perform appropriate quantitative analysis.
+Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
+Fig.
+\ref{fig:example} show typical MCR comments illustrating these issues.
 %\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
@@
 
-In this paper, we present an approach to automatically classify the usefulness of comments.
-We define that the usefulness is a comment that contribute to improve the proposed changes.
-In our approach, we analyze the similarity between commit message of the proposed changes and their comments.
-Our key idea is that useful comments are likely to contain similar topic as the proposed changes.
-To do so, we use text mining techniques, Vector Space Model (VSM) to calculate similarity and use euclidian distance to calculate dissimilarity.
-We create our predictive model by estimating a set of similarity and dissimilarity values that best discriminate between a useful and useless comments using the prediction evaluations: Precision, Recall and F-measure.
+%\dan{Much of the following material should be placed in a separate Motivation section} 
+In this paper we present a text mining approach to assisting in classifying the usefulness of comments.
+The purposed approach is meant to enable classifying the large amounts of MRC comments needed to conduct comment and code quality studies such as those discussed earlier.
+Manual classification can quickly become an untenable task.
+Our modest OSS case study has a over 17,000 potentially useful comments.
+At an optimistic 5 seconds peer comment classification we would expect about 24 person-hours of effort.
+Furthermore manual classification is subjective and error-prone.
+By introducing some automation support based on objective empirical criteria, the method we propose here aims to both reduce effort and increase confidence in classification to a degree practical for addressing very large MRC data sets.
+Because usefulness of a comment is not precisely defined and a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.
 
-For our case study, we used a review history of Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system which is tool for supporting MCR process.
-Our case studied project is Qt\footnote{\url{http://qt-project.org/}}, a open source project of a cross-platform application and UI framework supported by Digia corporation.
-To validate our approach, we manually classify the usefulness for 320 comments and measure its accuracy.
-We also used our predictive model for the all set of comments to preliminary estimate quality of reviews.
-According to this, we address the following two research questions:
+We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useful} comment as one that does not.
+Usefulness is not dichotomous and we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
+In our approach we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
+Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
+To do determine these semantic relationships we use the Vector Space Model (VSM) and calculate similarity as the cosine distance between the comment and commit message vectors and the euclidian distance between them to calculate dissimilarity.
+We create our predictive model by estimating pairs of similarity and dissimilarity values that discriminate between useful and useless comments that optimize prediction performance measures such as Precision, Recall and F-measure.
 
-\noindent \textbf{RQ1:} Can we identify useful and useless discussions in code review?\\
+For our case study of the method, we use a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
+For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
+We also apply our predictive model to the full set of
+17,000 
+%\dan{what's the actual number?}
+comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
+
+\noindent \textbf{RQ1:} Is VSM similarity a good indicator of MRC comment usefulness?\\
 \noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
-\noindent \textbf{RQ3:} Is this a cost-efficient way to identify useful and useless comments?
-
-\noindent The main contribution of this paper are:
+\noindent \textbf{RQ3:} Is VSM similarity classification cost-efficient, assurable, and scalable?
+%\dan{******** HERE *******}
+\noindent The main contributions of this paper are:
 \begin{itemize}

### 2014-07-26 sections/approach.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

@@
 
-\section{Reviewers' Comments Classification Approach}
+\section{Semantic Similarity Classification of Comment Usefulness}
 \begin{figure}[!t]
 \centering
-\includegraphics[scale=0.35, trim = 50 90 0 30, clip=true]{overview2}
+\includegraphics[scale=0.34, trim = 50 90 0 30, clip=true]{overview2}
 \caption{Overview of our classification approach.}
@@
 
-Fig. \ref{fig:overview} shows the overview of our proposed approach.
-We classified the usefulness of comments by measuring similarity between commit message of proposed change and its comments.
-To calculate similarity in Fig. \ref{fig:overview}(a), we used Vector Space Model (VSM) which is a well-known technique for retrieving similar documents written in unstructured natural language.
-Euclidian distance is also used to calculate dissimilarity.
-For our training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
+Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
+As discussed previously, this is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
+According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification \emph{similarity conditions}.
+\dan{can we find a reference for relevance and similarly?}
+That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
+Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity} , the less relevant, and hence less useful.
+Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
+That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
+The key is determining these degrees in a practical and effective manner.
+While this representation is straightforward and automatically adjusts ti the quality of the data, it has a few drawbacks.
+First, we have to accept that some comments cannot be reliably or confidently classified.
+We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} i.e.
+unable to assess (subjectively) comment usefulness.
+Again, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+This decreases the cost-effectiveness limiting the practicality of application to projects with a large enough number of comments whee the classification effort saved overcomes the training costs.
+% empirically driven and automatically adapts to the quality the data
+ Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
+Usefulness of a comment is determined by computing its semantic similarity with the commit message of proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
+The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
+In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.
+To calculate semantic similarity Fig.
+\ref{fig:overview}(a), we used the Vector Space Model (VSM) with the cosine distance measure which is a well-known technique for retrieving similar documents written in unstructured natural language.
+The Euclidian distance is a well-established measure of dissimilarity and applies analogously.
+%For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
 \ref{fig:overview}(b).
-\thai{The overview figure does not have (a) and (b)...}
-The results from Fig.
-\ref{fig:overview}(a) and from Fig.
-\ref{fig:overview}(b) are then used to estimate the similarity and dissimilarity threshold that can best discriminate useful/useless comments.
-Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history.
+\thai{The %overview figure does not have (a) and (b)...}
+%\dan{what was the actual effort (in person-hours) to create the training data?}
+The training data is a small set of randomly-selected pairs of comments and corresponding commit messages are manually assessed for usefulness.
+For statistical purposes at least 30 useful and 30 useless comments are needed.
+The similarity and dissimilarities are computed for the data set.
+These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
+Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows:
+\begin{itemize}
+\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
+\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
+\item \textbf{undetermined}: Neither of the above conditions are $\True$.
+\end{itemize}
 
-To classify usefulness of comment using similarity and dissimilarity, we first formalize our classification model as follows:
-\begin{itemize}
-\item \textbf{useful}: $\Theta(c,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
-\item \textbf{useless}: $\Omega(c,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
-\end{itemize}
-where $S_T$ and $D_T$ are similarity and dissimilarity thresholds for useful comments identification; and $S'_T$ and $D'_T$ are similarity and dissimilarity thresholds for useless comments identification.
+The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$.
+Two metrics are used because they are independently generated and thus provides better discrimination for classification.
+We also found experimentally that using two metrics has higher performance than just one.
 
-The functions $\Sim(m,c)$ and $\Dist(m,c)$ represents the similarity and dissimilarity of the text of the comment $c$, compared to the corresponding change's commit message $m$.
-Two metrics are used because they are independently generated and thus provides more dimensions for classification.
-We also found experimentally that using two metrics gives better performance than just one.
+The details of our approach are elaborated in the following subsections.
 
-The details our approach is described in the following subsections.
-
+\dan{**** ALERT **** this entire subsection is not needed!
+Everything in it is well-known and can simply be referenced.
+I suggest removing it if we need the space.
+I have not edited this section ....
+}
 \subsection{Similarity and Dissimilarity Calculation based on VSM}
@@
 
-\subsection{Estimating Similarity and Dissimilarity Threshold}
-We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that can maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$.
-This is an accuracy measurement for a binary classification considering an accuracy of prediction (precision) and  a coverage of classification (recall).
-This can be calculated using Equation \ref{eq:fmeasure}.
+\subsection{Estimating Similarity and Dissimilarity Thresholds}
+Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ to classify useful comments and we have the following values:
 
+$\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} and are \textit{actually useful} i.e. true-positives;
+
+$\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} but are \textit{actually useless} i.e. false positives;
+
+$\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model classifies as \textit{useless} but are \textit{actually useful}.
+
+We can now define the following classification  performance measures: 
 \begin{equation}
@@
 
-Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ as predict model to identify useful comments , $\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} and are actually useful; $\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model predicted as \textit{useful} but are actually useless; and $\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model predict as \textit{useless} but are actually useful.
-To measuring F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ model, it uses the same consideration but change the determination to useless comments.
-For the correctness of prediction, we determine from the useful/useless defined dataset.
+We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$ Equation \ref{eq:fmeasure}.
+This is a performance measurement for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
+
+The F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ is computed analogously where we change instances of useful to useless and vice-versa in the definitions.
+The correctness of classification is determined from the useful/useless defined dataset.
 

### 2014-07-26 sections/background.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

@@
 Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
+\dan{this section seems to only cover MCR. We could have this be a Background section with this and the other subsequent sections moved to sub-sections}
 \section{Modern Code Review Process}
@@
 (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
-(2) reviewers examine the proposed code changes whether it contains defects or not.
-(3) reviewers will give comments where should the author improve the code change.
-The author will create a new change according to the comments then re-submit a new patch again.
-Then, reviewers will examine the new change.
-If there is still a needed improvement, reviewers will give comments to fix again.
-The steps (1)-(3) will be iterated until reviewers can determine that this changes can be merge to the project or should not be merge (reject the change).
+(2) reviewers examine the proposed code changes for defects or concerns.
+(3) reviewers provide comments to the author.
+The author creates a revised proposed change according to the comments then re-submits for review.
+Then, reviewers will examine the revised proposed change.
+If the revision is not approved, reviewers provide comments to fix and the process continues until reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).
 
-According to this process, reviewers' comment is the most important for the software quality.
-McIntosh et.
+According to this process, reviewers' comments are the most important factor in determining software quality.
+In particular, McIntosh et.
 al.
-\cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs.
-However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective.
-Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}.
-Our observation in Qt project also correspond this finding.
-We found some comments are superficial and unrelated to the proposed changes.
-For example, a superficial and unconfident reviewer as shown in Fig.
-\ref{fig:example}(a), a comment for rule of using Version Control System (e.g.
-Git) in the project Fig.
-\ref{fig:example}(b).
+\cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
+However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers) and frequently comments are superficial or do not clearly identify defects or relevant issues (e.g.
+design suggestions, coding styles, etc.) for the proposed change and are thus of questionable usefulness.
+For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g.
+"Keep up the good work!").
+Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
+Our observations of the Qt project also correspond to this finding.
+We found some comments are superficial and unhelpful to the proposed changes.
+For example, the superficial and unconfident comment shown in Fig.
+\ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information.
+While the comment in Fig.
+\ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.
 

### 2014-07-26 sections/introduction.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

@@
 Yet notably so too does the ratio of useless to useful comments.
-%\dan{Do you think we can find a reference for this?}
+\dan{Do you think we can find a reference for this?}
 This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
@@
 
-%\dan{Much of the following material should be placed in a separate Motivation section} 
+\dan{Much of the following material should be placed in a separate Motivation section} 
 In this paper we present a text mining approach to assisting in classifying the usefulness of comments.
@@
 17,000 
-%\dan{what's the actual number?}
+\dan{what's the actual number?}
 comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
 
-\noindent \textbf{RQ1:} Is VSM similarity a good indicator of MRC comment usefulness?\\
+\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
 \noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
-\noindent \textbf{RQ3:} Is VSM similarity classification cost-efficient, assurable, and scalable?
-%\dan{******** HERE *******}
-\noindent The main contributions of this paper are:
+\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?
+
+\noindent In addition to addressing the research questions above, the main contributions of this paper are:
+\dan{these are more "results" than contributions.... need to reword this!}
 \begin{itemize}
-\item We propose an approach to mine natural text of comments in code reviews and classify their usefulness.
-\item The experimental results show that our approach can classify comments with an F$_1$ score of 0.681 and 0.693.
-\item We found that 85\% of comments in Gerrit are automatically generated.
-In the remaining 15\%, about 43\% of them are classified as useful, while about 34\% are classified as not useful comments.
-The remaining 23\% cannot be clearly classified.
+\item A practical to apply approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
+\item The experimental results show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
+\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
+For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful.
+The remaining 23\% are undetermined and require manual classification.
+Thus the classification effort is reduced by about 77\%.
+\item xx\% of the comments did not have unanimity (i.e.
+unclear), and of these yy\% were automatically determined to be useful or not useful.
+Follow up with dissenting assessors found mis-judgement occurred zz\% of the time whereby in retrospect the comment would have had unanimity.
+This indicates the method is useful in identifying subjective judgement errors.
+\item Of the 23\% not automatically classified (i.e.
+undetermined), qq\% were unclear.
+Of the (1-qq)\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear.
+This indicates the method is useful in identifying chance unanimity errors or group think bias.
 \end{itemize} 

### 2014-07-26 sections/methods.tex
Edited up though Case Study section
Added a title! We need to rearrange and remove some sections :( I’ll
work on it during my long trim ride to Tokyo on Sunday

@@
 
-\section{Case Study Design}
+\section{Case Study}
 
-We used the review history of Qt project from Gerrit code review tool provided by Hamasaki et.
+Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et.
 al.
 \cite{Hamasaki2013}.
-Qt project is a large open source project composed of small subsystems.
-For our case study, we selected the most active subproject \texttt{qtbase} project.
+Qt project is a large open source project composed of numerous small subsystems.
+We selected the most active subproject \texttt{qtbase} project.
 From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.
@@
 \subsection{Data Preparation}
-We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we firstly processed the commit message and comments as follows:
+We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we first processed the commit message and comments as follows:
 
@@
 In Gerrit, the comments are composed of comment messages from reviewers and automated messages.
-These automatic messages are generated by Gerrit and integration system to record activities, for example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}.
-Since these messages are not impact to software quality\cite{Mcintosh}, we removed them from our data set.
-We identified these automatic messages using regular expression and selecting frequently appeared pattern of messages.
+These automatic messages are generated by Gerrit and the integration system to record activities.
+For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}.
+Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
+In practice they are not considered in code review.
+They are easily determined as useless by our method and would artificially improve our classification performance.
+We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.
 
@@
 \subsubsection{Data Preprocessing}
- we extracted semantic words commit messages and comment messages before converting to vector.
+ As is customary for VSM processing we extracted semantic words from commit messages and comment messages before converting to vector.
 For each message, we removed all punctuation signs, digits, and common words (e.g.
@@
 \subsubsection{Ground-Truth Data Preparation}
-To prepare ground-truth data, we read comments and manually identified useful and useless comments.
-In this study, we use three people (the first two authors and one student) independently classify comments by giving a question that ``Does this comment technically contribute to its change or not?''.
-Then, the readers gave a vote for \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.
-From the voting scores, we regarded that the comments with three \texttt{YES} votes are \textbf{useful} comments and the comments with no \texttt{YES} votes (i.e.
-three \texttt{NO} votes) are \textbf{useless} comments.
-For the comments with one and two \texttt{YES}' votes, we remained them as \textbf{unclear} comments which we cannot confidently defined.
+To prepare ground-truth data, a team of three experienced developers independently read comments and manually assessed them useful or useless.
+The assessors were asked to answer for each comment the question ``Does this comment technically contribute to its proposed change?''.
+Then, the assessors cast their vote as \texttt{YES} if the comment is likely to useful and \texttt{No} if the comment is likely to useless.
+Comments with three \texttt{YES} votes are classified as \textbf{useful} comments and comments with three \texttt{NO} votes are \textbf{useless}.
+Comments lacking unanimity (i.e.
+one or two \texttt{YES} votes are deemed \textbf{unclear} and without confident usefulness.
 
@@
 
-\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}\\
+\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
 \indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
-Then, we used these comments for both training and test data set for our approach to determine an effectiveness of our approach.
+Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
 We also determined the robustness of our approach using cross validation.
@@
 The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.
+
+\dan{What what the effort in person-hours for this?}
 

### 2014-07-26 sections/methods.tex
Merged Case Study Design and Case Study Results sections
I’ve gone as far as I can for now. Please add the actual results so I
can make sure we present them clearly.

@@
 Comments with three \texttt{YES} votes are classified as \textbf{useful} comments and comments with three \texttt{NO} votes are \textbf{useless}.
-Comments lacking unanimity (i.e.
-one or two \texttt{YES} votes are deemed \textbf{unclear} and without confident usefulness.
+Comments lacking unanimity i.e.
+one or two \texttt{YES} votes are deemed \textbf{unclear} and not confidently useful or useless.
 
@@
 
+\dan{Why is this a separate section? Either the actual results should deb discussed here or this should be integrated into the results section.}
+
 \noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
@@
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
-We also determined the robustness of our approach using cross validation.
-We randomly selected 90\% of 320 comments for training set and 10\% for test set.
-The effectiveness was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}. We repeated this validation for 300 times and find average of accuracy.
+We also determined the effectiveness of our approach using bootstrapping cross validation.
+We randomly selected 90\% of 320 comments for training set and 10\% for the validation set.
+The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
+We repeated this validation for 300 times to estimate the mean and variance of the performance.
 
@@
 Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
+\dan{I thought we changed this! It would be bad if we didn't. Let me know what the actual situation is here.}
 
@@
 A statical analysis was performed to understand the impact of useful discussion to software quality.
+\dan{results?}
 
-\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
+\noindent \textbf{RQ3:  Is semantic similarity classification cost-efficient, assur- able, and scalable?}\\
 \indent
+\dan{results?}
 

### 2014-07-26 sections/results.tex
Merged Case Study Design and Case Study Results sections
I’ve gone as far as I can for now. Please add the actual results so I
can make sure we present them clearly.

@@
 
-\section{Case Study Results}
-\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
+\section{Case Study}
+%\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
+
+Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et.
+al.
+\cite{Hamasaki2013}.
+Qt project is a large open source project composed of numerous small subsystems.
+We selected the most active subproject \texttt{qtbase} project.
+From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.
+
+\subsection{Data Preparation}
+We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we first processed the commit message and comments as follows:
+
+\subsubsection{Automatically generated messages removal}
+In Gerrit, the comments are composed of comment messages from reviewers and automated messages.
+These automatic messages are generated by Gerrit and the integration system to record activities.
+For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}.
+Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
+In practice they are not considered in code review.
+They are easily determined as useless by our method and would artificially improve our classification performance.
+We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.
+
+\subsubsection{Data Preprocessing}
+ As is customary for VSM processing we extracted semantic words from commit messages and comment messages before converting to vector.
+For each message, we removed all punctuation signs, digits, and common words (e.g.
+a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}.
+We then used Porter stemming algorithm to remove the commoner morphological and inflexional endings from words in English.
+
 Table \ref{tb:datastatistic} summarizes data set we used for this study after preparation.
-From 72,484 comments of 6,605 reviews with its commit messages extracted from raw data set, there are 10,670 (15\%) of comments are written by reviewers while 85\% of comments are automatically generated by Gerrit system and integration bots.
 
@@
 All Comments & 72,484& - \\ \hline
-Reviewers Messages & 10,670 & 15\% \\ \hline
-Automated Messages. & 61,814 & 85\% \\ \hline
+Reviewers Comments & 10,670 & 15\% \\ \hline
+Automated Comments & 61,814 & 85\% \\ \hline
 
@@
 \end{table}
+
+\subsection{Research Questions}
 
@@
 
-\noindent \textbf{RQ1: Can we identify useful and useless discussions in code review?}
+\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
+\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
+Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
+We also determined the effectiveness of our approach using bootstrapping cross validation.
+We randomly selected 90\% of 320 comments for training set and 10\% for the validation set.
+The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
+We repeated this validation for 300 times to estimate the mean and variance of the performance.
+
+\dan{What what the effort in person-hours for this?}
+
+Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
+\dan{I thought we changed this! It would be bad if we didn't. Let me know what the actual situation is here.}
 
@@
 To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}. 
-\pick{We cannot brute force for every floating number.
-How did we calculate this?} Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
+\pick{We cannot brute force for every floating number. How did we calculate this?} 
+\dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
+
+Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
 \pick{I used dummy results.
@@
 \noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
+\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set.
+We then used these thresholds to classify the rest of comments.
+A statical analysis was performed to understand the impact of useful discussion to software quality.
 \pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}
@@
 
-\noindent \textbf{RQ3: Does this approach practical and cost-effective for large-scale projects?}\\
+\noindent \textbf{RQ3: Is semantic similarity classification cost-efficient, assur- able, and scalable?}\\
 

### 2014-07-27 sections/introduction.tex
edited the introduction. break long lines and paragraphs.

@@
 Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industrial and OSS projects.
-One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required,.
+One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
 Reviewers can find defects and hold discussions on them by adding comments through a code review tool or a mailing list.
@@
 it is possible that reviewers comments can either positively contribute to the proposed changes (i.e.
-"useful"), or be a discussion which is out of scope (i.e.
-"useless" relative to the proposed changes).
-Not surprisingly the amount of useless comments appears to increase with project size.
-Yet notably so too does the ratio of useless to useful comments.
-\dan{Do you think we can find a reference for this?}
-This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
+``\emph{useful}''), or be a discussion which is out of scope (i.e.
+``\emph{useless}'' relative to the proposed changes\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.}).
+
+Since MCR does not require strict guidelines, checklists, or formal processes, some people tend to review and just look for trivial issues (e.g.
+coding styles, conventions, and process issues), leaving deeper issues undiscussed \cite{Mcintosh}.
+This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.
+
 Current research has focused mostly on the relation between number of comments and quality.
-To the best of our knowledge the connection between degree of useful and useless comments and quality has not been studied.
-One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et.
-al.
-\cite{Beller}.
-MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify the comments to perform appropriate quantitative analysis.
+To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
+One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et. al. \cite{Beller}.
+MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014}, and it is painstaking and time consuming to classify the comments in order to perform appropriate quantitative analysis.
 Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
@@
 \ref{fig:example} show typical MCR comments illustrating these issues.
-%\pick{Need some connection. Says that Massive amount of commits and comment it would be expensive to manually identify. It's natural language }
+
 \begin{figure}[!t]

### 2014-07-27 sections/introduction.tex
updated more of the introduction...

@@
 \dan{Much of the following material should be placed in a separate Motivation section} 
-In this paper we present a text mining approach to assisting in classifying the usefulness of comments.
-The purposed approach is meant to enable classifying the large amounts of MRC comments needed to conduct comment and code quality studies such as those discussed earlier.
-Manual classification can quickly become an untenable task.
+In this paper we present a text mining approach to assist in classifying the usefulness of comments.
+The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
+
 Our modest OSS case study has a over 17,000 potentially useful comments.
-At an optimistic 5 seconds peer comment classification we would expect about 24 person-hours of effort.
-Furthermore manual classification is subjective and error-prone.
-By introducing some automation support based on objective empirical criteria, the method we propose here aims to both reduce effort and increase confidence in classification to a degree practical for addressing very large MRC data sets.
-Because usefulness of a comment is not precisely defined and a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.
+At an optimistic 5 seconds peer comment classification, we would expect about 24 person-hours of effort.
+Furthermore, manual classification is subjective and error-prone.
 
-We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useful} comment as one that does not.
-Usefulness is not dichotomous and we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
-In our approach we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
+By introducing some automation support based on objective empirical criteria,
+the method we propose here aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
+Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.
+
+We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless} comment as one that does not.
+Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
+
+In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
 Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
-To do determine these semantic relationships we use the Vector Space Model (VSM) and calculate similarity as the cosine distance between the comment and commit message vectors and the euclidian distance between them to calculate dissimilarity.
-We create our predictive model by estimating pairs of similarity and dissimilarity values that discriminate between useful and useless comments that optimize prediction performance measures such as Precision, Recall and F-measure.
+To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors.
+We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
+This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.
 
-For our case study of the method, we use a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
+For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
 For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
-We also apply our predictive model to the full set of
-17,000 
-\dan{what's the actual number?}
+We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
 comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:

### 2014-07-27 sections/introduction.tex
update more introduction... continuing early morning tomorrow.

@@
 \begin{itemize}
-\item A practical to apply approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
-\item The experimental results show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
+\item A practical approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
+\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
 \item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
@@
 Thus the classification effort is reduced by about 77\%.
-\item xx\% of the comments did not have unanimity (i.e.
-unclear), and of these yy\% were automatically determined to be useful or not useful.
-Follow up with dissenting assessors found mis-judgement occurred zz\% of the time whereby in retrospect the comment would have had unanimity.
+\item \TODO{xx}\% of the comments did not have unanimity (i.e.
+unclear), and of these \TODO{yy}\% were automatically determined to be useful or not useful.
+Follow up with dissenting assessors found mis-judgement occurred \TODO{zz}\% of the time whereby in retrospect the comment would have had unanimity.
 This indicates the method is useful in identifying subjective judgement errors.
 \item Of the 23\% not automatically classified (i.e.
-undetermined), qq\% were unclear.
-Of the (1-qq)\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear.
+undetermined), \TODO{qq}\% were unclear.
+Of the \TODO{(1-qq)}\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear.
 This indicates the method is useful in identifying chance unanimity errors or group think bias.

### 2014-07-27 sections/approach.tex
Propose a new title. Shorten Introduction (The rest is commented). and remove VSM section in approach

@@
 
-\dan{**** ALERT **** this entire subsection is not needed!
+%\dan{**** ALERT **** this entire subsection is not needed!
 Everything in it is well-known and can simply be referenced.
@@
 }
-\subsection{Similarity and Dissimilarity Calculation based on VSM}
-%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language.
+%\subsection{Similarity and Dissimilarity Calculation based on VSM}
+%%Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language.
 In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.
-For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
-To do so, we use VSM which is a model for representing text documents as vectors.
-For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
-The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
-
-\begin{equation}
-w_{t,d} = \operatorname{tf}_{t,d} \times \log\frac{|D|}{|\{d' \in D \:|\: t \in d'\}|}
-\label{eq:tf-idf}
-\end{equation}
-
-After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance.
-
-\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product.
+%For each review, we compute similarity and dissimilarity of every comments comparing with the commit message which is described the purpose of the change.
+%To do so, we use VSM which is a model for representing text documents as vectors.
+%For a set of commit messages and comments ($D$), each document, $d$ (commit message or comment) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in $D$.
+%The $w_{t,d}$ value is tf-idf weighting of term $t$ calculated from term occurrence frequency using Equation \ref{eq:tf-idf} where $\operatorname{tf}_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.
+%
+%\begin{equation}
+%w_{t,d} = \operatorname{tf}_{t,d} \times \log\frac{|D|}{|\{d' \in D \:|\: t \in d'\}|}
+%\label{eq:tf-idf}
+%\end{equation}
+%
+%After transforming commit message and comments to vectors, we calculate similarity using Cosine similarity and Euclidian distance. 
+%
+%
+%\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product.
 Given a vector commit message $\overrightarrow{V_m}$ and the vector of its comments $\overrightarrow{V_m}$, we can calculate Cosine similarity using Equation \ref{eq:cosine}.
 The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.
-
-\begin{equation}
-\Sim(c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
-\label{eq:cosine}
-\end{equation}
-
-\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}.
+%
+%\begin{equation}
+%\Sim(c) = \cos\theta(\overrightarrow{V_m},\overrightarrow{V_c}) = \frac{\sum_{i=1}^{|D|} w_{i,m} \times w_{i,c}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,m} \times \sum_{i=1}^{|D|} w^2_{i,c}}}
+%\label{eq:cosine}
+%\end{equation}
+%
+%\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}.
 We can use this distance as an dissimilarity.
@@
 The distance value is ranging $[0,\infty)$ where 0 means these vectors are the same vectors while a more distance means these vectors are less similar.
-
-\begin{equation}
-\Dist(m,c) = \|\overrightarrow{V_m} - \overrightarrow{V_c}\| = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
-\label{eq:euclid}
-\end{equation}
-
-\subsection{Estimating Similarity and Dissimilarity Thresholds}
-Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ to classify useful comments and we have the following values:
-
-$\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} and are \textit{actually useful} i.e. true-positives;
-
-$\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} but are \textit{actually useless} i.e. false positives;
-
-$\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model classifies as \textit{useless} but are \textit{actually useful}.
-
-We can now define the following classification  performance measures: 
-\begin{equation}
-\begin{split}
-\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
-\\
-\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
-\\
-\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
-\end{split}
-\label{eq:fmeasure}
-\end{equation}
+%
+%\begin{equation}
+%\Dist(m,c) = \|\overrightarrow{V_m} - \overrightarrow{V_c}\| = \sqrt{\sum_{i=1}^{|D|}(w_{i,m} - w_{i,c})^2}
+%\label{eq:euclid}
+%\end{equation}
+%
+%\subsection{Estimating Similarity and Dissimilarity Thresholds}
+%Suppose we use $\Theta(c,S_T=s_t,D_T=d_t)$ to classify useful comments and we have the following values:
+%
+%$\mathrm{TP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} and are \textit{actually useful} i.e. true-positives; 
+%
+%$\mathrm{FP}_{s_t,d_t}$ is the number of comments that our model classified as \textit{useful} but are \textit{actually useless} i.e. false positives;
+%
+%$\mathrm{FN}_{\theta_s,\theta_d}$ is the number of comments that our model classifies as \textit{useless} but are \textit{actually useful}. 
+% 
+%We can now define the following classification  performance measures: 
+%\begin{equation}
+%\begin{split}
+%\mathrm{F\text{-}measure}_{s_t,d_t} &= 2 \times \frac{\mathrm{precision}_{s_t,d_t} \times \mathrm{recall}_{s_t,d_t}}{\mathrm{precision}_{s_t,d_t} + \mathrm{recall}_{s_t,d_t}}
+%\\
+%\mathrm{precision}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FP}_{s_t,d_t}}
+%\\
+%\mathrm{recall}_{s_t,d_t}  &= \frac{\mathrm{TP}_{s_t,d_t}}{\mathrm{TP}_{s_t,d_t}+\mathrm{FN}_{s_t,d_t}}
+%\end{split}
+%\label{eq:fmeasure}
+%\end{equation}
 

### 2014-07-27 sections/background.tex
Propose a new title. Shorten Introduction (The rest is commented). and remove VSM section in approach

@@
 Then, we describe the background behind our approach composed of text mining techniques using VSM and euclidian distance and prediction evaluation techniques.
-\dan{this section seems to only cover MCR. We could have this be a Background section with this and the other subsequent sections moved to sub-sections}
+%\dan{this section seems to only cover MCR. We could have this be a Background section with this and the other subsequent sections moved to sub-sections}
+
 \section{Modern Code Review Process}
@@
 Then, reviewers will examine the revised proposed change.
-If the revision is not approved, reviewers provide comments to fix and the process continues until reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).
+If the revision is not approved, reviewers provide comments to fix and the process continues until (4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).
+
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
+\caption{Examples of comment in code reviews of Qt project.}
+\label{fig:example}
+\end{figure}
 
@@
 For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g.
-"Keep up the good work!").
+``Keep up the good work!").
 Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
@@
 \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
-\caption{Examples of comment in code reviews of Qt project.}
-\label{fig:example}
-\end{figure}

### 2014-07-27 sections/introduction.tex
Propose a new title. Shorten Introduction (The rest is commented). and remove VSM section in approach

--- 2014-07-27 sections/introduction.tex
@@
 One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
-Reviewers can find defects and hold discussions on them by adding comments through a code review tool or a mailing list.
-Developers then propose changes in response to these comments which in turn are reviewed for approval.  Fig. \ref{fig:process} illustrates a typical MCR process.
+Reviewers can find defects in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
+Developers then improve the changes in response to these comments which in turn are reviewed for approval.  
+%Fig. \ref{fig:process} illustrates a typical MCR process.
 
@@
 ``\emph{useful}''), or be a discussion which is out of scope (i.e.
-``\emph{useless}'' relative to the proposed changes\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.}).
+relatively  ``\emph{useless}''  to the proposed changes).
+Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g.
+coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
+This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.%This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.
 
-Since MCR does not require strict guidelines, checklists, or formal processes, some people tend to review and just look for trivial issues (e.g.
-coding styles, conventions, and process issues), leaving deeper issues undiscussed \cite{Mcintosh}.
-This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.
-
-Current research has focused mostly on the relation between number of comments and quality.
+Prior research has focused mostly on the relation between number of comments and quality.
 To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
@@
 MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014}, and it is painstaking and time consuming to classify the comments in order to perform appropriate quantitative analysis.
-Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
+Moreover, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
+
+% Fig. \ref{fig:example} show typical MCR comments illustrating these issues.
+%Moreover, unlike a checklist in used formal inspection, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
 Fig.
 \ref{fig:example} show typical MCR comments illustrating these issues.
+
+In this paper, we present a text mining approach to assist in classifying the usefulness of comments.
+The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
+By introducing some automation support based on objective empirical criteria,
+our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
+%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
+Through a case study of Qt project, we address the following research questions:
+\begin{description}
+\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
+\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
+\end{description}
+
+Our contributions are as follows:
+\begin{itemize}
+\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness based on using semantic similarity.
+\item We investigate relationship between usefulness of comments and semantic similarity.
+\item We investigate cost-efficient, assurable and scalable of semantic similarity in large open source project based on actual human effort.
+\end{itemize}
+
+%%%%%%%%% TEMP %%%%%%%%%
+%We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless}\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.} comment as one that does not.
+%Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
+%\dan{Much of the following material should be placed in a separate Motivation section} 
+%In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
+%Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
+%To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors.
+%We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
+%This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.
+%
+%For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
+%For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
+%We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
+%comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
+%
+%\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
+%\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
+%\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?
+%
+%\noindent In addition to addressing the research questions above, the main contributions of this paper are:
+%\dan{these are more "results" than contributions.... need to reword this!}
+%\begin{itemize}
+%\item A practical approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
+%\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
+%\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
+For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful.
+The remaining 23\% are undetermined and require manual classification.
+Thus the classification effort is reduced by about 77\%.
+%\item \TODO{xx}\% of the comments did not have unanimity (i.e.
+unclear), and of these \TODO{yy}\% were automatically determined to be useful or not useful.
+Follow up with dissenting assessors found mis-judgement occurred \TODO{zz}\% of the time whereby in retrospect the comment would have had unanimity.
+This indicates the method is useful in identifying subjective judgement errors.
+%\item Of the 23\% not automatically classified (i.e.
+undetermined), \TODO{qq}\% were unclear.
+Of the \TODO{(1-qq)}\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear.
+This indicates the method is useful in identifying chance unanimity errors or group think bias.
+%\end{itemize} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.
 
@@
 \end{figure}
-
-\dan{Much of the following material should be placed in a separate Motivation section} 
-In this paper we present a text mining approach to assist in classifying the usefulness of comments.
-The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
-
-Our modest OSS case study has a over 17,000 potentially useful comments.
-At an optimistic 5 seconds peer comment classification, we would expect about 24 person-hours of effort.
-Furthermore, manual classification is subjective and error-prone.
-
-By introducing some automation support based on objective empirical criteria,
-the method we propose here aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
-Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.
-
-We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless} comment as one that does not.
-Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
-
-In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
-Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
-To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors.
-We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
-This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.
-
-For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
-For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
-We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
-comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
-
-\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
-\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
-\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?
-
-\noindent In addition to addressing the research questions above, the main contributions of this paper are:
-\dan{these are more "results" than contributions.... need to reword this!}
-\begin{itemize}
-\item A practical to apply approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
-\item The experimental results show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
-\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
-For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful.
-The remaining 23\% are undetermined and require manual classification.
-Thus the classification effort is reduced by about 77\%.
-\item xx\% of the comments did not have unanimity (i.e.
-unclear), and of these yy\% were automatically determined to be useful or not useful.
-Follow up with dissenting assessors found mis-judgement occurred zz\% of the time whereby in retrospect the comment would have had unanimity.
-This indicates the method is useful in identifying subjective judgement errors.
-\item Of the 23\% not automatically classified (i.e.
-undetermined), qq\% were unclear.
-Of the (1-qq)\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear.
-This indicates the method is useful in identifying chance unanimity errors or group think bias.
-\end{itemize} 
-%Software Inspection is basically composed of a three-step procedure: preparation, inspection meeting, and repair.

### 2014-07-27 sections/background.tex
lots of change to the paper text.

@@
 
-An overview of MCR process based on Gerrit system is shown in Fig.
-\ref{fig:process}.
-The grey area shows the review process of the system which composed of four main steps.
-(1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system.
+An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}.
+The grey area shows the review process of the system which composed of four main steps:
+(1) an author creates a patch and submits a set of new or modified files as a review request to Gerrit system.
 (2) reviewers examine the proposed code changes for defects or concerns.
 (3) reviewers provide comments to the author.
-The author creates a revised proposed change according to the comments then re-submits for review.
+The author creates a revised proposed change according to the comments and re-submits for review.
 Then, reviewers will examine the revised proposed change.
@@
 According to this process, reviewers' comments are the most important factor in determining software quality.
-In particular, McIntosh et.
-al.
-\cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
-However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers) and frequently comments are superficial or do not clearly identify defects or relevant issues (e.g.
-design suggestions, coding styles, etc.) for the proposed change and are thus of questionable usefulness.
-For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g.
-``Keep up the good work!").
-Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
+In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
+However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.
+
+% (e.g. coding styles, documentation, process workflow, etc.)
+
+For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
+Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
 Our observations of the Qt project also correspond to this finding.
 We found some comments are superficial and unhelpful to the proposed changes.
-For example, the superficial and unconfident comment shown in Fig.
-\ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information.
-While the comment in Fig.
-\ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.
+For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
+while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

### 2014-07-27 sections/methods.tex
lots of change to the paper text.

@@
 % !TEX root = ../paper.tex
+%%
+%%    THIS FILE IS NOT USED!
+%%
+%%    The Methods section has been merged with the Results section, now titled "Case Study."
+%%
 
@@
 Qt project is a large open source project composed of numerous small subsystems.
-We selected the most active subproject \texttt{qtbase} project.
-From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.
+We selected the most active subproject, which is called \texttt{qtbase}.
+From this project, we used the review history before June 13\textsuperscript{th}, 2012, which has 6,605 changes and 72,484 comments in its Gerrit code review system.
 

### 2014-07-27 sections/results.tex
lots of change to the paper text.

@@
 \section{Case Study}
-%\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}
 
@@
 Qt project is a large open source project composed of numerous small subsystems.
-We selected the most active subproject \texttt{qtbase} project.
-From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.
+We selected the most active subproject, which is called \texttt{qtbase}.
+From this subproject, we used the review history before June 13\textsuperscript{th}, 2012, which contains 6,605 changes and 72,484 comments.
 
 \subsection{Data Preparation}
-We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we first processed the commit message and comments as follows:
+We used the commit messages and comments in the dataset.
+Before classifying the usefulness of comments, we first processed the commit message and comments as follows:
 
-\subsubsection{Automatically generated messages removal}
+\subsubsection{Removal of automatically generated messages}
 In Gerrit, the comments are composed of comment messages from reviewers and automated messages.

### 2014-07-27 sections/results.tex
Going through the results section.

@@
 \subsubsection{Removal of automatically generated messages}
-In Gerrit, the comments are composed of comment messages from reviewers and automated messages.
-These automatic messages are generated by Gerrit and the integration system to record activities.
-For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}.
-Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
-In practice they are not considered in code review.
+In Gerrit, the comments are composed of human-written comments from reviewers and automatically generated messages.
+These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
+\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples of these messages.
+
+Since these messages are generally record keeping,
+they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
+In practice, they are not considered in code review.
 They are easily determined as useless by our method and would artificially improve our classification performance.
-We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.
 
-\subsubsection{Data Preprocessing}
- As is customary for VSM processing we extracted semantic words from commit messages and comment messages before converting to vector.
-For each message, we removed all punctuation signs, digits, and common words (e.g.
+These messages are identified by looking for the most common lines of text.
+Regular expression patterns are then constructed to match these messages.
+Occurrences of these patterns are then removed from our dataset prior to further preprocessing.
+
+Automatic messages are also often inserted as part of review comments.
+They too are removed from our dataset, leaving us with only human-written part.
+We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
+
+\subsubsection{Data preprocessing}
+As is customary for VSM processing, we extracted semantic words from commit messages and comment messages before converting to vector.
+For each message, we removed all punctuation signs (except apostrophe) and other non alphanumeric characters.
+We also removed common words (e.g.
 a, an, the) using Google stop word list\footnote{Available at \url{http://meta.wikimedia.org/wiki/Stop_word_list/google_stop_word_list#English}}.

### 2014-07-28 sections/results.tex
Now going through the results.

@@
 
-\noindent \textbf{RQ1: Is semantic similarity a good indicator of MCR comment usefulness?}\\
-\indent To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
+\begin{ResearchQuestions}
+\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?
+\end{ResearchQuestions}
+
+To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
-We also determined the effectiveness of our approach using bootstrapping cross validation.
-We randomly selected 90\% of 320 comments for training set and 10\% for the validation set.
+We also determined the effectiveness of our approach using bootstrapping cross validation:
+We randomly selected 90\% of 320 comments for training set and used the remaining 10\% for the validation set.
 The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
-We repeated this validation for 300 times to estimate the mean and variance of the performance.
+This validation was repeated for 300 times to estimate the mean and variance of the performance.
 
-\dan{What what the effort in person-hours for this?}
+% \dan{What what the effort in person-hours for this?}
+% Thai sez:  Average time per comment is 28 seconds.
+%            Since we do a lot of other things while training, it gives us a STDEV of 45 seconds.
+%            The median, by the way, is just 10 seconds.
 
-Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
-\dan{I thought we changed this! It would be bad if we didn't. Let me know what the actual situation is here.}
+% Since our models do not include unclear type of comments, we defined them as negative condition i.e useless comments in case of useful classification (when using $\Theta(c,S_T,D_T)$ model) and useful comments in case of useless classification (when using $\Omega(c,S'_T,D'_T)$ model).
+%\dan{I thought we changed this! It would be bad if we didn't. Let me know what the actual situation is here.}
+%
+% Thai sez:  We did not. Maybe this is just a matter of wording. I believe what the text says is:
+%                - For useful classification, we only look for 3 scored comments.
+%                - For useless classification, we only look for 0 scored comments.
 
 From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from \TODO{.......}. 
-\pick{We cannot brute force for every floating number. How did we calculate this?} 
-\dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
+To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
+% \TODO{.......}. 
+% \pick{We cannot brute force for every floating number. How did we calculate this?} 
+% \dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
+% Thai sez: answered.
 

### 2014-07-28 sections/results.tex
Actually, we have 318 usable samples...

@@
 
-To answer this question, we randomly sampled 320 comments from our data set and manually identified usefulness as described in previous subsection.
+To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness as described in previous subsection.
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
@@
 
-From 320 samples, the number of labeled comments were 87, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-To estimated estimated similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
+From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
+To estimate similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
 % \TODO{.......}. 
@@
 Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
-\pick{I used dummy results.
-Please change it} \pick{What we got from this table?
-What information can we interpret?
-The threshold is slightly different?
-Is it good or bad?
-Please describes.}
+% \pick{I used dummy results. Please change it}
+\pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}
 
@@
 Useless & 69 & 23 & 7 & 6 \\
-Useful & 4 & 13 & 24 & 95 \\
+Useful & 3 & 12 & 24 & 95 \\
 Overlap & 1 & 1 & 0 & 1 \\

### 2014-07-28 sections/results.tex
Update with new data...

@@
 We also determined the effectiveness of our approach using bootstrapping cross validation:
-We randomly selected 90\% of 320 comments for training set and used the remaining 10\% for the validation set.
+We randomly selected 90\% of 318 comments for training set and used the remaining 10\% for the validation set.
 The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
@@
 
-Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F-measure score.
+Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
 % \pick{I used dummy results. Please change it}
@@
 \small
-\caption{Number of comments classified by our approach against ground truth data }
+\caption{Number of comments classified by our approach against ground truth data}
 \begin{tabular}{ccccc}
@@
 Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
-\multirow{7}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
-& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
-& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline \hline
-\multirow{7}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$} & 1 & 0.09028129266684175 & 2.245146382888072 &  1.00000 & 1.00000 & 1.00000 \\ \cline{2-7}
-& 2 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 3 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00& 1.00 \\ \cline{2-7}
-& 4 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& 5 & 0.09028129266684175 & 2.245146382888072 &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00  \\ \hline
+\multirow{5}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$}
+& 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
+& 2 & 0.015529 & 3.077129 & 0.740 & 0.693 & 0.795 \\ \cline{2-7}
+& 3 & 0.016713 & 2.494944 & 0.739 & 0.704 & 0.779 \\ \cline{2-7}
+& 4 & 0.015411 & 2.494944 & 0.738 & 0.696 & 0.787 \\ \cline{2-7}
+& 5 & 0.015411 & 3.077129 & 0.738 & 0.688 & 0.795
+% \\ \cline{2-7}
+% & \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
+\\ \hline \hline
+\multirow{5}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$}
+& 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
+& 2 & 0.087522 & 2.250422 & 0.722 & 0.642 & 0.824 \\ \cline{2-7}
+& 3 & 0.087522 & 2.324771 & 0.720 & 0.663 & 0.788 \\ \cline{2-7}
+& 4 & 0.052856 & 2.265679 & 0.719 & 0.645 & 0.812 \\ \cline{2-7}
+& 5 & 0.087522 & 2.249675 & 0.718 & 0.636 & 0.824
+% \\ \cline{2-7}
+%& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
+\\ \hline
 \end{tabular}

### 2014-07-28 sections/approach.tex

@@
 As discussed previously, this is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
-According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification \emph{similarity conditions}.
+According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}. 
 \dan{can we find a reference for relevance and similarly?}
+
 That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
-Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity} , the less relevant, and hence less useful.
+Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.
+
 Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
@@
 The key is determining these degrees in a practical and effective manner.
-While this representation is straightforward and automatically adjusts ti the quality of the data, it has a few drawbacks.
+While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
+
 First, we have to accept that some comments cannot be reliably or confidently classified.
-We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} i.e.
-unable to assess (subjectively) comment usefulness.
-Again, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This decreases the cost-effectiveness limiting the practicality of application to projects with a large enough number of comments whee the classification effort saved overcomes the training costs.
+We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
+Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
 % empirically driven and automatically adapts to the quality the data
+
 Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
@@
 In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.
-To calculate semantic similarity Fig.
-\ref{fig:overview}(a), we used the Vector Space Model (VSM) with the cosine distance measure which is a well-known technique for retrieving similar documents written in unstructured natural language.
-The Euclidian distance is a well-established measure of dissimilarity and applies analogously.
+
+% again, I can't see Fig. \ref{fig:overview}(a)
+% Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
+To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving similar documents written in unstructured natural language; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously.
 %For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
@@
 %\dan{what was the actual effort (in person-hours) to create the training data?}
-The training data is a small set of randomly-selected pairs of comments and corresponding commit messages are manually assessed for usefulness.
-For statistical purposes at least 30 useful and 30 useless comments are needed.
-The similarity and dissimilarities are computed for the data set.
+
+Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
+These comments are manually assessed for usefulness.
+For statistical purposes, at least 30 useful and 30 useless comments must be collected.
+The similarity and dissimilarities are then computed for the data set.
 These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
-Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows:
+
+Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
 \begin{itemize}
@@
 \item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
-\item \textbf{undetermined}: Neither of the above conditions are $\True$.
+\item \textbf{undetermined}: neither or both of the above conditions are $\True$.
+% We also refer to them as \emph{neither} and \emph{overlap}.
 \end{itemize}
@@
 
-The details of our approach are elaborated in the following subsections.
+% The details of our approach are elaborated in the following subsections.
 
@@
 
-We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize $\mathrm{F\text{-}measure}_{s_t,d_t}$ Equation \ref{eq:fmeasure}.
-This is a performance measurement for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
+We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
+which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
 
-The F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ is computed analogously where we change instances of useful to useless and vice-versa in the definitions.
+In this paper, we used the F$_1$ measure, which gives equal weight to both precision and recall.
+Depending on application, different weights can be given by choosing a different F$_\beta$ measure.
+
+% Thai sez: We did not mention the F-measure for \Theta, thus suddenly referring to \Omega does not make much sense...
+% The F-measure for $\Omega(c,S_T=s_t,D_T=d_t)$ is computed analogously where we change instances of useful to useless and vice-versa in the definitions.
 The correctness of classification is determined from the useful/useless defined dataset.

### 2014-07-28 sections/discussion.tex

% !TEX root = ../paper.tex
\section{Discussion}

% noisy data, and binary classification
Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear.
These samples cannot be classified as either useful or not useful.
This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.

% tuning the F score for precision and recall
Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
For instance, if we wanted to measure the amount of useful comments within a large dataset, we can give more weight to precision, sacrificing some good comments.
If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.
%\subsection{Reasons of Classification}
% reasons for classification as useful or not useful
During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

\begin{itemize}
	\item they contain new information;
	\item they contain constructive suggestions;
	\item they discuss directly about the change; and
	\item they discuss technical matters.
\end{itemize}

Examples of reasons for negative comments include:

\begin{itemize}
	\item chatting (i.e. no new information, just communication);
	\item not discussing directly about the change;
	\item discussing about the process workflow; and
	\item discussing about Git or Gerrit itself.
\end{itemize}

%\subsection{Binary Classification}

By removing the samples with scores of 1 and 2 from our data set, leaving with 209 samples without disagreements, we can perform a binary classification, in which all comments will receive either a positive or negative score.
By cross-validation using only samples in total agreement, we obtained a much better F$_1$ score of 0.896.

We could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
However, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.

\begin{figure}[h]
\centering
\includegraphics[width=3in]{binary}
\caption{The amount of comments by score classified by the binary classifier.}
\label{fig:binary}
\end{figure}

### 2014-07-28 sections/approach.tex
working on section 3

@@
 \section{Semantic Similarity Classification of Comment Usefulness}
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.34, trim = 50 90 0 30, clip=true]{overview2}
-\caption{Overview of our classification approach.}
-\label{fig:overview}
-\end{figure}
 
 Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
-As discussed previously, this is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
-According to relevance theory, a primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}. 
-\dan{can we find a reference for relevance and similarly?}
-
-That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
+We define a \emph{useful} comment as one that contributes to improving the proposed changes and a \emph{useless}\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.} comment as one that does not.
+Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
+Therefore, our approach is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
+A primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}\cite{Davies2012}. 
+%\dan{can we find a reference for relevance and similarly?}
+We assume that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
 Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.
@@
 While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
-
 First, we have to accept that some comments cannot be reliably or confidently classified.
@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.34, trim = 50 90 0 30, clip=true]{overview2}
+\caption{An overview of classification of comment usefulness using semantic similarity}
+\label{fig:overview}
+\end{figure}
+
+%\textbf{Approach Overview.} 
 Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
-Usefulness of a comment is determined by computing its semantic similarity with the commit message of proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
+Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
 The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
@@
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving similar documents written in unstructured natural language; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously.
+To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
 %For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
@@
 The similarity and dissimilarities are then computed for the data set.
-These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
+These are used to determine the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
 
-Using these thresholds, we can classify the usefulness of comments for the rest of comments in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
+%\textbf{Usefulness Classification Conditions.} 
+Using those thresholds, we can classify the usefulness of comments for the rest of comments (as test data) in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
 \begin{itemize}
@@
 
-The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$.
+The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance respectively.
 Two metrics are used because they are independently generated and thus provides better discrimination for classification.

### 2014-07-28 scripts_for_thaipang/scatter_graph.R

@@ -1,9 +1,9 @@
 dat <- read.csv("scatter_value.csv")
 dat$Similarity[which(dat$Similarity == 0)] = 0.000000001 
-St1 = 0.015528
-Dt1 = 2.494944
-St2 = 0.087522
-Dt2 = 2.265679 
+St1 = 0.015528969196702956
+Dt1 = 2.4949438168165483
+St2 = 0.08752176628812282
+Dt2 = 2.26567908457803
 
 colors = c("red","darkorange","blue","darkgreen")
 pch = c(4,2,3,16)

### 2014-07-28 sections/approach.tex
updated lots of text

--- 2014-07-28 sections/approach.tex
@@
 These comments are manually assessed for usefulness.
+Each comment is assessed by three different people independently.
+For each \texttt{YES} vote, a single point is given to that comment.
+This means that a comment will receive a score of 0, 1, 2, or 3.
 For statistical purposes, at least 30 useful and 30 useless comments must be collected.
-The similarity and dissimilarities are then computed for the data set.
+
+The similarity and dissimilarity metrics are then computed for the data set.
 These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.

### 2014-07-28 sections/discussion.tex
updated lots of text

@@
 % noisy data, and binary classification
-Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear.
-These samples cannot be classified as either useful or not useful.
+Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
 This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
@@
 Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
-For instance, if we wanted to measure the amount of useful comments within a large dataset, we can give more weight to precision, sacrificing some good comments.
-If we wanted to modify a code review software such that it displays useful comments more prominently, we can give more weight to recall.
+For instance, if we wanted to measure the amount of useful comments within a large dataset, more weight can be given to precision, sacrificing some useful comments.
+If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.
+
 %\subsection{Reasons of Classification}
@@
 
-By removing the samples with scores of 1 and 2 from our data set, leaving with 209 samples without disagreements, we can perform a binary classification, in which all comments will receive either a positive or negative score.
-By cross-validation using only samples in total agreement, we obtained a much better F$_1$ score of 0.896.
+Another approach we tried is to perform a \emph{binary classification}.
+This means we assume that there are no unclear on undetermined comments; only useful and useless.
+For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
+By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.
 
@@
 \centering
-\includegraphics[width=3in]{binary}
+\includegraphics[width=3in]{posneg}
 \caption{The amount of comments by score classified by the binary classifier.}

### 2014-07-28 sections/approach.tex

--- 2014-07-28 sections/approach.tex
@@
 These comments are manually assessed for usefulness.
+Each comment is assessed by three different people independently.
+For each \texttt{YES} vote, a single point is given to that comment.
+This means that a comment will receive a score of 0, 1, 2, or 3.
 For statistical purposes, at least 30 useful and 30 useless comments must be collected.
-The similarity and dissimilarities are then computed for the data set.
-These are used to determine the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
+
+The similarity and dissimilarity metrics are then computed for the data set.
+These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
 

### 2014-07-28 sections/results.tex

@@
 All Comments & 72,484& - \\ \hline
-Reviewers Comments & 10,670 & 15\% \\ \hline
+Reviewers Comments & 10,583 & 15\% \\ \hline
 Automated Comments & 61,814 & 85\% \\ \hline
@@
 
-\textbf{Model Effectiveness.} Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
-The green area represents useful model $\Theta(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$ and the red area represents useless classification model $\Omega(c,S_T=0.09028129266684175,D_T= 2.245146382888072)$.
+\textbf{Model Effectiveness.}
+Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
+The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S_T=0.087522,D_T=2.265679)$.
 This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
-As shown in the figure, most of comments fall in green area is useful comments and very few useless comments fall in this area.
-Similarly, most of comments fall in red area is useless comments.
+
+As shown in the figure, most comments falling in green area are useful comments, while very few useless comments fall in this area.
+Similarly, most comments in the red area are considered useless.
 However, some comments were not determined (in white area).
-From the example comment, it shows that these comments discussed on .....
-which did not contains any similar words.
-Moreover, the areas of these two models are overlap.
+From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
+Some areas of these two models overlap, making results undeterminable.
+
 Table \ref{tb:classify_number} summarizes the number of classification from this results.
-Interestingly, 87\% useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
-This is same as the results of useful class that most of them have \texttt{YES} = 2 and 3 voting scores
-This finding suggests that these unclear comments have something.....
+Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
+From useful class, a similar proportion is obtained---that most useful comments have \texttt{YES} = 2 and 3 voting scores
 
@@
 Useless & 69 & 23 & 7 & 6 \\
-Useful & 3 & 12 & 24 & 95 \\
+Useful & 3 & 12 & 24 & 94 \\
 Overlap & 1 & 1 & 0 & 1 \\
-Undetermined & 12 & 24 & 20 & 20 \\
+Undetermined & 12 & 24 & 20 & 21 \\
 \hline
@@
 This indicates that we can use our approach to classify with confident of 69.8\%.
-\pick{Precision? Recall?}
+\pick{Precision? Recall?} \thai{This is some confidence interval...}
 
-According to the results, we can answer  RQ1 that \textit{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}
+According to the results, we can answer RQ1 that \emph{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}
 
@@
 
-\noindent \textbf{RQ2: Do code reviewers intensively discuss on the proposed changes?}\\
-\indent To answer this question, we estimated similarity and dissimilarity thresholds using comments from RQ1 for training set.
-We then used these thresholds to classify the rest of comments.
-A statical analysis was performed to understand the impact of useful discussion to software quality.
-\pick{The questions: How many \% automatic / useful/ useless/ unclear messages for each reviews? Does these numbers have a relationship with factor of code review (e.g. reviewing time)?}
+\begin{ResearchQuestions}
+\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
+\end{ResearchQuestions}
 
-\pick{If there is high \% of useless messages, it means ineffective review, isn't it?}
+To answer this question, timestamps are recorded as three people assess each comment.
+Since three people work on their leisure time, there is much variability in the time between each vote.
+Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
 
-\noindent \textbf{RQ3: Is semantic similarity classification cost-efficient, assur- able, and scalable?}\\
+On average, it takes 28 seconds to assess each comment.
+However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess; only few comments take long time.
+This also suggests that the time to assess each comment is not normally distributed.
+The standard deviation is 45 seconds.
 
-%\subsection{Model Generation}
+To estimate the total time for us to assess these 318 comments,
+we multiplied the average time by the number of comments and the number of people.
+This results in $\frac{318 \times 28 \times 3}{3600 \text{ seconds/hour}} = 7.42$ person hours.
 
-%% the criteria that were found
-%From our training data,
-%the following criteria have been obtained that maximizes the F$_1$ score:
-%
-%Criteria to find samples with score of 3 (``positive''):
-%\begin{gather*} similarity \geq 0.015528 \text{ and } distance \leq 2.494944
-%\\ \text{(F$_1$-score: 0.741313)} \end{gather*}
-%
-%Criteria to find samples with score of 0 (``negative''):
-%\begin{gather*} similarity \leq 0.087522 \text{ and } distance \geq 2.265679
-%\\ \text{(F$_1$-score: 0.725389)}\end{gather*}
-%
-%Note that these constant values can vary from project to project, and thus is not a universal constant.
-%
-%% run result
-%
-%Running our model against the training data gives us the result displayed in the following table.
-%In the table, \emph{Neither} means that the comment did not meet either criteria, while \emph{Overlap} means that the comment  met both ``positive'' and ``negative'' criteria.
-%
-%\begin{center}
-%\begin{tabular}{|r|rrrr|}
-%\hline
-%& \bfseries 0 & \bfseries 1 & \bfseries 2 & \bfseries 3 \\
-%\hline
-%Negative & 69 & 23 & 7 & 6 \\
-%Neither & 12 & 24 & 20 & 20 \\
-%Overlap & 1 & 1 & 0 & 1 \\
-%Positive & 4 & 13 & 24 & 95 \\
-%\hline
-%\end{tabular}
-%\end{center}
-%
-%As expected, most comments classified as \emph{negative} have score of 0 and 1,
-%while most \emph{positive} comments have score of 2 and 3.
-%However, some comments in every score type were classified as \emph{neither}.
-%
-%
-
-% cross validation result
+To manually assess all 10,583 comments---even with only one person working at 10 comments per minute---this would take 17.6 person hours.
+By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
+That means that about 77\% of the effort is saved.

### 2014-07-28 sections/approach.tex
more refactorings

--- 2014-07-28 sections/approach.tex
@@
 That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
-Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.
+Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity.}, the less relevant, and hence less useful.
 
@@
 The key is determining these degrees in a practical and effective manner.
-While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
-
-First, we have to accept that some comments cannot be reliably or confidently classified.
-We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
-Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
-% empirically driven and automatically adapts to the quality the data
 
@@
 
+% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
+While our proposed approach is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
+First, we have to accept that some comments cannot be reliably or confidently classified.
+We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
+Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+% empirically driven and automatically adapts to the quality the data
+
 % Thai sez: We did not mention the F-measure for \Theta, thus suddenly referring to \Omega does not make much sense...

### 2014-07-28 sections/introduction.tex
lots of change to the paper text.
use enumitems for better research questions styling
Now going through the results.
working on section 3
more refactorings

@@
 coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
-This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.%This is a concern because lack of useful comments can degrade the cost-effectiveness and perceived utility of MCR.
+%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
+This is a concern because a low-degree of useful comments can degrade the overall quality and perceived utility of MCR.
 
@@
 Through a case study of Qt project, we address the following research questions:
-\begin{description}
+\begin{ResearchQuestions}
 \item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
 \item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
-\end{description}
+\end{ResearchQuestions}
 
@@
 \begin{itemize}
-\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness based on using semantic similarity.
+\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness using semantic similarity.
 \item We investigate relationship between usefulness of comments and semantic similarity.

### 2014-07-28 sections/discussion.tex
discussion

@@
 If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.
+
+% examples.
+In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
+due to the same word being used in a different context.
+For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
+better code generation with GCC at least.''}
+This comment, \emph{``I'll study the generated code a bit more,''} is not technically contributing, but is classified as a useful comment, which may be because of the word \emph{generate} appears both documents.
 
@@
 Another approach we tried is to perform a \emph{binary classification}.
-This means we assume that there are no unclear on undetermined comments; only useful and useless.
+This means we assume that there are no unclear or undetermined comments; only useful and useless.
 For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
@@
 \centering
-\includegraphics[width=3in]{posneg}
+\includegraphics[width=2.5in]{posneg}
 \caption{The amount of comments by score classified by the binary classifier.}

### 2014-07-28 sections/results.tex
add from and to date
removed a sentence about explaining the example. Move to discussion.

@@
 We selected the most active subproject, which is called \texttt{qtbase}.
-From this subproject, we used the review history before June 13\textsuperscript{th}, 2012, which contains 6,605 changes and 72,484 comments.
+From this subproject, we used the review history from May 25, 2011 to June 13, 2012, which contains 6,605 changes and 72,484 comments.
 
@@
 However, some comments were not determined (in white area).
-From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
 Some areas of these two models overlap, making results undeterminable.

### 2014-07-28 sections/results.tex
fixed some notations
working on cast study

--- 2014-07-28 sections/results.tex
@@
 
-\subsubsection{Removal of automatically generated messages}
-In Gerrit, the comments are composed of human-written comments from reviewers and automatically generated messages.
+\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
+%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
 These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
-\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples of these messages.
+For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}.
+In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
 
-Since these messages are generally record keeping,
-they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
-In practice, they are not considered in code review.
-They are easily determined as useless by our method and would artificially improve our classification performance.
+To do so, we first ignore all comments written by bots i.e.
+\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
+Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression.
+This would leave us only human-written comments that will be used in further preprocessing.
 
-These messages are identified by looking for the most common lines of text.
-Regular expression patterns are then constructed to match these messages.
-Occurrences of these patterns are then removed from our dataset prior to further preprocessing.
-
-Automatic messages are also often inserted as part of review comments.
-They too are removed from our dataset, leaving us with only human-written part.
-We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
+%, . and hence are useless by our definition.
+%%They are easily determined as useless by our method and would artificially improve our classification performance.
+%These messages are identified by looking for the most common lines of text using regular expression.
+%%Regular expression patterns are then constructed to match and remove these messages.
+%Occurrences of these patterns are then removed from our dataset prior to further preprocessing.
+%
+%Automatic messages are also often inserted as part of review comments.
+%They too are removed from our dataset, leaving us with only human-written part.
+%We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
 
@@
 
-To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness as described in previous subsection.
+\textbf{Approach.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
-We also determined the effectiveness of our approach using bootstrapping cross validation:
+We also determined the effectiveness of our approach using bootstrapping cross validation.
 We randomly selected 90\% of 318 comments for training set and used the remaining 10\% for the validation set.
-The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
+The performance on the 10\% was measured using precision, recall and F-measure.
 This validation was repeated for 300 times to estimate the mean and variance of the performance.
 
+To manually assess comment usefulness, three participants (the first two authors and one student) independently classify comments by giving a question that “Does this comment technically contribute to its change or not?”.
+Then, the participants gave a vote for \texttt{YES} if the comment is likely to useful and  \texttt{NO}  if the comment is likely to useless.
+From the voting scores, we regarded that the comments with three  \texttt{YES}  votes are \emph{useful} comments and the comments with no  \texttt{YES}  votes (i.e.
+three  \texttt{NO}  votes) are \emph{useless} comments.
+For the comments with one and two YES’ votes, we defined them as unclear comments.
 % \dan{What what the effort in person-hours for this?}
@@
 From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-To estimate similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
-% \TODO{.......}. 
-% \pick{We cannot brute force for every floating number. How did we calculate this?} 
-% \dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
-% Thai sez: answered.
+To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
+Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
+We selected the first rank of thresholds for the further analysis and applied models, i.e.
+useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
 
-Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-% \pick{I used dummy results. Please change it}
-\pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}
+\textbf{Classification Result:}  We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
+We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}.
+The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.
+Thus, the comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless.
+While, the comments drawn in the white area are those not satisfied any condition (i.e.
+undetermined).
+%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
 
-\textbf{Model Effectiveness.}
-Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
-The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S_T=0.087522,D_T=2.265679)$.
-This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
+%%Interpret: comments & model%%%%
+As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area.
+Similarly, most comments in the red area are useless.
+The unclear comments are drawn in both area.
+Between these areas, there is an overlap section.
+This is because the similarity and dissimilarity values between useful and useless are vague.
+Both models tend to maximize coverage of classification.
+Thus, it is possible that there is overlap between these two models.
+However, from the results, there are few comments drawn in this overlap section.
+This shows that error of our model is low.
+For comments that were undetermined (drawn in white area), we investigate characteristics of these comments. The findings are described in our discussion section.
+%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
 
-As shown in the figure, most comments falling in green area are useful comments, while very few useless comments fall in this area.
-Similarly, most comments in the red area are considered useless.
-However, some comments were not determined (in white area).
-From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
-Some areas of these two models overlap, making results undeterminable.
+%%Interpret: comments & similarity values%%%%
+The graph also shows that the useful comments have less distance (not higher than 3 approximately) while most of useless comments have zero similarity.
+However, the unclear comments are still spread out over the graph which we cannot determine relationship between their similarity.
+Furthermore, it is interesting that comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity.
+This indicates that the comments  in each group have relationship other than similarity.
+This led us to investigate insight into these comments to find other properties in our future work.
 
-Table \ref{tb:classify_number} summarizes the number of classification from this results.
-Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
-From useful class, a similar proportion is obtained---that most useful comments have \texttt{YES} = 2 and 3 voting scores
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
+\caption{The similarity and distance plot of the training data.
+The symbol represents the score, which ranges from 0 to 3.}
+\label{fig:scatter}
+\end{figure}
+
+From Table \ref{tb:classify_number}, Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
+The similar proportion is obtained for useful comments classified by our model i.e. most useful comments have \texttt{YES} = 2 and 3 voting scores.
 
@@
 \hline
-& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
+& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
 Our&  Useless  & Unclear  & Unclear & Useful \\
@@
 Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
-\multirow{5}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$}
+\multirow{5}{*}{\textbf{useful}: $\Theta(c,S_T=s_t,D_T=d_t)$}
 & 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
@@
 \\ \hline \hline
-\multirow{5}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$}
+\multirow{5}{*}{\textbf{useless}: $\Omega(c,S_T=s_t,D_T=d_t)$}
 & 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
@@
 
-\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
+\textbf{Validation} After we performed cross validation, we obtained the following result:
 for useful and useless classifications,
@@
 %This is because the comment text and the corresponding commit message has no word in comment.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
-\caption{The similarity and distance plot of the training data.
-The symbol represents the score, which ranges from 0 to 3.}
-\label{fig:scatter}
-\end{figure}
 

### 2014-07-28 scripts_for_thaipang/scatter_graph.R

@@ -5,7 +5,7 @@ Dt1 = 2.4949438168165483
 St2 = 0.08752176628812282
 Dt2 = 2.26567908457803
 
-colors = c("red","darkorange","blue","darkgreen")
+colors = c("red","magenta","blue","darkgreen")
 pch = c(4,2,3,16)
 
 #Print Graph with Log

### 2014-07-28 sections/discussion.tex
elaborated on the example

@@
 better code generation with GCC at least.''}
-This comment, \emph{``I'll study the generated code a bit more,''} is not technically contributing, but is classified as a useful comment, which may be because of the word \emph{generate} appears both documents.
+This comment, \emph{``I'll study the generated code a bit more,''} is just an author's response, and thus is not technically contributing.
+However, it is classified as a useful comment.
+This may be caused by the word \emph{generate} which appears in both documents.
 

### 2014-07-28 sections/approach.tex
joined sentences about F1 score
drawbacks
reorder

--- 2014-07-28 sections/approach.tex
@@
 
+\pick{Thai version}
+That is, we assume that that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
+Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity.}, the less relevant, and hence less useful.
+
 Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
@@
 The key is determining these degrees in a practical and effective manner.
+
+\pick{Thai move this section}
 While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
@@
 which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
-
 In this paper, we used the F$_1$ measure, which gives equal weight to both precision and recall.
 Depending on application, different weights can be given by choosing a different F$_\beta$ measure.
+
+% Our proposed approach is empirically driven and automatically adjusts to the quality the data.
+While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
+First, we have to accept that some comments cannot be reliably or confidently classified.
+We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
+Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+% empirically driven and automatically adapts to the quality the data
 

### 2014-07-28 sections/discussion.tex

--- 2014-07-28 sections/discussion.tex
@@
 better code generation with GCC at least.''}
-This comment, \emph{``I'll study the generated code a bit more,''} is not technically contributing, but is classified as a useful comment, which may be because of the word \emph{generate} appears both documents.
+This comment, \emph{``I'll study the generated code a bit more,''} is not technically contributing, but is classified as a useful comment, which may be caused by the word \emph{generate} which appears in both documents.
 

### 2014-07-28 sections/results.tex

@@
 From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
+
 To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
@@
 The similar proportion is obtained for useful comments classified by our model i.e. most useful comments have \texttt{YES} = 2 and 3 voting scores.
+
+\pick{Thai version}
+To estimate similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
+% \TODO{.......}. 
+% \pick{We cannot brute force for every floating number. How did we calculate this?} 
+% \dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
+% Thai sez: answered.
+
+Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
+% \pick{I used dummy results. Please change it}
+\pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}
+
+\textbf{Model Effectiveness.}
+Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
+The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S_T=0.087522,D_T=2.265679)$.
+This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
+
+As shown in the figure, most comments falling in green area are useful comments, while very few useless comments fall in this area.
+Similarly, most comments in the red area are considered useless.
+However, some comments were not determined (in white area).
+Some areas of these two models overlap, making results undeterminable.
+
+Table \ref{tb:classify_number} summarizes the number of classification from this results.
+Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
+From useful class, a similar proportion is obtained---that most useful comments have \texttt{YES} = 2 and 3 voting scores
 
@@
 we multiplied the average time by the number of comments and the number of people.
-This results in $\frac{318 \times 28 \times 3}{3600 \text{ seconds/hour}} = 7.42$ person hours.
+This results in 7.42 person hours.
 

### 2014-07-28 sections/approach.tex
fix from merge in approach

--- 2014-07-28 sections/approach.tex
@@
 The key is determining these degrees in a practical and effective manner.
-While this representation is straightforward and automatically adjusts to the quality of the data, it has a few drawbacks.
-First, we have to accept that some comments cannot be reliably or confidently classified.
-We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
-Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
-% empirically driven and automatically adapts to the quality the data
 
@@
 These comments are manually assessed for usefulness.
-Each comment is assessed by three different people independently.
-For each \texttt{YES} vote, a single point is given to that comment.
-This means that a comment will receive a score of 0, 1, 2, or 3.
+%Each comment is assessed by three different people independently.
+%For each \texttt{YES} vote, a single point is given to that comment.
+%This means that a comment will receive a score of 0, 1, 2, or 3.
 For statistical purposes, at least 30 useful and 30 useless comments must be collected.
-
 The similarity and dissimilarity metrics are then computed for the data set.

### 2014-07-28 sections/results.tex
fix merge in result section

--- 2014-07-28 sections/results.tex
@@
 \end{table}
+\subsection{Manual Comment Usefulness Assessment}
+In this case study, three participants (the first two authors and one student) independently classify comments by giving a question that “Does this comment technically contribute to its change or not?”.
+Then, the participants gave a vote for \texttt{YES} if the comment is likely to useful and  \texttt{NO}  if the comment is likely to useless.
+From the voting scores, we regarded that the comments with three  \texttt{YES}  votes are \emph{useful} comments and the comments with no  \texttt{YES}  votes (i.e.
+three  \texttt{NO}  votes) are \emph{useless} comments.
+For the comments with one and two YES’ votes, we defined them as unclear comments.
 
 \subsection{Research Questions}
-
+To validate our approach, we addressed two research questions: \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?
+and \textbf{RQ2:} Is semantic similarity classification cost-efficient, assurable, and scalable?.
+\pick{Do we need motivation for these RQs?}
 %\pick{I realize that your figure is better for the presentation :)}
@@
 %This means that each document will be converted into a vector of 20,025 dimensions, each dimension representing a single word.
-%
 
@@
 
-\textbf{Approach.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
+\textbf{Methodology.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
@@
 
-To manually assess comment usefulness, three participants (the first two authors and one student) independently classify comments by giving a question that “Does this comment technically contribute to its change or not?”.
-Then, the participants gave a vote for \texttt{YES} if the comment is likely to useful and  \texttt{NO}  if the comment is likely to useless.
-From the voting scores, we regarded that the comments with three  \texttt{YES}  votes are \emph{useful} comments and the comments with no  \texttt{YES}  votes (i.e.
-three  \texttt{NO}  votes) are \emph{useless} comments.
-For the comments with one and two YES’ votes, we defined them as unclear comments.
 % \dan{What what the effort in person-hours for this?}
@@
 Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the first rank of thresholds for the further analysis and applied models, i.e.
+We selected the first rank of thresholds and applied models, i.e.
 useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
+The precision and Recall of these models are 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
 
-\textbf{Classification Result:}  We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
+\textbf{Classification Results:}  We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
 We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}.
@@
 Thus, it is possible that there is overlap between these two models.
-However, from the results, there are few comments drawn in this overlap section.
-This shows that error of our model is low.
-For comments that were undetermined (drawn in white area), we investigate characteristics of these comments. The findings are described in our discussion section.
+However, from the results in Table \ref{tb:classify_number}, only three comments were classified overlap section.
+This shows that error of our models is low.
+Furthermore, there are 12 useless comments  (14\%) and  21 useful comments (17\%) still are undetermined (drawn in white area).
+We investigate characteristics of these comments.
+The findings are described in our discussion section.
 %From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
@@
 
-\begin{table}[h]
-\centering
-\small
-\caption{Number of comments classified by our approach against ground truth data}
-\begin{tabular}{ccccc}
-\hline
-& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
-Our&  Useless  & Unclear  & Unclear & Useful \\
-Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
-\hline \hline
-Useless & 69 & 23 & 7 & 6 \\
-Useful & 3 & 12 & 24 & 94 \\
-Overlap & 1 & 1 & 0 & 1 \\
-Undetermined & 12 & 24 & 20 & 21 \\
-\hline
-\end{tabular}
-\label{tb:classify_number}
-\end{table}
-
 \begin{table*}[!t]
@@
 \\ \hline \hline
-\multirow{5}{*}{\textbf{useless}: $\Omega(c,S_T=s_t,D_T=d_t)$}
+\multirow{5}{*}{\textbf{useless}: $\Omega(c,S'_T=s_t,D'_T=d_t)$}
 & 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
@@
 \end{table*}
+
+\begin{table}[h]
+\centering
+\small
+\caption{Number of comments classified by our approach against ground truth data}
+\begin{tabular}{ccccc}
+\hline
+& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
+Our&  Useless  & Unclear  & Unclear & Useful \\
+Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
+\hline \hline
+Useful & 3 & 12 & 24 & 94 \\
+Useless & 69 & 23 & 7 & 6 \\
+Overlap & 1 & 1 & 0 & 1 \\
+Undetermined & 12 & 24 & 20 & 21 \\
+\hline
+\end{tabular}
+\label{tb:classify_number}
+\end{table}
 

### 2014-07-28 sections/results.tex
working on result RQ1

@@
 
-From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
 To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
@@
 useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
-The precision and Recall of these models are 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
 
-\textbf{Classification Results:}  We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
+\textbf{Classification Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
+The precision and Recall of the models are 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
+We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
 We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}.
@@
 
-From Table \ref{tb:classify_number}, Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
-The similar proportion is obtained for useful comments classified by our model i.e. most useful comments have \texttt{YES} = 2 and 3 voting scores.
+Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores.
+The classification of useless comments also have similar proportion i.e.
+having high number of comment with \texttt{YES} = 0 and 1 voting scores.
+It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
+Due to subjective and error-prone manual classification, these comments were not received three voting scores.
+This suggests us to re-examine the comments again.
+\pick{I'm not sure if comments with vote 2 are highly classified as useful and comments with vote 1 are highly classified as useless, what will we do.}
 
-\begin{table*}[!t]
-\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
-\hline
-Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
-\multirow{5}{*}{\textbf{useful}: $\Theta(c,S_T=s_t,D_T=d_t)$}
-& 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
-& 2 & 0.015529 & 3.077129 & 0.740 & 0.693 & 0.795 \\ \cline{2-7}
-& 3 & 0.016713 & 2.494944 & 0.739 & 0.704 & 0.779 \\ \cline{2-7}
-& 4 & 0.015411 & 2.494944 & 0.738 & 0.696 & 0.787 \\ \cline{2-7}
-& 5 & 0.015411 & 3.077129 & 0.738 & 0.688 & 0.795
-% \\ \cline{2-7}
-% & \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
-\\ \hline \hline
-\multirow{5}{*}{\textbf{useless}: $\Omega(c,S'_T=s_t,D'_T=d_t)$}
-& 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
-& 2 & 0.087522 & 2.250422 & 0.722 & 0.642 & 0.824 \\ \cline{2-7}
-& 3 & 0.087522 & 2.324771 & 0.720 & 0.663 & 0.788 \\ \cline{2-7}
-& 4 & 0.052856 & 2.265679 & 0.719 & 0.645 & 0.812 \\ \cline{2-7}
-& 5 & 0.087522 & 2.249675 & 0.718 & 0.636 & 0.824
-% \\ \cline{2-7}
-%& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
-\\ \hline
-\end{tabular}
-\label{tb:thresholds}
-\end{table*}
+%\begin{table*}[!t]
+%\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
+%\small
+%\centering
+%\def\arraystretch{1.2}
+%\begin{tabular}{ccccccc}
+%\hline
+%Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
+%\multirow{5}{*}{\textbf{useful}: $\Theta(c,S_T=s_t,D_T=d_t)$}
+%& 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
+%& 2 & 0.015529 & 3.077129 & 0.740 & 0.693 & 0.795 \\ \cline{2-7}
+%& 3 & 0.016713 & 2.494944 & 0.739 & 0.704 & 0.779 \\ \cline{2-7}
+%& 4 & 0.015411 & 2.494944 & 0.738 & 0.696 & 0.787 \\ \cline{2-7}
+%& 5 & 0.015411 & 3.077129 & 0.738 & 0.688 & 0.795
+%% \\ \cline{2-7}
+%% & \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+%%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
+%\\ \hline \hline
+%\multirow{5}{*}{\textbf{useless}: $\Omega(c,S'_T=s_t,D'_T=d_t)$}
+%& 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
+%& 2 & 0.087522 & 2.250422 & 0.722 & 0.642 & 0.824 \\ \cline{2-7}
+%& 3 & 0.087522 & 2.324771 & 0.720 & 0.663 & 0.788 \\ \cline{2-7}
+%& 4 & 0.052856 & 2.265679 & 0.719 & 0.645 & 0.812 \\ \cline{2-7}
+%& 5 & 0.087522 & 2.249675 & 0.718 & 0.636 & 0.824
+%% \\ \cline{2-7}
+%%& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
+%%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
+%\\ \hline
+%\end{tabular}
+%\label{tb:thresholds}
+%\end{table*}
 
@@
 
-\textbf{Validation} After we performed cross validation, we obtained the following result:
-for useful and useless classifications,
-we obtained an average F$_1$ score of 0.693 and 0.681,
-with standard deviation of 0.090 and 0.118, respectively.
-This indicates that we can use our approach to classify with confident of 69.8\%.
-\pick{Precision? Recall?} \thai{This is some confidence interval...}
+\textbf{Validation.} After validating our approach using bootstrapping cross validation with 300 iterations, for the random select test datasets, we obtained the results described in Table \ref{}.
+
+%the average of F-measure score are 0.6
+%
+%After we performed cross validation, we obtained the following result:
+%for useful and useless classifications,
+%we obtained an average F$_1$ score of 0.693 and 0.681,
+%with standard deviation of 0.090 and 0.118, respectively.
+%This indicates that we can use our approach to classify with confident of 69.8\%.
+%\pick{Precision? Recall?} \thai{This is some confidence interval...}
 

### 2014-07-28 sections/results.tex
make the threshould table only one row for each model

--- 2014-07-28 sections/results.tex
@@
 
-\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
-%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
+\subsubsection{Removal of automatically generated messages}
+In Gerrit, the comments are composed of human-written comments from reviewers and automatically generated messages.
 These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
-For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}.
-In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
+\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples of these messages.
 
-To do so, we first ignore all comments written by bots i.e.
-\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
-Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression.
-This would leave us only human-written comments that will be used in further preprocessing.
+Since these messages are generally record keeping,
+they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
+In practice, they are not considered in code review.
+They are easily determined as useless by our method and would artificially improve our classification performance.
 
-%, . and hence are useless by our definition.
-%%They are easily determined as useless by our method and would artificially improve our classification performance.
-%These messages are identified by looking for the most common lines of text using regular expression.
-%%Regular expression patterns are then constructed to match and remove these messages.
-%Occurrences of these patterns are then removed from our dataset prior to further preprocessing.
-%
-%Automatic messages are also often inserted as part of review comments.
-%They too are removed from our dataset, leaving us with only human-written part.
-%We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
+These messages are identified by looking for the most common lines of text.
+Regular expression patterns are then constructed to match these messages.
+Occurrences of these patterns are then removed from our dataset prior to further preprocessing.
+
+Automatic messages are also often inserted as part of review comments.
+They too are removed from our dataset, leaving us with only human-written part.
+We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
 
@@
 
-\textbf{Approach.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
+To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness as described in previous subsection.
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
-We also determined the effectiveness of our approach using bootstrapping cross validation.
+We also determined the effectiveness of our approach using bootstrapping cross validation:
 We randomly selected 90\% of 318 comments for training set and used the remaining 10\% for the validation set.
-The performance on the 10\% was measured using precision, recall and F-measure.
+The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
 This validation was repeated for 300 times to estimate the mean and variance of the performance.
 
-To manually assess comment usefulness, three participants (the first two authors and one student) independently classify comments by giving a question that “Does this comment technically contribute to its change or not?”.
-Then, the participants gave a vote for \texttt{YES} if the comment is likely to useful and  \texttt{NO}  if the comment is likely to useless.
-From the voting scores, we regarded that the comments with three  \texttt{YES}  votes are \emph{useful} comments and the comments with no  \texttt{YES}  votes (i.e.
-three  \texttt{NO}  votes) are \emph{useless} comments.
-For the comments with one and two YES’ votes, we defined them as unclear comments.
 % \dan{What what the effort in person-hours for this?}
@@
 From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-
-To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
-Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the first rank of thresholds for the further analysis and applied models, i.e.
-useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
-
-\textbf{Classification Result:}  We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
-We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}.
-The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.
-Thus, the comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless.
-While, the comments drawn in the white area are those not satisfied any condition (i.e.
-undetermined).
-%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
-
-%%Interpret: comments & model%%%%
-As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area.
-Similarly, most comments in the red area are useless.
-The unclear comments are drawn in both area.
-Between these areas, there is an overlap section.
-This is because the similarity and dissimilarity values between useful and useless are vague.
-Both models tend to maximize coverage of classification.
-Thus, it is possible that there is overlap between these two models.
-However, from the results, there are few comments drawn in this overlap section.
-This shows that error of our model is low.
-For comments that were undetermined (drawn in white area), we investigate characteristics of these comments. The findings are described in our discussion section.
-%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
-
-%%Interpret: comments & similarity values%%%%
-The graph also shows that the useful comments have less distance (not higher than 3 approximately) while most of useless comments have zero similarity.
-However, the unclear comments are still spread out over the graph which we cannot determine relationship between their similarity.
-Furthermore, it is interesting that comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity.
-This indicates that the comments  in each group have relationship other than similarity.
-This led us to investigate insight into these comments to find other properties in our future work.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
-\caption{The similarity and distance plot of the training data.
-The symbol represents the score, which ranges from 0 to 3.}
-\label{fig:scatter}
-\end{figure}
-
-From Table \ref{tb:classify_number}, Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
-The similar proportion is obtained for useful comments classified by our model i.e. most useful comments have \texttt{YES} = 2 and 3 voting scores.
-
-\pick{Thai version}
 To estimate similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
@@
 
-Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-% \pick{I used dummy results. Please change it}
-\pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}
+Table \ref{tb:thresholds} shows the thresholds that best classify useful and useless comments based on F-measure.
+
+\begin{table*}[!t]
+\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{ccccccc}
+\hline
+Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
+$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
+$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
+\end{tabular}
+\label{tb:thresholds}
+\end{table*}
 
@@
 \hline
-& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
+& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
 Our&  Useless  & Unclear  & Unclear & Useful \\
@@
 
-\begin{table*}[!t]
-\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
-\hline
-Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
-\multirow{5}{*}{\textbf{useful}: $\Theta(c,S_T=s_t,D_T=d_t)$}
-& 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
-& 2 & 0.015529 & 3.077129 & 0.740 & 0.693 & 0.795 \\ \cline{2-7}
-& 3 & 0.016713 & 2.494944 & 0.739 & 0.704 & 0.779 \\ \cline{2-7}
-& 4 & 0.015411 & 2.494944 & 0.738 & 0.696 & 0.787 \\ \cline{2-7}
-& 5 & 0.015411 & 3.077129 & 0.738 & 0.688 & 0.795
-% \\ \cline{2-7}
-% & \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
-\\ \hline \hline
-\multirow{5}{*}{\textbf{useless}: $\Omega(c,S_T=s_t,D_T=d_t)$}
-& 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
-& 2 & 0.087522 & 2.250422 & 0.722 & 0.642 & 0.824 \\ \cline{2-7}
-& 3 & 0.087522 & 2.324771 & 0.720 & 0.663 & 0.788 \\ \cline{2-7}
-& 4 & 0.052856 & 2.265679 & 0.719 & 0.645 & 0.812 \\ \cline{2-7}
-& 5 & 0.087522 & 2.249675 & 0.718 & 0.636 & 0.824
-% \\ \cline{2-7}
-%& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
-%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
-\\ \hline
-\end{tabular}
-\label{tb:thresholds}
-\end{table*}
-
-\textbf{Validation} After we performed cross validation, we obtained the following result:
+\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
 for useful and useless classifications,
@@
 %This is because the comment text and the corresponding commit message has no word in comment.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
+\caption{The similarity and distance plot of the training data.
+The symbol represents the score, which ranges from 0 to 3.}
+\label{fig:scatter}
+\end{figure}
 

### 2014-07-28 sections/results.tex
add cross validation table

@@
 
-\begin{table*}[!t]
-\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
-\hline
-Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
-$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
-$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
-\end{tabular}
-\label{tb:thresholds}
-\end{table*}
-
 \textbf{Model Effectiveness.}
 Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
-The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S_T=0.087522,D_T=2.265679)$.
-This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
+The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S'_T=0.087522,D'_T=2.265679)$.
+% This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
+% Thai sez: Comment examples are in the discussion.
 
@@
 
-\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
-for useful and useless classifications,
-we obtained an average F$_1$ score of 0.693 and 0.681,
-with standard deviation of 0.090 and 0.118, respectively.
-This indicates that we can use our approach to classify with confident of 69.8\%.
-\pick{Precision? Recall?} \thai{This is some confidence interval...}
+\textbf{Model Robustness.} After we performed bootstrapping cross validation, we obtained the result as shown in Table \ref{tb:xvalidate}.
+\thai{How to explain this table? Maybe with some kind of confidence interval? How to calculate it? (I tried the Confidence Interval calculator and the result is plain wrong.) Wow.}
+
+\newcommand{\SampleMean}{$\bar{x}$}
+\newcommand{\SampleSD}{$s$}
+
+\begin{table*}[!t]
+\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{ccccccc}
+\hline
+Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
+$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
+$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
+\end{tabular}
+\label{tb:thresholds}
+\end{table*}
+
+\begin{table*}[!t]
+\caption{Bootstrapping cross validation result of our model. For each metric, we included the average and standard deviation.}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{ccccccc}
+\hline
+\multirow{2}{*}{Prediction Models} & \multicolumn{2}{c}{F-measure} & \multicolumn{2}{c}{Precision} & \multicolumn{2}{c}{Recall} \\
+& \SampleMean & \SampleSD & \SampleMean & \SampleSD & \SampleMean & \SampleSD \\ \hline \hline
+$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.693 & 0.089 &  0.654 & 0.116 &  0.759 & 0.123 \\
+$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 0.681 & 0.118 &  0.636 & 0.144 &  0.755 & 0.148 \\
+\hline
+\end{tabular}
+\label{tb:xvalidate}
+\end{table*}
 

### 2014-07-28 sections/discussion.tex
working on discussion

--- 2014-07-28 sections/discussion.tex
@@
 \end{figure}
+\subsection*{Can other text mining techniques be used to classify discussions?}
+To find relevance between comments and the corresponding commit message, topic modeling technique can be used as the study of \cite{Barua2012a}.
+This technique discovers topics for a given collection of documents.
+However, in MCR context, the documents generally is short descriptions and short discussions.
+The topic modeling technique would generate topics that include diverse actual topics of documents since the content of documents is insufficient to determine.
+We have applied Latent Dirichlet allocation (LDA), which is a well-known model of topic modeling techniques, on our data set.
+We found that the generated topics were diverse and some of them cannot did not have a relation between documents and their topics.
+Therefore, the topic modeling cannot be used to classify discussions.
+Others techniques will be investigated in our future work to improve our approach.
+
+\subsection{Threat to Validity}

### 2014-07-28 sections/results.tex
working on discussion

--- 2014-07-28 sections/results.tex
@@
 It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
-Due to subjective and error-prone manual classification, these comments were not received three voting scores.
-This suggests us to re-examine the comments again.
-\pick{I'm not sure if comments with vote 2 are highly classified as useful and comments with vote 1 are highly classified as useless, what will we do.}
+Since the manual classification can be, these comments were not received three voting scores.
 

### 2014-07-28 sections/results.tex
Fix conflig

@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
+\caption{The similarity and distance plot of the training data.
+The symbol represents the score, which ranges from 0 to 3.}
+\label{fig:scatter}
+\end{figure}
+
 \textbf{Methodology.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
@@
 
+\begin{table}[!t]
+\centering
+\small
+\caption{Number of comments classified by our approach against ground truth data}
+\begin{tabular}{ccccc}
+\hline
+& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
+Our&  Useless  & Unclear  & Unclear & Useful \\
+Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
+\hline \hline
+Useful & 3 & 12 & 24 & 94 \\
+Useless & 69 & 23 & 7 & 6 \\
+Overlap & 1 & 1 & 0 & 1 \\
+Undetermined & 12 & 24 & 20 & 21 \\
+\hline
+\end{tabular}
+\label{tb:classify_number}
+\end{table}
+
 %%Interpret: comments & similarity values%%%%
@@
 This led us to investigate insight into these comments to find other properties in our future work.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[scale=0.45, trim=0 0 30 50, clip=true]{scatter_log}
-\caption{The similarity and distance plot of the training data.
-The symbol represents the score, which ranges from 0 to 3.}
-\label{fig:scatter}
-\end{figure}
 
@@
 
-\begin{table}[h]
+\textbf{Validation.} After validating our approach using bootstrapping cross validation with 300 iterations, for the random select test datasets, we obtained the results described in Table \ref{tb:xvalidate}.
+
+%\begin{table*}[!t]
+%\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
+%\small
+%\centering
+%\def\arraystretch{1.2}
+%\begin{tabular}{ccccccc}
+%\hline
+%Prediction Models & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
+%$\Theta(c,S_T=s_t,D_T=d_t)$   & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \hline
+%$\Omega(c,S'_T=s_t,D'_T=d_t)$ & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \hline
+%\end{tabular}
+%\label{tb:thresholds}
+%\end{table*}
+
+\begin{table}[!t]
+\caption{Bootstrapping cross validation result of our models}
+\small
 \centering
-\small
-\caption{Number of comments classified by our approach against ground truth data}
-\begin{tabular}{ccccc}
+\def\arraystretch{1.2}
+\begin{tabular}{ccc|cc|cc}
 \hline
-& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
-Our&  Useless  & Unclear  & Unclear & Useful \\
-Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
-\hline \hline
-Useful & 3 & 12 & 24 & 94 \\
-Useless & 69 & 23 & 7 & 6 \\
-Overlap & 1 & 1 & 0 & 1 \\
-Undetermined & 12 & 24 & 20 & 21 \\
+Classifcation & \multicolumn{2}{c|}{F-measure} & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c}{Recall} \\ \cline{2-7}
+Models & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
+$\Theta(c,S_T,D_T)$   & 0.693 & 0.089 &  0.654 & 0.116 &  0.759 & 0.123 \\
+$\Omega(c,S'_T,D'_T)$ & 0.681 & 0.118 &  0.636 & 0.144 &  0.755 & 0.148 \\
 \hline
 \end{tabular}
-\label{tb:classify_number}
+\label{tb:xvalidate}
 \end{table}
-
-\textbf{Validation.} After validating our approach using bootstrapping cross validation with 300 iterations, for the random select test datasets, we obtained the results described in Table \ref{}.
-
-%the average of F-measure score are 0.6
-%
-%After we performed cross validation, we obtained the following result:
-%for useful and useless classifications,
-%we obtained an average F$_1$ score of 0.693 and 0.681,
-%with standard deviation of 0.090 and 0.118, respectively.
-%This indicates that we can use our approach to classify with confident of 69.8\%.
-%\pick{Precision? Recall?} \thai{This is some confidence interval...}
 

### 2014-07-28 sections/results.tex
Done result for RQ1

@@
 \subsection{Research Questions}
-To validate our approach, we addressed two research questions: \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?
+We addressed two research questions: \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?
 and \textbf{RQ2:} Is semantic similarity classification cost-efficient, assurable, and scalable?.
@@
 
-\textbf{Methodology.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
+To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
 Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
 We also determined the effectiveness of our approach using bootstrapping cross validation.
-We randomly selected 90\% of 318 comments for training set and used the remaining 10\% for the validation set.
-The performance on the 10\% was measured using precision, recall and F-measure.
-This validation was repeated for 300 times to estimate the mean and variance of the performance.
 
@@
 To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
-Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the first rank of thresholds and applied models, i.e.
+%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
+We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e.
 useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
 
-\textbf{Classification Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
+\textbf{Model Effectiveness Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
 The precision and Recall of the models are 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
@@
 having high number of comment with \texttt{YES} = 0 and 1 voting scores.
+As the manual classification can be subjective, these comments were not received three voting scores.
 It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
-Since the manual classification can be, these comments were not received three voting scores.
 
@@
 
-\textbf{Validation.} After validating our approach using bootstrapping cross validation with 300 iterations, for the random select test datasets, we obtained the results described in Table \ref{tb:xvalidate}.
+\textbf{Validation:} We validated our approach using bootstrapping cross validation.
+We randomly selected 90\% of 318 comments for training set and determine thresholds.
+We then applied the constructed model on the remaining 10\% comments as the validation set.
+The performance on the validation sets was measured using precision, recall and F-measure.
+This validation was repeated for 300 times to estimate the performance of our models.
+
+Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
+The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately.
+This is better results than random model which achieved only XX\% of precision and YY\% of recall.
+\pick{Giving a random model as a base line would be easily to determine the performance of our models.}
 
@@
 \begin{table}[!t]
-\caption{Bootstrapping cross validation result of our models}
+\caption{Results from bootstrapping cross validation of our classification models}
 \small
@@
 \hline
-Classifcation & \multicolumn{2}{c|}{F-measure} & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c}{Recall} \\ \cline{2-7}
+Classifcation & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{2-7}
 Models & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
-$\Theta(c,S_T,D_T)$   & 0.693 & 0.089 &  0.654 & 0.116 &  0.759 & 0.123 \\
-$\Omega(c,S'_T,D'_T)$ & 0.681 & 0.118 &  0.636 & 0.144 &  0.755 & 0.148 \\
+$\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\
+$\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\
 \hline
@@
 
-According to the results, we can answer RQ1 that \emph{we can automatically classify usefulness of comments from similarity and dissimilarity using our approach.}
+According to the results, we can answer RQ1 that \emph{there is a relation between semantic similarity usefulness of comments.
+Based on our approach, the semantic similarity can be used as an indicator to classify usefulness of comments.
+}
 

### 2014-07-28 sections/results.tex
Note from Dan sensei, for RQ2

@@
 That means that about 77\% of the effort is saved.
+
+\pick{Note from Dan sensei,}
+
+For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
+
+ Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
+
+You cannot, but some estimates are possble
+
+first, human beings have a fairly well known rate of making errors in classification
+
+second, look at the comments in the training set that the method classified differently, especially the unclear.
+
+Review these to see if the method suggested a better classification than was originally made by the assessors
+
+You can consider these errors. Now look at what wans the percent of errors in the training set
+
+This is also an estimate of the human error rate

### 2014-07-28 sections/introduction.tex
Minor edits for Introduction

@@
 Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
-Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industrial and OSS projects.
+Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
 One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
-Reviewers can find defects in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
-Developers then improve the changes in response to these comments which in turn are reviewed for approval.  
+Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
+Developers then improve the changes in response to these comments and re-submit for review until the changes are approved.  
 %Fig. \ref{fig:process} illustrates a typical MCR process.
 
-Because performance of code review has a clear relationship to the quality of software project, many studies have investigated the influencing factors in MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
-However, little research exists investigating how the discussion for a proposed change impacts software quality.
+Because performance of code review has a clear relationship to the quality of the software, many studies have investigated factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
+However, little research exists investigating how review discussion for a proposed change impacts software quality.
 Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
-it is possible that reviewers comments can either positively contribute to the proposed changes (i.e.
-``\emph{useful}''), or be a discussion which is out of scope (i.e.
-relatively  ``\emph{useless}''  to the proposed changes).
+it is possible that they can either positively contribute to the proposed changes (i.e.
+are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e.
+relatively ``\emph{useless}'' ).
 Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g.
@@
 To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
-One reason for this may be that to assess the impact of discussion in MCR, a manual classification is required as in the study of Beller et. al. \cite{Beller}.
-MCR can produce a massive amount of changes and comments\cite{Balachandran2013,Thongtanunam2014}, and it is painstaking and time consuming to classify the comments in order to perform appropriate quantitative analysis.
+One reason for this may be that to assess the impact of discussion in MCR, effort intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
+MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify comments usefulness.
 Moreover, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
@@
 
-In this paper, we present a text mining approach to assist in classifying the usefulness of comments.
-The proposed approach is meant to enable classifying the large amounts of MRC comments, in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
-By introducing some automation support based on objective empirical criteria,
+In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
+The proposed approach is meant to better enable classifying large amounts of MRC comments in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
+By introducing automation support based on objective empirical criteria,
 our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
@@
 %%%%%%%%% TEMP %%%%%%%%%
+%\dan{Much of the following material should be placed in a separate Motivation section}
+
 %We define a \emph{useful} comment as one that \emph{contributes to improving the proposed changes} and a \emph{useless}\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.} comment as one that does not.
 %Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
-%\dan{Much of the following material should be placed in a separate Motivation section} 
+
 %In our approach, we analyze the similarity between a commit message of the proposed changes and the respective comments that follow.
+
 %Our key idea is that useful comments are likely to have a strong semantic similarity to the proposed changes, while useless comments are more likely strongly dissimilar.
 %To determine these semantic relationships, we use the Vector Space Model (VSM) and calculate similarity (using cosine similarity) and dissimilarity (using euclidean distance) between the comment and commit message vectors.
+
 %We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.

### 2014-07-28 sections/results.tex
add random
finalize result of validation in RQ1

@@
 We selected the most active subproject, which is called \texttt{qtbase}.
-From this subproject, we used the review history from May 25, 2011 to June 13, 2012, which contains 6,605 changes and 72,484 comments.
+From this subproject, we used the review history from May 2011 to June 2012, which contains 6,605 changes and 72,484 comments.
 
@@
 
+\begin{table*}[!t]
+\caption{Results from bootstrapping cross validation of our classification models against random models}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{cccc|cc|cc}
+\hline
+\multicolumn{2}{c}{Classifcation}   & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{3-8}
+\multicolumn{2}{c}{Models} & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
+\multirow{2}{*}{Useful} & $\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\ \cline{2-8}
+& Random     &  0.421 & 0.114 &  0.376 & 0.116 & 0.496 & 0.144\\ \hline
+\multirow{2}{*}{Useless}  & $\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\ \cline{2-8}
+& Random    &  0.336 & 0.131 &  0.269 & 0.115 & 0.478 & 0.182\\
+\hline
+\end{tabular}
+\label{tb:xvalidate}
+\end{table*}
+
 \textbf{Validation:} We validated our approach using bootstrapping cross validation.
@@
 This validation was repeated for 300 times to estimate the performance of our models.
+For a baseline of our models, we determined the performance of the random models using same methods.
 
@@
 The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately.
-This is better results than random model which achieved only XX\% of precision and YY\% of recall.
-\pick{Giving a random model as a base line would be easily to determine the performance of our models.}
+Moreover, our models also achieved higher results than the random models twice for both precision and recall.
 
@@
 %\end{table*}
-
-\begin{table}[!t]
-\caption{Results from bootstrapping cross validation of our classification models}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccc|cc|cc}
-\hline
-Classifcation & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{2-7}
-Models & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
-$\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\
-$\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\
-\hline
-\end{tabular}
-\label{tb:xvalidate}
-\end{table}
 

### 2014-07-28 sections/discussion.tex
working on discussion

@@
 \section{Discussion}
-
-% noisy data, and binary classification
-Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
-This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
+Our results have shown that using semantic similarity can classify usefulness of comments and our approach also can reduce human effort ant error prone of manual classification.
+Besides the results, we also found interesting findings in our case study.
+We discuss these findings as follows:
 
 % tuning the F score for precision and recall
-Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
-For instance, if we wanted to measure the amount of useful comments within a large dataset, more weight can be given to precision, sacrificing some useful comments.
-If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.
+%Depending on the use case, we can fine-tune the F-score to give more weight to recall or precision.
+%For instance, if we wanted to measure the amount of useful comments within a large dataset, more weight can be given to precision, sacrificing some useful comments.
+%If we wanted to modify a code review software such that it displays useful comments more prominently, more weight can be given to recall.
 
 % examples.
-In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
-due to the same word being used in a different context.
-For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
-better code generation with GCC at least.''}
-This comment, \emph{``I'll study the generated code a bit more,''} is just an author's response, and thus is not technically contributing.
+\subsection{What kind of comments cannot be classified using semantic similarity?}
+From the results of RQ1, we found that some comments were not determined by our models.
+Specifically, we were interested in comments with useful class (\texttt{YES} = 3) and useless class (\texttt{YES} = 0).
+To investigate the reason behind this, we examined these comments.
+We found that .....
+
+%In some cases, similarity and dissimilarity failed to measure the usefulness of the comment,
+%due to the same word being used in a different context.
+%For example, consider this excerpt from the commit message: \emph{``In the no-assert case, make Q\_ASSERT decay to Q\_ASSUME. I can confirm
+%better code generation with GCC at least.''}
+%This comment, \emph{``I'll study the generated code a bit more,''} is just an author's response, and thus is not technically contributing.
 However, it is classified as a useful comment.
@@
 
-%\subsection{Reasons of Classification}
-% reasons for classification as useful or not useful
-During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
-
-\begin{itemize}
-	\item they contain new information;
-	\item they contain constructive suggestions;
-	\item they discuss directly about the change; and
-	\item they discuss technical matters.
-\end{itemize}
-
-Examples of reasons for negative comments include:
-
-\begin{itemize}
-	\item chatting (i.e. no new information, just communication);
-	\item not discussing directly about the change;
-	\item discussing about the process workflow; and
-	\item discussing about Git or Gerrit itself.
-\end{itemize}
-
 %\subsection{Binary Classification}
-
+\subsection{How much impact of unclear class on model construction?}
 Another approach we tried is to perform a \emph{binary classification}.
@@
 
-\subsection{Threat to Validity}
+%\subsection{Reasons of Classification}
+% reasons for classification as useful or not useful
+\subsection*{What decisions are made during the manual classification?}
+During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
+
+\begin{itemize}
+	\item they contain new information;
+	\item they contain constructive suggestions;
+	\item they discuss directly about the change; and
+	\item they discuss technical matters.
+\end{itemize}
+
+Examples of reasons for negative comments include:
+
+\begin{itemize}
+	\item chatting (i.e. no new information, just communication);
+	\item not discussing directly about the change;
+	\item discussing about the process workflow; and
+	\item discussing about Git or Gerrit itself.
+\end{itemize}
+
+\subsection*{Threat to Validity}
+\indent \textbf{Internal Valdity:} % noisy data, and binary classification
+Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
+This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score. \\
+\indent \textbf{External Validity:} \\

### 2014-07-29 sections/results.tex
formatting

@@
 \end{table}
+
 \subsection{Manual Comment Usefulness Assessment}
-In this case study, three participants (the first two authors and one student) independently classify comments by giving a question that “Does this comment technically contribute to its change or not?”.
-Then, the participants gave a vote for \texttt{YES} if the comment is likely to useful and  \texttt{NO}  if the comment is likely to useless.
+In this case study, three participants (the first two authors and one student) independently classify comments by giving a question, ``does this comment technically contribute to its change or not?''
+Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
 From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e.
 three \texttt{NO} votes) are \emph{useless} comments.
-For the comments with one and two YES’ votes, we defined them as unclear comments.
+For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.
 
@@
 While, the comments drawn in the white area are those not satisfied any condition (i.e.
-undetermined).
+\emph{undetermined}).
 %This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

### 2014-07-29 sections/discussion.tex
updated graph to include legend

@@
 This means we assume that there are no unclear or undetermined comments; only useful and useless.
-For this, we removed the samples with 1 and 2 \texttt{YES} votes from our data set. 209 samples without disagreements are left.
-By performing cross-validation using only samples with 0 and 3 \texttt{YES} votes, we obtained a much better F$_1$ score of 0.896.
+For this, we removed the samples with 1 and 2 \texttt{YES} votes from our training set.
+This leaves us with 209 remaining samples, all without a disagreement.
+By performing cross-validation using these samples, we obtained a much better F$_1$ score of 0.896.
 
-We could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
-However, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.
+However, we could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
+But interestingly, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.
 

### 2014-07-29 sections/approach.tex
Don't think we should mention about cost-effectiveness here.
Just the practicality limit should be enough....

@@
 Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.  
 % empirically driven and automatically adapts to the quality the data

### 2014-07-29 sections/discussion.tex
working on discussion

--- 2014-07-28 sections/discussion.tex
@@
 Specifically, we were interested in comments with useful class (\texttt{YES} = 3) and useless class (\texttt{YES} = 0).
-To investigate the reason behind this, we examined these comments.
-We found that .....
+To investigate the reason behind this, we observed these comments and the corresponding commit messages.
+We found that there were few common keywords between comments and commit messages and their length are relatively unequal.
+This makes low similarity values and low dissimilarity values as they shown in  bottom left white area in Fig.
+\ref{fig:scatter} which our models cannot determine.
 
@@
 \subsection{How much impact of unclear class on model construction?}
+ % noisy data, and binary classification
+Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
+This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
+
 Another approach we tried is to perform a \emph{binary classification}.
@@
 \subsection*{What decisions are made during the manual classification?}
-During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
+During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes.
+We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters.
+For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) little direct to the proposed changes, 3) discuss about process workflow and supporting system i.e.
+Git and Gerrit.
+%During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
+%
+%\begin{itemize}
+%	\item they contain new information;
+%	\item they contain constructive suggestions;
+%	\item they discuss directly about the change; and
+%	\item they discuss technical matters.
+%\end{itemize}
+%
+%Examples of reasons for negative comments include:
+%
+%\begin{itemize}
+%	\item chatting (i.e. no new information, just communication);
+%	\item not discussing directly about the change;
+%	\item discussing about the process workflow; and
+%	\item discussing about Git or Gerrit itself.
+%\end{itemize}
 
-\begin{itemize}
-	\item they contain new information;
-	\item they contain constructive suggestions;
-	\item they discuss directly about the change; and
-	\item they discuss technical matters.
-\end{itemize}
-
-Examples of reasons for negative comments include:
-
-\begin{itemize}
-	\item chatting (i.e. no new information, just communication);
-	\item not discussing directly about the change;
-	\item discussing about the process workflow; and
-	\item discussing about Git or Gerrit itself.
-\end{itemize}
-
-\subsection*{Threat to Validity}
-\indent \textbf{Internal Valdity:} % noisy data, and binary classification
-Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
-This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score. \\
-\indent \textbf{External Validity:} \\
+\subsection{Can the determined thresholds in this study be used to other projects?} 
+In this study, we determined the similarity conditions using training set in Qt project and the results show that the conditions can classify usefulness of comments.
+However, to apply our approach on other projects, preparing training set is still required and it cost human effort.
+To fully automate this approach, we will investigate the use of similarity conditions for cross projects.
+Thus, additional studies are needed to improve our approach.

### 2014-07-29 sections/discussion.tex
minor change for format

@@
 \subsection{How much impact of unclear class on model construction?}
+\pick{This topic of discuss should be changed....}
  % noisy data, and binary classification
@@
 \end{figure}
-\subsection*{Can other text mining techniques be used to classify discussions?}
+
+\subsection{Can other text mining techniques be used to classify discussions?}
 To find relevance between comments and the corresponding commit message, topic modeling technique can be used as the study of \cite{Barua2012a}.
@@
 % reasons for classification as useful or not useful
-\subsection*{What decisions are made during the manual classification?}
+\subsection{What decisions are made during the manual classification?}
 During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes.

### 2014-07-29 sections/results.tex
updated graph to include legend
minor change for format

@@
 
-To manually assess all 10,583 comments---even with only one person working at 10 comments per minute---this would take 17.6 person hours.
+However, to manually assess all 10,583 comments---even with only one person working at 10 comments per minute---this would take 17.6 person hours.
 By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
 That means that about 77\% of the effort is saved.
-
-\pick{Note from Dan sensei,}
-
-For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
-
- Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
-
-You cannot, but some estimates are possble
-
-first, human beings have a fairly well known rate of making errors in classification
-
-second, look at the comments in the training set that the method classified differently, especially the unclear.
-
-Review these to see if the method suggested a better classification than was originally made by the assessors
-
-You can consider these errors. Now look at what wans the percent of errors in the training set
-
-This is also an estimate of the human error rate

### 2014-07-29 sections/conclusion.tex
add conclusion

% !TEX root = ../paper.tex

\section{Conclusion and Future Work}
In this paper, we propose a practical approach to classify usefulness discussion in MCR based on VSM similarity.
The results from our case study show that our approach can classify comments achieved better results than random model twice for both precision and recall.
Moreover, we found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.

For our future work,.....

### 2014-07-30 sections/conclusion.tex
forgot to commit

@@
 
-\section{Conclusion and Future Work}
-In this paper, we propose a practical approach to classify usefulness discussion in MCR based on VSM similarity.
-The results from our case study show that our approach can classify comments achieved better results than random model twice for both precision and recall.
-Moreover, we found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
-For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful.
-The remaining 23\% are undetermined and require manual classification.
-Thus the classification effort is reduced by about 77\%.
-
-For our future work,.....
+\section{Conclusions}

### 2014-07-30 sections/approach.tex
forgot to commit
Minor change in Approach section

--- 2014-07-28 sections/approach.tex
@@
 
+\subsection{Approach}
 Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
@@
 The key is determining these degrees in a practical and effective manner.
+%\textbf{Approach Overview.} 
+Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
+Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
+The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
 
@@
 
-%\textbf{Approach Overview.} 
-Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
-Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
-The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
-In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.
-
 % again, I can't see Fig. \ref{fig:overview}(a)
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
+We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
 %For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
@@
 The similarity and dissimilarity metrics are then computed for the data set.
-These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
+These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
+%Other likelihood functions could be used depending on precision, recall, or risk goals.
+We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
+which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
+In this study, we used the F$_1$-measure, which equally prioritize precision and recall.
+Different weighting can be used by different F$_\beta$ measures depending on an application.
 
-%\textbf{Usefulness Classification Conditions.} 
+\subsection{Usefulness Classification Conditions} 
 Using those thresholds, we can classify the usefulness of comments for the rest of comments (as test data) in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
@@
 
-We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
-which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
-In this paper, we used the F$_1$ measure, which gives equal weight to both precision and recall.
-Depending on application, different weights can be given by choosing a different F$_\beta$ measure.
-
 % Our proposed approach is empirically driven and automatically adjusts to the quality the data.

### 2014-07-30 sections/approach.tex

@@
 Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+
 % empirically driven and automatically adapts to the quality the data

### 2014-07-30 sections/results.tex

@@
 \def\arraystretch{1.2}
-\begin{tabular}{cccc|cc|cc}
+\begin{tabular}{cccc|cc|cc|cc}
 \hline
-\multicolumn{2}{c}{Classifcation}   & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c}{F-measure} \\ \cline{3-8}
-\multicolumn{2}{c}{Models} & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
-\multirow{2}{*}{Useful} & $\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089\\ \cline{2-8}
-& Random     &  0.421 & 0.114 &  0.376 & 0.116 & 0.496 & 0.144\\ \hline
-\multirow{2}{*}{Useless}  & $\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118\\ \cline{2-8}
-& Random    &  0.336 & 0.131 &  0.269 & 0.115 & 0.478 & 0.182\\
+\multicolumn{2}{c}{Classifcation}   & \multicolumn{2}{c|}{Precision} & \multicolumn{2}{c|}{Recall} & \multicolumn{2}{c|}{F-measure} & \multicolumn{2}{c}{Accuracy} \\ \cline{3-10}
+\multicolumn{2}{c}{Models} & Avg. & STD. & Avg. & STD. & Avg. & STD. & Avg. & STD. \\ \hline \hline
+\multirow{2}{*}{Useful} & $\Theta(c,S_T,D_T)$    &  0.654 & 0.116 &  0.759 & 0.123 & 0.693 & 0.089 & 0.752 & 0.067 \\ \cline{2-10}
+& Random     &  0.421 & 0.114 &  0.376 & 0.116 & 0.496 & 0.144 & 0.496 & 0.089 \\ \hline
+\multirow{2}{*}{Useless}  & $\Omega(c,S'_T,D'_T)$  &  0.636 & 0.144 &  0.755 & 0.148 & 0.681 & 0.118 & 0.815 & 0.064 \\ \cline{2-10}
+& Random    &  0.336 & 0.131 &  0.269 & 0.115 & 0.478 & 0.182 & 0.500 & 0.089 \\
 \hline
@@
 On average, it takes 28 seconds to assess each comment.
-However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess; only few comments take long time.
+However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
 This also suggests that the time to assess each comment is not normally distributed.
@@
 
-However, to manually assess all 10,583 comments---even with only one person working at 10 comments per minute---this would take 17.6 person hours.
+However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
 By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
 That means that about 77\% of the effort is saved.
+
+Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
+As the figure shows, the proportion is similar to the result of .
+
+\begin{table}[!t]
+\caption{Proportion of classifications when applied to the whole data set.}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{ccccccc}
+\hline
+Class &        over all samples & only training data  \\ \hline
+useful &            42.8\%      &      41.8\%         \\
+useless &           33.7\%      &      33.1\%         \\
+undetermined &      23.5\%      &      25.1\%         \\ \hline
+\end{tabular}
+\label{tb:percent}
+\end{table}
+
+%\pick{Note from Dan sensei,}
+%For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
+% Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
+%You cannot, but some estimates are possble
+%first, human beings have a fairly well known rate of making errors in classification
+%second, look at the comments in the training set that the method classified differently, especially the unclear.
+%Review these to see if the method suggested a better classification than was originally made by the assessors
+%You can consider these errors. Now look at what wans the percent of errors in the training set
+%This is also an estimate of the human error rate

### 2014-07-30 sections/approach.tex
Move limitation described in approach section to discussion

@@
 While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
-First, we have to accept that some comments cannot be reliably or confidently classified.
+We have to accept that some comments cannot be reliably or confidently classified.
 We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
 Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
 

### 2014-07-30 sections/approach.tex
edit text

--- 2014-07-30 sections/approach.tex
@@
 
+\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless}\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.} comment as one that does not.
+
 Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
-We define a \emph{useful} comment as one that contributes to improving the proposed changes and a \emph{useless}\footnote{Although we call these comments \emph{useless}, it might be useful---or sometimes even required---in some other context, such as to facilitate communication.} comment as one that does not.
 Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
@@
 
-\subsection{Approach}
 Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
-That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
-The key is determining these degrees in a practical and effective manner.
-%\textbf{Approach Overview.} 
-Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
-Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
-The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
+That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely useless.
+The key is to determine these degrees in a practical and effective manner.
 
@@
 
+%\textbf{Approach Overview.} 
+Fig. \ref{fig:overview} shows an overview of our proposed classification approach.
+Usefulness of a comment is determined by computing its semantic similarity with the commit message of its proposed change and observing if it satisfies \emph{usefulness classification likelihood conditions}.
+The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
+In our case example we chose to maximize the F-measure, but other likelihood functions could be used depending on precision, recall, or risk goals.
+
 % again, I can't see Fig. \ref{fig:overview}(a)
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
+To calculate semantic similarity, we used the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
 %For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
@@
 The similarity and dissimilarity metrics are then computed for the data set.
-These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
-%Other likelihood functions could be used depending on precision, recall, or risk goals.
-We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
-which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
-In this study, we used the F$_1$-measure, which equally prioritize precision and recall.
-Different weighting can be used by different F$_\beta$ measures depending on an application.
+These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that can best (relative to some likelihood function such as F-measure) discriminate useful comments and $S'_T$ and $D'_T$ for useless comments.
 
-\subsection{Usefulness Classification Conditions} 
+%\textbf{Usefulness Classification Conditions.} 
 Using those thresholds, we can classify the usefulness of comments for the rest of comments (as test data) in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
@@
 
-The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance respectively.
+The functions $\Sim(m,c)$ and $\Dist(m,c)$ are the similarity and dissimilarity measures relative to the proposed change commit message $m$ for the text of comment $c$ using cosine similarity and euclidian distance, respectively.
 Two metrics are used because they are independently generated and thus provides better discrimination for classification.
@@
 
+We find similarity and dissimilarity thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
+which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
+In this paper, we used the F$_1$ measure, which gives equal weight to both precision and recall.
+Depending on application, different weights can be given by choosing a different F$_\beta$ measure.
+
 % Our proposed approach is empirically driven and automatically adjusts to the quality the data.

### 2014-07-30 sections/results.tex
edit text

@@
 These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
-For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}.
+\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples.
 In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
 
-To do so, we first ignore all comments written by bots i.e.
-\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
+To do so, we first ignore all comments written by bots (i.e.
+\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}).
 Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression.
@@
 \subsection{Manual Comment Usefulness Assessment}
-In this case study, three participants (the first two authors and one student) independently classify comments by giving a question, ``does this comment technically contribute to its change or not?''
+In this case study, three participants (the first two authors and one student) independently classified comments by giving a question, ``does this comment technically contribute to its change or not?''
 Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
@@
 \caption{The similarity and distance plot of the training data.
-The symbol represents the score, which ranges from 0 to 3.}
+The symbol represents the score, which ranges from 0 to 3.
+The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.}
 \label{fig:scatter}
@@
 %Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e.
-useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
+We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
+The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.
 
 \textbf{Model Effectiveness Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-The precision and Recall of the models are 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
-We summarizes the number of classification from result described in Table \ref{tb:classify_number}.
-We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}.
-The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.
-Thus, the comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless.
-While, the comments drawn in the white area are those not satisfied any condition (i.e.
-\emph{undetermined}).
+The precision and recall of the models are 0.701 and 0.787 for useful model, and 0.648 and 0.824 for useless model.
+We summarized the number of comments by manually-classified score and our classification result in Table \ref{tb:classify_number}.
+The results and relationship between manual classification and our model based on similarity thresholds are shown in Fig  \ref{fig:scatter}.
+Comments in the green area are those that satisfied the conditions of the useful model.
+Comments in the red area are those that satisfied condition of the useless model.
+Finally, comments in the white area are those that did not satisfy any condition (i.e. \emph{undetermined}). 
 %This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
@@
 %%Interpret: comments & model%%%%
-As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area.
-Similarly, most comments in the red area are useless.
+As shown in the figure, most useful comments went into the green area; only few useful comments ended up in the red area.
+Similarly, most useless comments went into the red area.
 The unclear comments are drawn in both area.
@@
 This is because the similarity and dissimilarity values between useful and useless are vague.
-Both models tend to maximize coverage of classification.
-Thus, it is possible that there is overlap between these two models.
-However, from the results in Table \ref{tb:classify_number}, only three comments were classified overlap section.
-This shows that error of our models is low.
+Both models tried to maximize the coverage (and the precision) of classification, which makes it possible that there is some overlapping between these two models.
+Fortunately, this overlapping area is small.
+
+% These should go into the discussion.
+%However, from the results in Table \ref{tb:classify_number}, only three comments were classified in the overlapping section.
+%This shows that error of our models is low.
 Furthermore, there are 12 useless comments  (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area).
@@
 %%Interpret: comments & similarity values%%%%
-The graph also shows that the useful comments have less distance (not higher than 3 approximately) while most of useless comments have zero similarity.
-However, the unclear comments are still spread out over the graph which we cannot determine relationship between their similarity.
-Furthermore, it is interesting that comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity.
+The graph also shows that the useful comments have low dissimilarity value (less than 3, approximately),
+while most useless comments have zero similarity.
+However, the unclear comments are spread out over the graph in a way which we cannot classify using our model.
+This suggests that other factors may come into play.
+
+%Interestingly, comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity.
 This indicates that the comments  in each group have relationship other than similarity.
@@
 
-Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores.
-The classification of useless comments also have similar proportion i.e.
-having high number of comment with \texttt{YES} = 0 and 1 voting scores.
-As the manual classification can be subjective, these comments were not received three voting scores.
-It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
+Interestingly, in Table \ref{tb:classify_number},
+89\% of useful-class comments received 2 or 3 \texttt{YES} votes,
+and 88\% of useless-class comments received 0 or 1 \texttt{YES} votes.
+
+%Probably should be in the discussion?
+% As manual classification can be subjective, these comments were not received three voting scores.
+% It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
 
@@
 
-\textbf{Validation:} We validated our approach using bootstrapping cross validation.
+\textbf{Validation:}
+We validated our approach using bootstrapping cross validation.
 We randomly selected 90\% of 318 comments for training set and determine thresholds.
-We then applied the constructed model on the remaining 10\% comments as the validation set.
-The performance on the validation sets was measured using precision, recall and F-measure.
-This validation was repeated for 300 times to estimate the performance of our models.
-For a baseline of our models, we determined the performance of the random models using same methods.
+The constructed model is then applied on the remaining 10\% comments as the validation set.
+The precision, recall and F-measure scores are measured and recorded.
+This validation was repeated 300 times to give an average performance of our models.
+For a baseline, we also determined the performance of the random classifier using the same methods.
 
 Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
-The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately.
-Moreover, our models also achieved higher results than the random models twice for both precision and recall.
+The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
+In addition, our models also achieved higher results than the random models twice for both precision and recall.
 

### 2014-07-30 sections/approach.tex

--- 2014-07-30 sections/approach.tex
@@
 Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
-That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely not useful.
-The key is determining these degrees in a practical and effective manner.
-%\textbf{Approach Overview.} 
+That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely useless.
+The key is to determine these degrees in a practical and effective manner.
+
 Fig. \ref{fig:overview} shows an overview of our proposed classification approach.

### 2014-07-30 sections/discussion.tex

@@
 \subsection{Can the determined thresholds in this study be used to other projects?} 
+This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+
 In this study, we determined the similarity conditions using training set in Qt project and the results show that the conditions can classify usefulness of comments.

### 2014-07-30 sections/approach.tex
minor modification

--- 2014-07-30 sections/approach.tex
@@
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language\cite{did}; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously\cite{dfdf}.
+We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously.
 %For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.

### 2014-07-30 sections/discussion.tex
minor modification

@@
  % noisy data, and binary classification
+
+Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores.
+The classification of useless comments also have similar proportion i.e.
+having high number of comment with \texttt{YES} = 0 and 1 voting scores.
+As the manual classification can be subjective, these comments were not received three voting scores.
+It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
+
 Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.

### 2014-07-30 sections/results.tex
minor modification

--- 2014-07-30 sections/results.tex
@@
 %%Interpret: comments & model%%%%
-As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area.
-Similarly, most comments in the red area are useless.
+As shown in the figure, most comments drawn in green area are useful labels and very few useless labeled comments drawn in this area.
+Similarly, most comments in the red area are useless labels.
 The unclear comments are drawn in both area.
@@
 \hline
-& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
-Our&  Useless  & Unclear  & Unclear & Useful \\
-Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
+Result from & \multicolumn{4}{c}{Label set by manual assessment} \\ \cline{2-5}
+Classification &  Useless  & Unclear  & Unclear & Useful \\
+Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
 \hline \hline
@@
 This led us to investigate insight into these comments to find other properties in our future work.
-
-Interestingly, in Table \ref{tb:classify_number}, there are 88\% of useful comments classified by our model have \texttt{YES} = 2 and 3 voting scores.
-The classification of useless comments also have similar proportion i.e.
-having high number of comment with \texttt{YES} = 0 and 1 voting scores.
-As the manual classification can be subjective, these comments were not received three voting scores.
-It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
 

### 2014-07-30 sections/results.tex
update text about table iv

--- 2014-07-30 sections/results.tex
@@
 
-To answer this question, timestamps are recorded as three people assess each comment.
-Since three people work on their leisure time, there is much variability in the time between each vote.
+To answer this question, timestamps are recorded as three people voted on each comment.
+Since three people work in their leisure time, there is much variability in the time between each vote.
 Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
@@
 Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
-As the figure shows, the proportion is similar to the result of .
+As the table shows, the proportions are very similar in both the training dataset and all dataset,
+which may suggest that our model will have a similar performance in the real data.
 
@@
 \hline
-Class &        over all samples & only training data  \\ \hline
+Classification & over all samples & only training data  \\ \hline
 useful &            42.8\%      &      41.8\%         \\

### 2014-07-30 sections/results.tex
remove the paragraph that is moved to the discussion

@@
 
-Interestingly, in Table \ref{tb:classify_number},
-89\% of useful-class comments received 2 or 3 \texttt{YES} votes,
-and 88\% of useless-class comments received 0 or 1 \texttt{YES} votes.
+%Interestingly, in Table \ref{tb:classify_number},
+%89\% of useful-class comments received 2 or 3 \texttt{YES} votes,
+%and 88\% of useless-class comments received 0 or 1 \texttt{YES} votes.
 
@@
 %we obtained an average F$_1$ score of 0.693 and 0.681,
-%with standard deviation of 0.090 and 0.118, respectively.
-%This indicates that we can use our approach to classify with confident of 69.8\%.
-
-%After the similarity and distance metrics have been calculated,
-%these metrics appear to be able to separate the useful comments from the non-useful ones,
-%as can be seen in Fig.\ref{fig:scatter}.
-%Note that many comments have a cosine similarity metric of 0.
-%This is because the comment text and the corresponding commit message has no word in comment.
-
-\begin{ResearchQuestions}
-\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
-\end{ResearchQuestions}
-
-To answer this question, timestamps are recorded as three people voted on each comment.
-Since three people work in their leisure time, there is much variability in the time between each vote.
-Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
-
-On average, it takes 28 seconds to assess each comment.
-However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
-This also suggests that the time to assess each comment is not normally distributed.
-The standard deviation is 45 seconds.
-
-To estimate the total time for us to assess these 318 comments,
-we multiplied the average time by the number of comments and the number of people.
-This results in 7.42 person hours.
-
-However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
-By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
-That means that about 77\% of the effort is saved.
-
-Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
-As the table shows, the proportions are very similar in both the training dataset and all dataset,
-which may suggest that our model will have a similar performance in the real data.
-
-\begin{table}[!t]
-\caption{Proportion of classifications when applied to the whole data set.}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
-\hline
-Classification & over all samples & only training data  \\ \hline
-useful &            42.8\%      &      41.8\%         \\
-useless &           33.7\%      &      33.1\%         \\
-undetermined &      23.5\%      &      25.1\%         \\ \hline
-\end{tabular}
-\label{tb:percent}
-\end{table}
-
-%\pick{Note from Dan sensei,}
-%For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
-% Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
-%You cannot, but some estimates are possble
-%first, human beings have a fairly well known rate of making errors in classification
-%second, look at the comments in the training set that the method classified differently, especially the unclear.
-%Review these to see if the method suggested a better classification than was originally made by the assessors
-%You can consider these errors. Now look at what wans the percent of errors in the training set
-%This is also an estimate of the human error rate
+%wit

### 2014-07-30 sections/results.tex
fix numbers in table
revise RQ1 result

--- 2014-07-30 sections/results.tex
@@
 These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
-\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples.
+For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}.
 In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
 
-To do so, we first ignore all comments written by bots (i.e.
-\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}).
+To do so, we first ignore all comments written by bots i.e.
+\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.
 Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression.
@@
 \subsection{Manual Comment Usefulness Assessment}
-In this case study, three participants (the first two authors and one student) independently classified comments by giving a question, ``does this comment technically contribute to its change or not?''
+In this case study, three participants (the first two authors and one student) independently classify comments by giving a question, ``does this comment technically contribute to its change or not?''
 Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
@@
 \caption{The similarity and distance plot of the training data.
-The symbol represents the score, which ranges from 0 to 3.
-The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model.}
+The symbol represents the score, which ranges from 0 to 3.}
 \label{fig:scatter}
@@
 %Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
-The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.
+We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e.
+useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
 
-\textbf{Model Effectiveness Results:} From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
-The precision and recall of the models are 0.701 and 0.787 for useful model, and 0.648 and 0.824 for useless model.
-We summarized the number of comments by manually-classified score and our classification result in Table \ref{tb:classify_number}.
-The results and relationship between manual classification and our model based on similarity thresholds are shown in Fig  \ref{fig:scatter}.
-Comments in the green area are those that satisfied the conditions of the useful model.
-Comments in the red area are those that satisfied condition of the useless model.
-Finally, comments in the white area are those that did not satisfy any condition (i.e. \emph{undetermined}). 
-%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.
+\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 60, 51, and 122 for useless set (\texttt{YES} = 0), unclear set (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively.
+The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
+
+Figure \ref{fig:scatter} shows the relationship between usefulness class from our classification model and comment sets from manual assessment. 
+The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model.
+The comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless.
+While, the comments drawn in the white area are those not satisfied any condition (i.e.
+\emph{undetermined}).
+The total number of comments from this classification results is described in Table \ref{tb:classify_number}.
 
 %%Interpret: comments & model%%%%
-As shown in the figure, most useful comments went into the green area; only few useful comments ended up in the red area.
-Similarly, most useless comments went into the red area.
-The unclear comments are drawn in both area.
-Between these areas, there is an overlap section.
-This is because the similarity and dissimilarity values between useful and useless are vague.
-Both models tried to maximize the coverage (and the precision) of classification, which makes it possible that there is some overlapping between these two models.
-Fortunately, this overlapping area is small.
+Corresponding to the precision and recall values, the figure shows that most comments drawn in green area are comments of useful set and very few comments of useless set drawn in this area.
+Similarly, most comments in the red area are comments of useless set.
+It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
+Most of useful set (\texttt{YES} = 3) adhere in the top left of the graph while useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
+However, the unclear set still spread out over the graph which we cannot determine relationship between their similarity values.
 
-% These should go into the discussion.
-%However, from the results in Table \ref{tb:classify_number}, only three comments were classified in the overlapping section.
-%This shows that error of our models is low.
+There is an overlap section as shown in Fig. \ref{fig:scatter}. This is a conflict results between our two models where a comment received true outcome from both classification models.  
+This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
+However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
+This is very small error for our models.
+Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}.
 Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area).
-We investigate characteristics of these comments.
-The findings are described in our discussion section.
+These comments were not satisfied our models.
+This suggests us that other indicators are needed to satisfy condition and identify usefulness.
 %From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
@@
 \centering
-\small
+
 \caption{Number of comments classified by our approach against ground truth data}
-\begin{tabular}{ccccc}
+\begin{tabular}{cccccc}
 \hline
-& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
-Our&  Useless  & Unclear  & Unclear & Useful \\
-Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
+Result from & \multicolumn{4}{c}{Results from manual assessment}  & \multirow{3}{*}{Precision}\\ \cline{2-5}
+Classification &  Useless  & Unclear  & Unclear & Useful \\
+Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
 \hline \hline
-Useful & 3 & 12 & 24 & 94 \\
-Useless & 69 & 23 & 7 & 6 \\
-Overlap & 1 & 1 & 0 & 1 \\
-Undetermined & 12 & 24 & 20 & 21 \\
+Useful & 3 & 12 & 24 & 94 & 0.706\\
+Useless & 69 & 23 & 7 & 6 &  0.657\\
+Overlap & 1 & 1 & 0 & 1 & - \\
+Undetermined & 12 & 24 & 20 & 21 & - \\
 \hline
+Recall & 0.812 & - & - & 0.770\\ \hline 
 \end{tabular}
@@
 \end{table}
-
-%%Interpret: comments & similarity values%%%%
-The graph also shows that the useful comments have low dissimilarity value (less than 3, approximately),
-while most useless comments have zero similarity.
-However, the unclear comments are spread out over the graph in a way which we cannot classify using our model.
-This suggests that other factors may come into play.
-
-%Interestingly, comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity.
-This indicates that the comments  in each group have relationship other than similarity.
-This led us to investigate insight into these comments to find other properties in our future work.
-
-Interestingly, in Table \ref{tb:classify_number},
-89\% of useful-class comments received 2 or 3 \texttt{YES} votes,
-and 88\% of useless-class comments received 0 or 1 \texttt{YES} votes.
-
-%Probably should be in the discussion?
-% As manual classification can be subjective, these comments were not received three voting scores.
-% It is possible that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with can be useless comments.
 
@@
 
-\textbf{Validation:}
-We validated our approach using bootstrapping cross validation.
+\textbf{Validation:} We validated our approach using bootstrapping cross validation.
 We randomly selected 90\% of 318 comments for training set and determine thresholds.
-The constructed model is then applied on the remaining 10\% comments as the validation set.
-The precision, recall and F-measure scores are measured and recorded.
-This validation was repeated 300 times to give an average performance of our models.
-For a baseline, we also determined the performance of the random classifier using the same methods.
+We then applied the constructed model on the remaining 10\% comments as the validation set.
+The performance on the validation sets was measured using precision, recall and F-measure.
+This validation was repeated for 300 times to estimate the performance of our models.
+For a baseline of our models, we determined the performance of the random models using same methods.
 
 Table \ref{tb:xvalidate} describes the performance of useful and useless classification models including an average and standard deviation of precision, recall, and F-measure.
-The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
-In addition, our models also achieved higher results than the random models twice for both precision and recall.
+The results show that both of our models can achieve  60\% of precision and  75\% of recall approximately.
+Moreover, our models also achieved higher results than the random models twice for both precision and recall.
 
@@
 
-According to the results, we can answer RQ1 that \emph{there is a relation between semantic similarity usefulness of comments.
-Based on our approach, the semantic similarity can be used as an indicator to classify usefulness of comments.
-}
+According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random model as twice.}
 
@@
 
-To answer this question, timestamps are recorded as three people voted on each comment.
-Since three people work in their leisure time, there is much variability in the time between each vote.
+To answer this question, timestamps are recorded as three people assess each comment.
+Since three people work on their leisure time, there is much variability in the time between each vote.
 Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
@@
 Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
-As the table shows, the proportions are very similar in both the training dataset and all dataset,
-which may suggest that our model will have a similar performance in the real data.
+As the figure shows, the proportion is similar to the result of .
 
@@
 \hline
-Classification & over all samples & only training data  \\ \hline
+Class &        over all samples & only training data  \\ \hline
 useful &            42.8\%      &      41.8\%         \\

### 2014-07-30 sections/background.tex
working on section 3
more refactorings
working on result RQ1

@@
 Then, reviewers will examine the revised proposed change.
-If the revision is not approved, reviewers provide comments to fix and the process continues until (4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).
+If the revision is not approved, reviewers provide comments to fix and the process continues until
+(4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (rejected).
+
+According to this process, reviewers' comments are the most important factor in determining software quality.
+In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
+However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.
+% (e.g. coding styles, documentation, process workflow, etc.)
+For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
+Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
+Our observations of the Qt project also correspond to this finding.
+We found that some comments are superficial and unhelpful to the proposed changes.
+For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
+while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.
 
@@
 \end{figure}
-
-According to this process, reviewers' comments are the most important factor in determining software quality.
-In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
-However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.
-
-% (e.g. coding styles, documentation, process workflow, etc.)
-
-For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
-Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
-Our observations of the Qt project also correspond to this finding.
-We found some comments are superficial and unhelpful to the proposed changes.
-For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
-while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

### 2014-07-30 sections/introduction.tex
add conclusion

@@
 are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e.
-relatively ``\emph{useless}'' ).
+relatively ``\emph{useless}'').
 Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g.
@@
 To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
-One reason for this may be that to assess the impact of discussion in MCR, effort intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
-MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify comments usefulness.
-Moreover, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.
+One reason for this may be that to assess the impact of discussion in MCR, effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
+MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify their usefulness.
+Moreover, comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible misinterpretation.
 
@@
 In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
-The proposed approach is meant to better enable classifying large amounts of MRC comments in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
-By introducing automation support based on objective empirical criteria,
-our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
+The proposed approach is meant to ease classifying large amounts of MRC comments in order to conduct comment and code quality studies (such as those discussed earlier) as manual classification can quickly become an untenable task.
+By introducing automation support based on objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
 %Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
@@
 %\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
-%\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
-For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful.
-The remaining 23\% are undetermined and require manual classification.
-Thus the classification effort is reduced by about 77\%.
+%\item 
 %\item \TODO{xx}\% of the comments did not have unanimity (i.e.

### 2014-07-30 sections/results.tex

@@
 %Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e.
-useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.
+We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
+The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.
 
@@
 These comments were not satisfied our models.
-This suggests us that other indicators are needed to satisfy condition and identify usefulness.
+This suggests us that other indicators are needed to investigate for usefulness classification.
+
 %From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
@@
 \hline \hline
-Useful & 3 & 12 & 24 & 94 & 0.706\\
+Useful & 3 & 12 & 24 & 95 & 0.709\\
 Useless & 69 & 23 & 7 & 6 &  0.657\\
 Overlap & 1 & 1 & 0 & 1 & - \\
-Undetermined & 12 & 24 & 20 & 21 & - \\
+Undetermined & 12 & 24 & 20 & 20 & - \\
 \hline
-Recall & 0.812 & - & - & 0.770\\ \hline 
+Recall & 0.812 & - & - & 0.778\\ \hline 
 \end{tabular}
@@
 %we obtained an average F$_1$ score of 0.693 and 0.681,
-%with standard deviation of 0.090 and 0.118, respectively.
-%This indicates that we can use our approach to classify with confident of 69.8\%.
-
-%After the similarity and distance metrics have been calculated,
-%these metrics appear to be able to separate the useful comments from the non-useful ones,
-%as can be seen in Fig.\ref{fig:scatter}.
-%Note that many comments have a cosine similarity metric of 0.
-%This is because the comment text and the corresponding commit message has no word in comment.
-
-\begin{ResearchQuestions}
-\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
-\end{ResearchQuestions}
-
-To answer this question, timestamps are recorded as three people assess each comment.
-Since three people work on their leisure time, there is much variability in the time between each vote.
-Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
-
-On average, it takes 28 seconds to assess each comment.
-However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
-This also suggests that the time to assess each comment is not normally distributed.
-The standard deviation is 45 seconds.
-
-To estimate the total time for us to assess these 318 comments,
-we multiplied the average time by the number of comments and the number of people.
-This results in 7.42 person hours.
-
-However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
-By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
-That means that about 77\% of the effort is saved.
-
-Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
-As the figure shows, the proportion is similar to the result of .
-
-\begin{table}[!t]
-\caption{Proportion of classifications when applied to the whole data set.}
-\small
-\centering
-\def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
-\hline
-Class &        over all samples & only training data  \\ \hline
-useful &            42.8\%      &      41.8\%         \\
-useless &           33.7\%      &      33.1\%         \\
-undetermined &      23.5\%      &      25.1\%         \\ \hline
-\end{tabular}
-\label{tb:percent}
-\end{table}
-
-%\pick{Note from Dan sensei,}
-%For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
-% Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
-%You cannot, but some estimates are possble
-%first, human beings have a fairly well known rate of making errors in classification
-%second, look at the comments in the training set that the method classified differently, especially the unclear.
-%Review these to see if the method suggested a better classification than was originally made by the assessors
-%You can consider these errors. Now look at what wans the percent of errors in the training set
-%This is also an estimate of the human error rate
+%wit

### 2014-07-30 sections/background.tex
please come back, RQ2.

@@
 For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
-Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
+Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design issues \cite{Bacchelli2013a}.
 Our observations of the Qt project also correspond to this finding.

### 2014-07-30 sections/results.tex
please come back, RQ2.

--- 2014-07-30 sections/results.tex
@@
 \hline \hline
-Useful & 3 & 12 & 24 & 94 \\
+Useful & 3 & 12 & 24 & 95 \\
 Useless & 69 & 23 & 7 & 6 \\
 Overlap & 1 & 1 & 0 & 1 \\
-Undetermined & 12 & 24 & 20 & 21 \\
+Undetermined & 12 & 24 & 20 & 20 \\
 \hline
@@
 %we obtained an average F$_1$ score of 0.693 and 0.681,
-%wit
+%with standard deviation of 0.090 and 0.118, respectively.
+%This indicates that we can use our approach to classify with confident of 69.8\%.
+
+%After the similarity and distance metrics have been calculated,
+%these metrics appear to be able to separate the useful comments from the non-useful ones,
+%as can be seen in Fig.\ref{fig:scatter}.
+%Note that many comments have a cosine similarity metric of 0.
+%This is because the comment text and the corresponding commit message has no word in comment.
+
+\begin{ResearchQuestions}
+\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
+\end{ResearchQuestions}
+
+To answer this question, timestamps are recorded as three people voted on each comment.
+Since three people work in their leisure time, there is much variability in the time between each vote.
+Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
+
+On average, it takes 28 seconds to assess each comment.
+However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
+This also suggests that the time to assess each comment is not normally distributed.
+The standard deviation is 45 seconds.
+
+To estimate the total time for us to assess these 318 comments,
+we multiplied the average time by the number of comments and the number of people.
+This results in 7.42 person hours.
+
+However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
+By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
+That means that about 77\% of the effort is saved.
+
+Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
+As the table shows, the proportions are very similar in both the training dataset and all dataset,
+which may suggest that our model will have a similar performance in the real data.
+
+\begin{table}[!t]
+\caption{Proportion of classifications when applied to the whole data set.}
+\small
+\centering
+\def\arraystretch{1.2}
+\begin{tabular}{ccccccc}
+\hline
+Classification & over all samples & only training data \\ \hline
+useful & 42.8\% & 41.8\% \\
+useless & 33.7\% & 33.1\% \\
+undetermined & 23.5\% & 25.1\% \\ \hline
+\end{tabular}
+\label{tb:percent}
+\end{table}
+
+%\pick{Note from Dan sensei,}
+%For cpost effectivness we can state the reduction percentage in the number of comments that much be checked manually.
+% Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
+%You cannot, but some estimates are possble
+%first, human beings have a fairly well known rate of making errors in classification
+%second, look at the comments in the training set that the method classified differently, especially the unclear.
+%Review these to see if the method suggested a better classification than was originally made by the assessors
+%You can consider these errors. Now look at what wans the percent of errors in the training set
+%This is also an estimate of the human error rate

### 2014-07-30 sections/discussion.tex
revise result for RQ2

--- 2014-07-30 sections/discussion.tex
@@
 %\subsection{Binary Classification}
-\subsection{How much impact of unclear class on model construction?}
-\pick{This topic of discuss should be changed....}
- % noisy data, and binary classification
-Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
-This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
-
-Another approach we tried is to perform a \emph{binary classification}.
-This means we assume that there are no unclear or undetermined comments; only useful and useless.
-For this, we removed the samples with 1 and 2 \texttt{YES} votes from our training set.
-This leaves us with 209 remaining samples, all without a disagreement.
-By performing cross-validation using these samples, we obtained a much better F$_1$ score of 0.896.
-
-However, we could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
-But interestingly, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=2.5in]{posneg}
-\caption{The amount of comments by score classified by the binary classifier.}
-\label{fig:binary}
-\end{figure}
+%\subsection{How much impact of unclear class on model construction?}
+%\pick{This topic of discuss should be changed....}
+% % noisy data, and binary classification
+%
+% 
+% 
+%Our training data contains much variability because there are disagreements between our judgment of ``usefulness,'' rendering our results unclear; they cannot be classified as either useful or not useful.
+%This impacts the trade-off between the precision and recall for our model, and consequently, the F$_1$ score.
+%
+%Another approach we tried is to perform a \emph{binary classification}.
+%This means we assume that there are no unclear or undetermined comments; only useful and useless.
+%For this, we removed the samples with 1 and 2 \texttt{YES} votes from our training set.
+%This leaves us with 209 remaining samples, all without a disagreement.
+%By performing cross-validation using these samples, we obtained a much better F$_1$ score of 0.896.
+%
+%However, we could not objectively measure the F$_1$ score for all samples, because giving positive or negative classification to 1 and 2-scored samples introduces a bias.
+%But interestingly, the results seen in Fig.\ref{fig:binary} suggests that the binary classifier tends to gives positive classification to samples with score of 2 more than samples with score of 1, and the \emph{vice versa} for negative classification.
+%
+%\begin{figure}[h]
+%\centering
+%\includegraphics[width=2.5in]{posneg}
+%\caption{The amount of comments by score classified by the binary classifier.}
+%\label{fig:binary}
+%\end{figure}
 
@@
 \subsection{Can the determined thresholds in this study be used to other projects?} 
+\pick{need to be revised}
 This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.

### 2014-07-30 sections/results.tex
revise result for RQ2

@@
 \hline \hline
-Useful & 3 & 12 & 24 & 95 & 0.709\\
-Useless & 69 & 23 & 7 & 6 &  0.657\\
+Useful Class & 3 & 12 & 24 & 95 & 0.709\\
+Useless Class & 69 & 23 & 7 & 6 &  0.657\\
 Overlap & 1 & 1 & 0 & 1 & - \\
@@
 
-According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random model as twice.}
+According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random  classification models as twice.}
 
@@
 
-To answer this question, timestamps are recorded as three people voted on each comment.
-Since three people work in their leisure time, there is much variability in the time between each vote.
-Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
+Automatic system generally known that it can  save human effort  and also reduce erroneous from human.
+We analyse the results to determine the performance of our models.
+Moreover, we also consider scalability of our models as it only validated in the small set of comments.
+\pick{Trying to explain why we considering this}
 
-On average, it takes 28 seconds to assess each comment.
-However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
-This also suggests that the time to assess each comment is not normally distributed.
-The standard deviation is 45 seconds.
+\textbf{Cost Efficiency:} We determined cost efficiency in terms of time use for manual assessment.
+For 318 comments in RQ1, we found that the manual assessment took \TODO{XX} person hours on average.
+However, this time can be inaccurate since practitioners did not assess under the controlled environment.
+To be more precise, we considered only the interval time less ten minutes.
+The average interval time is 28 seconds.
+Thus, for 318 comments, the assessment time should be 7.42 person hours.
+Using the same average interval time for all 10,583 comments, we can imply that the manual assessment time would be 82.3 person hours.
+When applying our approach to classify these all comments, the models left only 23.5\% of comments for manual assessment (undetermined comments) as shown in Table  \ref{tb:percent}.
+This means that an additional manual assessment needs only 19.34 person hours for these undermined comments which save human effort 76.5\%.
 
-To estimate the total time for us to assess these 318 comments,
-we multiplied the average time by the number of comments and the number of people.
-This results in 7.42 person hours.
+%To answer this question, timestamps are recorded as three people voted on each comment.
+%Since three people work in their leisure time, there is much variability in the time between each vote.
+%Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.
+%
+%On average, it takes 28 seconds to assess each comment.
+%However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
+%This also suggests that the time to assess each comment is not normally distributed.
+%The standard deviation is 45 seconds.
+%
+%To estimate the total time for us to assess these 318 comments,
+%we multiplied the average time by the number of comments and the number of people.
+%This results in 7.42 person hours.
+%
+%However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
+%By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
+%That means that about 77\% of the effort is saved.
 
-However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
-By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
-That means that about 77\% of the effort is saved.
+\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores.
+The classification of useless class also have similar proportion i.e.
+having high number of comment with \texttt{YES} = 0 and 1 voting scores.
+We conjecture that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with \texttt{YES} = 1 can be useless comments.
+This might be an error prone from the manual assessment.
+To verify this, we asked practitioners to re-examined the unclear comments.
+We found that there are \TODO{XX}\% of 66 unclear comments changed an answer.
+This indicates that ......
 
-Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
+%As the manual classification can be subjective, these comments were not received three voting scores.
+
+\textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
 As the table shows, the proportions are very similar in both the training dataset and all dataset,
@@
 \begin{table}[!t]
-\caption{Proportion of classifications when applied to the whole data set.}
+\caption{Percentage of classifications results for all comments in the \texttt{qtbase} project }
 \small
@@
 \def\arraystretch{1.2}
-\begin{tabular}{ccccccc}
+\begin{tabular}{c|c|c}
 \hline
-Classification & over all samples & only training data \\ \hline
-useful & 42.8\% & 41.8\% \\
-useless & 33.7\% & 33.1\% \\
-undetermined & 23.5\% & 25.1\% \\ \hline
+
+Result from & Sample Comments   &  All Comments \\ \cline{2-3}
+Classification Models &  318 comments  & 10,583 comments \\ \hline \hline
+Useful Class  & 41.8\% & 42.8\% \\
+Useless Class   & 33.1\%  & 33.7\% \\
+undetermined  & 25.1\% & 23.5\% \\ \hline
 \end{tabular}

### 2014-07-31 sections/results.tex
sum the number of unclear set.

@@
 
-\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 60, 51, and 122 for useless set (\texttt{YES} = 0), unclear set (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively.
+\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively.
 The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.

### 2014-07-31 sections/results.tex
fix some sentence joiners

@@
 The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model.
-The comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless.
-While, the comments drawn in the white area are those not satisfied any condition (i.e.
+The comments drawn in the green area are those satisfied condition of useful model, and the comments drawn in the red area are those satisfied condition of useless, while the comments drawn in the white area are those not satisfied any condition (i.e.
 \emph{undetermined}).

### 2014-07-31 sections/results.tex
change some wording of the result

@@
 %%Interpret: comments & model%%%%
-Corresponding to the precision and recall values, the figure shows that most comments drawn in green area are comments of useful set and very few comments of useless set drawn in this area.
-Similarly, most comments in the red area are comments of useless set.
+Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments of useless set drawn in this area.
+Similarly, majority of comments drawn in the red area are comments from the useless set.
 It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
-Most of useful set (\texttt{YES} = 3) adhere in the top left of the graph while useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
-However, the unclear set still spread out over the graph which we cannot determine relationship between their similarity values.
+Most comments from the useful set (\texttt{YES} = 3) adhere in the top left of the graph
+while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
+However, the unclear set still spread out over the graph.
+Therefore, we cannot determine relationship between their similarity values.
 
-There is an overlap section as shown in Fig. \ref{fig:scatter}. This is a conflict results between our two models where a comment received true outcome from both classification models.  
+There is an overlap section as shown in Fig. \ref{fig:scatter}.
+This is a conflict results between our two models where a comment received true outcome from both classification models.  
 This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
-However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
-This is very small error for our models.
+However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap). This is very small error for our models.
 Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}.

### 2014-07-31 sections/conclusion.tex
results and more conclusion on future work

@@
 \section{Conclusions}
+
+In this paper, we propose a practical approach to classify usefulness discussion in MCR based on VSM similarity.
+The results from our case study show that our approach can classify comments with better performance than a random model both for precision and recall.
+In addition, we found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping).
+For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful.
+The remaining 23\% could not be classified by model, and required manual classification.
+Thus the classification effort is reduced by about 77\%.
+
+More work could be done in the future to relate the amount of useful comments to the software quality, perhaps in a similar way to McIntosh's paper \cite{Mcintosh}.
+This could enable a way of assessing the quality of review process in a quantitative way.

### 2014-07-31 sections/results.tex
results and more conclusion on future work

@@
 
-Automatic system generally known that it can  save human effort  and also reduce erroneous from human.
-We analyse the results to determine the performance of our models.
-Moreover, we also consider scalability of our models as it only validated in the small set of comments.
-\pick{Trying to explain why we considering this}
+Automatic systems are generally known for saving human effort and also reduce human errors.
+We analyze the results to determine the performance of our models.
+In addition, we also consider scalability of our models as it only validated in the small set of comments.
+% \pick{Trying to explain why we considering this}
 
-\textbf{Cost Efficiency:} We determined cost efficiency in terms of time use for manual assessment.
-For 318 comments in RQ1, we found that the manual assessment took \TODO{XX} person hours on average.
+\textbf{Cost Efficiency:}
+% briefly explain
+We determined cost efficiency in terms of time use for manual assessment.
+For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
 However, this time can be inaccurate since practitioners did not assess under the controlled environment.
-To be more precise, we considered only the interval time less ten minutes.
-The average interval time is 28 seconds.
+
+% nitty-gritty details
+To be more precise, we considered only the time interval between two votes that are not more than 10 minutes apart.
+The average time interval between votes is 28 seconds.
 Thus, for 318 comments, the assessment time should be 7.42 person hours.
-Using the same average interval time for all 10,583 comments, we can imply that the manual assessment time would be 82.3 person hours.
+Using the same average interval time for all 10,583 comments,
+we can imply that the manual assessment time would be 82.3 person hours.
+
+% how our model helps
 When applying our approach to classify these all comments, the models left only 23.5\% of comments for manual assessment (undetermined comments) as shown in Table \ref{tb:percent}.
-This means that an additional manual assessment needs only 19.34 person hours for these undermined comments which save human effort 76.5\%.
+This means that only 19.34 person hours of additional manual assessment of these undermined comments are needed, thus saving 76.5\% of human effort.
 

### 2014-07-31 sections/discussion.tex
edited the discussions

@@
 \section{Discussion}
-Our results have shown that using semantic similarity can classify usefulness of comments and our approach also can reduce human effort ant error prone of manual classification.
+Our results have shown that using semantic similarity can classify the usefulness of comments
+and that our approach can also reduce human effort and error proneness of manual classification.
 Besides the results, we also found interesting findings in our case study.
@@
 \subsection{What kind of comments cannot be classified using semantic similarity?}
+
 From the results of RQ1, we found that some comments were not determined by our models.
@@
 We found that there were few common keywords between comments and commit messages and their length are relatively unequal.
-This makes low similarity values and low dissimilarity values as they shown in  bottom left white area in Fig.
-\ref{fig:scatter} which our models cannot determine.
+This makes low similarity values and low dissimilarity values as they shown in  bottom left white area in Fig. \ref{fig:scatter} which our models cannot determine.
 
@@
 \subsection{Can other text mining techniques be used to classify discussions?}
-To find relevance between comments and the corresponding commit message, topic modeling technique can be used as the study of \cite{Barua2012a}.
+To find relevance between comments and the corresponding commit message,
+topic modeling technique can be used, as the study of \cite{Barua2012a}.
 This technique discovers topics for a given collection of documents.
-However, in MCR context, the documents generally is short descriptions and short discussions.
-The topic modeling technique would generate topics that include diverse actual topics of documents since the content of documents is insufficient to determine.
-We have applied Latent Dirichlet allocation (LDA), which is a well-known model of topic modeling techniques, on our data set.
-We found that the generated topics were diverse and some of them cannot did not have a relation between documents and their topics.
-Therefore, the topic modeling cannot be used to classify discussions.
-Others techniques will be investigated in our future work to improve our approach.
+However, in MCR context, the documents generally are short descriptions and discussions, which makes it unsuitable for LDA.
+Nevertheless, we have tried applying Latent Dirichlet Allocation (LDA, a well-known topic modeling techniques) model on our data set.
+The topic modeling technique generated ambiguous topics with many unrelated keywords, since the content of the documents too short, and thus is insufficient for LDA to correctly determine the topic.
+Others techniques could be investigated in the future to improve the results.
 

### 2014-07-31 sections/discussion.tex
revised discussion question 4

@@
 We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters.
-For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) little direct to the proposed changes, 3) discuss about process workflow and supporting system i.e.
-Git and Gerrit.
+For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g.
+Git and Gerrit).
 %During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:
@@
 \subsection{Can the determined thresholds in this study be used to other projects?}
-\pick{need to be revised}
-This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
-Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
-This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
 
 In this study, we determined the similarity conditions using training set in Qt project and the results show that the conditions can classify usefulness of comments.
-However, to apply our approach on other projects, preparing training set is still required and it cost human effort.
-To fully automate this approach, we will investigate the use of similarity conditions for cross projects.
-Thus, additional studies are needed to improve our approach.
+However, to apply our approach on other projects, training set preparation is still required and it cost human effort.
+This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+To fully automate this approach, we have to investigate the use of similarity conditions for many other different projects. Thus, additional studies are needed to improve our approach.
+
+%
+%Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+This decreases the cost-effectiveness and limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.

### 2014-07-31 sections/abstract.tex
Rewrote the abstract

@@
 \begin{abstract}
-Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project.
-Its main intention is to early identify defects before integrating changes.
-Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and put into software development regularly in both industrial and OSS projects.
-The main benefit of MCR is that in-person meetings are not required, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}.
-Reviewers can find defects and discuss by adding comments through a code review tool or a mailing list.
-Developers will then fix their changes following those comments.
-
-% the freeform style of modern code review
-Even though Modern Code Review has less process overhead, it can be less effective if not done properly.
-\TODO{explain about our methods}
-
-% some comments are not technically contributing
+Modern Code Review (MCR) where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list has  received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
+Recent studies have indicated a positive relationship between the number of review comments and code quality.
+However little research exists investigating how such discussion impacts software quality.
+In fact there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated  issues.
+Indeed we have observed that such comments are quite frequent and may even constitute the majority.
+We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are "useful").
+To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not.
+For a large OSS project such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.
+We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments.
+Our case-study results indicate that our approach can classify comments with significant precision and recall and reduce classification effort by about 77\%.
 

### 2014-07-31 sections/results.tex
add results for unclear

@@
 having high number of comment with \texttt{YES} = 0 and 1 voting scores.
-We conjecture that the unclear comments with \texttt{YES} = 2 can be useful comments and comments with \texttt{YES} = 1 can be useless comments.
-This might be an error prone from the manual assessment.
-To verify this, we asked practitioners to re-examined the unclear comments.
-We found that there are \TODO{XX}\% of 66 unclear comments changed an answer.
-This indicates that ......
+We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless.
+The unclear result could be from error of manual assessment caused by human.
+To verify this conjecture, we asked practitioners to re-examine the unclear comments.
+We found that 17\% of these 66 comments became unclear because of human error.
+This shows that our model \thai{what can we say about this model?}
 

### 2014-08-01 sections/abstract.tex
reword

@@
 \begin{abstract}
-Modern Code Review (MCR) where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list has  received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
+Modern Code Review (MCR)---where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list---has received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
 Recent studies have indicated a positive relationship between the number of review comments and code quality.
-However little research exists investigating how such discussion impacts software quality.
-In fact there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated  issues.
-Indeed we have observed that such comments are quite frequent and may even constitute the majority.
-We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are "useful").
+However, little research exists investigating how such discussion impacts software quality.
+In fact, there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated issues.
+Indeed, we have observed that such comments are quite frequent and may even constitute the majority.
+We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are ``useful'').
 To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not.
@@
 We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments.
-Our case-study results indicate that our approach can classify comments with significant precision and recall and reduce classification effort by about 77\%.
+Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce classification effort by about 77\%.
 

### 2014-08-01 sections/conclusion.tex
reword

@@
 
-More work could be done in the future to relate the amount of useful comments to the software quality, perhaps in a similar way to McIntosh's paper \cite{Mcintosh}.
-This could enable a way of assessing the quality of review process in a quantitative way.
+More work could be done in the future to relate the amount of useful comments to the software quality.
+This could enable a way of assessing process quality in a quantitative way.
+Future work could also consider different models other than semantic similarity.

### 2014-08-01 sections/introduction.tex
reword

@@
 Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
-Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
+Nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
 One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.

### 2014-08-01 sections/approach.tex
moved the footnote to the end of paragraph

@@
 
-\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless}\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.} comment as one that does not.
+\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless} comment as one that does not\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.}.
 

### 2014-08-02 sections/results.tex
reword
just present the result about assurance

@@
 \subsection{Research Questions}
-We addressed two research questions: \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?
+% We addressed two research questions: \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?
 and \textbf{RQ2:} Is semantic similarity classification cost-efficient, assurable, and scalable?.
-\pick{Do we need motivation for these RQs?}
+% \pick{Do we need motivation for these RQs?}
+% Thai sez: these recitation of research questions are very redundant...
+%           for the motivation, I think it should have been discussed at the introduction.
+
 %\pick{I realize that your figure is better for the presentation :)}
@@
 We found that 17\% of these 66 comments became unclear because of human error.
-This shows that our model \thai{what can we say about this model?}
+%This shows that our model \thai{what can we say about this model?}
 

### 2014-08-02 sections/abstract.tex
Touched up abstract

@@
 \begin{abstract}
-Modern Code Review (MCR)---where reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list---has received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
+Modern Code Review (MCR) is a practice whereby reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list.
+It has received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
 Recent studies have indicated a positive relationship between the number of review comments and code quality.
@@
 We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments.
-Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce classification effort by about 77\%.
+Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce comment usefulness assessment effort by about 77\%.
 

### 2014-08-02 sections/results.tex
explained the result
minor changes

@@
 \textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively.
-The precision and Recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
+The precision and recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
 
@@
 %%Interpret: comments & model%%%%
-Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments of useless set drawn in this area.
+Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set drawn in this area.
 Similarly, majority of comments drawn in the red area are comments from the useless set.
@@
 This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
-However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap). This is very small error for our models.
-Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}.
+However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
+This means that the erroneous overlapping section is relatively small.
+Excluding the overlaping classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}.
 Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area).
@@
 
-According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach successfully classify comment usefulness with precision of 0.6 and recall of 0.7 approximately and this is better than random  classification models as twice.}
+According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random  classifier.}
 
@@
 We found that 17\% of these 66 comments became unclear because of human error.
+This shows that some unclear comments are actually useful or useless, thus giving our model more confidence.
 %This shows that our model \thai{what can we say about this model?}

### 2014-08-03 sections/abstract.tex
Introduction edited, elaborated scalability in Results

@@
 \begin{abstract}
-Modern Code Review (MCR) is a practice whereby reviewers virtually discuss proposed changes by adding comments through a code review tool or a mailing list.
-It has received much attention recently due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
-Recent studies have indicated a positive relationship between the number of review comments and code quality.
+Modern Code Review (MCR) is an informal practice whereby reviewers virtually discuss proposed changes by adding comments through a code review tool or mailing list.
+It has received much research attention due to its perceived cost-effectiveness and popularity with industrial and OSS projects.
+Recent studies indicate there is a positive relationship between the number of review comments and code quality.
 However, little research exists investigating how such discussion impacts software quality.
-In fact, there has been concern that the informality of MCR encourages a focus on trivial, tangential, or unrelated issues.
+The concern is that the informality of MCR encourages a focus on trivial, tangential, or unrelated issues.
 Indeed, we have observed that such comments are quite frequent and may even constitute the majority.
 We conjecture that an effective MCR actually depends on having a substantive quantity of comments that directly impact a proposed change (or are ``useful'').
-To investigate this, a necessary step requires distinguishing review comments that are useful to a proposed change from those that are not.
-For a large OSS project such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.
-We propose that semantic similarity is a practical, cost-efficient, and empirically assurable approach for assisting with such assessments.
+To investigate this, a necessary first step requires distinguishing review comments that are useful to a proposed change from those that are not.
+For a large OSS projects such as our Qt case study, manual assessment of the over 72,000 comments is a daunting task.
+We propose to utilize semantic similarity as a practical, cost-efficient, and empirically assurable approach for assisting with the manual usefulness assessment of MCR comments.
 Our case-study results indicate that our approach can classify comments with an average F-measure score of 0.73 and reduce comment usefulness assessment effort by about 77\%.

### 2014-08-03 sections/introduction.tex
Introduction edited, elaborated scalability in Results

--- 2014-07-30 sections/introduction.tex
@@
 \section{Introduction}
-Software code review is an established cost-effective software quality management practice.
-Its main intent is to  identify  defects early and encourage quality development practices such as adherence to coding standards and improving code readability.
-Nowadays less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} have received much attention and are commonly used within both industry and OSS projects.
+Software code review is a well-established software quality management practice.
+Fundamentally the intent is to identify defects early and encourage quality development policy and practices such as adherence to coding standards and improving code readability.
+Traditionally code reviews were a highly structured activity.
+Nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects.
 One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
@@
 %Fig. \ref{fig:process} illustrates a typical MCR process. 
-
-Because performance of code review has a clear relationship to the quality of the software, many studies have investigated factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
-However, little research exists investigating how review discussion for a proposed change impacts software quality.
+The popularity of MCR and readily available data have made it an attractive research area.  
+In particular, because performance of code review has a clear relationship to the quality of the software, many studies have investigated the factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013} effectiveness.
+However, little research exists investigating \emph{how} review discussion for a proposed change impacts software quality.
 Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
-it is possible that they can either positively contribute to the proposed changes (i.e.
+it's possible that comments can either positively contribute to the proposed changes (i.e.
 are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e.
 relatively ``\emph{useless}'').
-Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g.
-coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
+Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to focus on trivial issues (e.g.
+coding styles), leaving deeper and possibly more quality-important issues undiscussed \cite{Bacchelli2013a}.
 %This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
-This is a concern because a low-degree of useful comments can degrade the overall quality and perceived utility of MCR.
+This is a concern because a low-degree of useful comments may degrade the overall effectiveness and perceived utility of MCR.
 
-Prior research has focused mostly on the relation between number of comments and quality.
+Prior research has focused primarily on the relationship between number of comments and quality.
 To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
-One reason for this may be that to assess the impact of discussion in MCR, effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
-MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify their usefulness.
-Moreover, comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible misinterpretation.
+One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
+So while the data may be easy to access, MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
+Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.
 
@@
 In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
-The proposed approach is meant to ease classifying large amounts of MRC comments in order to conduct comment and code quality studies (such as those discussed earlier) as manual classification can quickly become an untenable task.
-By introducing automation support based on objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
+As manual classification can quickly become an untenable task, our proposed approach is meant to ease classifying large amounts of MCR comments in order to conduct comment and code quality studies (such as those discussed earlier).
+By introducing automation support for assessment grounded with objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MCR data sets.
 %Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
-Through a case study of Qt project, we address the following research questions:
+Hence through our case study of Qt project, in this work we explore the following research questions:
 \begin{ResearchQuestions}
@@
 \begin{itemize}
-\item We propose a practical approach to mine natural text of comments in code reviews and classify their usefulness using semantic similarity.
-\item We investigate relationship between usefulness of comments and semantic similarity.
-\item We investigate cost-efficient, assurable and scalable of semantic similarity in large open source project based on actual human effort.
+\item An investigation on the practicality of mining natural text comments in code reviews to classify their usefulness using semantic similarity.
+\item Determination and validation of a model relating usefulness of comments and semantic similarity.
+\item A case-study application and performance analysis of the model for a large open source project based (Qt) on actual human effort.
 \end{itemize}

### 2014-08-03 sections/results.tex
Introduction edited, elaborated scalability in Results

@@
 \textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
-As the table shows, the proportions are very similar in both the training dataset and all dataset,
-which may suggest that our model will have a similar performance in the real data.
+As the table shows, the proportions are very similar in both the training dataset and all dataset.
+Indeed experiments for our case study using increasingly large random subsets of comments show the percentage of undetermined and overlap classification comments (and hence the manual effort required) is constant at about 23\%.
+While the percentage might vary for other projects, this result suggests that our method is scalable to very large numbers of comments.
+That is, the percentage of unclassified comments does not increase and hence we expect the method will reduce a substantial amount of manual assessment effort.
+This enables us to assess MCR comments for very large projects that currently are impractical to do without assistance.
+\dan{can we find a suitable example project to get some numbers for the example below?}
+For example, OSS project XXX currently has YYY comments.
+Assuming constant effort and error rate (a dubious assumption), manual assessment effort for these would be estimated at ZZZ hours which is fundamentally impractical.
+However using similarity assessment with an estimated 23\% unclassified comments would reduce this effort to QQQ, a much more tractable effort.
 

### 2014-08-03 sections/background.tex
edited introduction and background sections

@@
 
-An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}.
-The grey area shows the review process of the system which composed of four main steps:
-(1) an author creates a patch and submits a set of new or modified files as a review request to Gerrit system.
-(2) reviewers examine the proposed code changes for defects or concerns.
-(3) reviewers provide comments to the author.
+An overview of MCR process based on the Gerrit code review system is shown in Fig. \ref{fig:process}.
+The grey area shows the review process of the system which is composed of four main steps:
+(1) An author creates a patch and submits a set of new or modified files as a review request to the Gerrit system.
+(2) Reviewers examine the proposed code changes for defects or concerns.
+(3) Reviewers provide comments to the author.
 The author creates a revised proposed change according to the comments and re-submits for review.
-Then, reviewers will examine the revised proposed change.
+Reviewers then examine the revised proposed change.
 If the revision is not approved, reviewers provide comments to fix and the process continues until
@@
 According to this process, reviewers' comments are the most important factor in determining software quality.
-In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
-However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.
+In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion (i.e. no comments) are likely to contain bugs.
+However, it has not been shown that components with comments are less likely to contain bugs.
+Tools supporting MCR such as Gerrit allow reviewers to freely write messages to authors (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness and consequently may have little impact on quality.
 % (e.g. coding styles, documentation, process workflow, etc.)
-For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
+For example, a comment may be related to something outside the scope of the proposed change, perhaps author or reviewer personal issues or inter-personal communication e.g.
+``Keep up the good work everyone!".
 Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design issues \cite{Bacchelli2013a}.
-Our observations of the Qt project also correspond to this finding.
-We found that some comments are superficial and unhelpful to the proposed changes.
-For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
-while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.
+Our observations of the Qt project also corroborate this finding.
+We found that many examples of comments that are superficial and unhelpful to the proposed changes.
+For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is certainly within the scope of the proposed change, yet provides little useful information.
+While the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope, and not directly useful for the proposed change.
+
+Ultimately our aim is to understand the impact of useful and useless comments on code quality.
+Specifically, what degree of useful comments are needed to effect positive impact on quality.
+Study of this necessitates ascertaining, with high confidence, the usefulness of a large number of comments.
+This  had proven difficult to accomplish manually, so here we investigate the pragmatics of using semantic similarity to assist with this task.
 

### 2014-08-03 sections/introduction.tex
edited introduction and background sections

@@
 One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
-So while the data may be easy to access, MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
+So while the data may be easy to access, MCR can produce a massive amounts of change requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
 Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.
@@
 \item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
-\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
+\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable for large MCR data sets?
 \end{ResearchQuestions}
 
-Our contributions are as follows:
+The contributions in this paper are as follows:
 \begin{itemize}

### 2014-08-03 sections/approach.tex
Approach section edited. Some references are needed.

@@
 
-\textbf{Definition:} We define a \emph{useful} comment as one that contributes to improving the proposed change, and a \emph{useless} comment as one that does not\footnote{Although we call these comments \emph{useless} in our study, it might actually be useful---or sometimes even required---in some other contexts, such as to facilitate communication or to enforce guidelines.}.
+\textbf{Definition:} We define a \emph{useful} comment as one that directly contributes to improving a proposed change, and a \emph{useless} comment as one that does not\footnote{Although we call these comments \emph{useless} in our study, it might actually have utility--or sometimes  be required---in some other contexts, such as to facilitate communication or to enforce guidelines or process.}.
 
-Our goal is to improve the efficiency and confidence in determining the usefulness of review comments.
-Usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential.
-Therefore, our approach is largely based on relevance the comment has to the proposed change (as documented within a MCR system).
+Our goal here is to improve the efficiency and confidence in the task of determining the usefulness of review comments.
+As with many subjective assessments, usefulness is not dichotomous and hence we must accept a third qualification, \emph{unclear}, to allow for the case where a comment does not directly make a positive contribution but is not clearly out of scope or tangential i.e.
+it may be useful.
+Our approach is largely based on the assumption that usefulness is determined by the relevance a comment has to the proposed change (as documented within a MCR system).
 A primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}\cite{Davies2012}. 
 %\dan{can we find a reference for relevance and similarly?}
-We assume that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
-Conversely, the more dissimilar\footnote{This can be arbitrarily large, thus not simply the opposite of similarity}, the less relevant, and hence less useful.
+We speculate that the more similar a comment is to the proposed change, the more relevant it is and hence more likely useful.
+Conversely, the more dissimilar\footnote{This is technically not simply the opposite of similarity.
+Unlike similarity, dissimilarity can be arbitrarily large.}, the less relevant, and hence less useful.
 
 \subsection{Approach}
+We seek to develop a model based on similarity criteria to classify (i.e. \emph{determine}) comments as either useful or useless. 
 Given the subjective nature of usefulness, precise classification conditions probably do not exist and so we resort to conditions that indicate a meaningful \emph{likelihood} of classification.
-That is, for some degree of similarity a comment is most likely useful, and for some degree of dissimilarity it is most likely useless.
-The key is to determine these degrees in a practical and effective manner.
+That is, for some degree of similarity a comment is determined to be \emph{most likely useful}, and for some degree of dissimilarity it is \emph{most likely useless}.
+Because this is a liklihood model, it is possible that a classification cannot be determined (i.e.
+no classification is likely enough) or determined to be in multiple classifications (i.e.
+overlap in likelihood conditions).
+It's important to keep in mind that these last two outcomes are not actual classifications whose interpretation is difficult and perhaps unreliable.
+The key to our approach is to determine the classification conditions in a practical, assurable manner that also is effective to use for assessing comment usefulness.
 
@@
 The conditions are simply threshold values of similarity and dissimilarity empirically determined to optimize a desired likelihood objectives.
+While more complex conditions are possible and may perform better, we begin with this simple model and investigate if it is sufficient for our assessment task.
 
@@
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-We calculate semantic similarity using the Vector Space Model (VSM) with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language; and the Euclidian distance, which is a well-established measure of dissimilarity and applies analogously.
+We calculate semantic similarity using the Vector Space Model (VSM) 
+\dan{need a reference for this}
+with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language.
+The Euclidian distance, which is a well-established measure of dissimilarity,  applies here analogously for retrieving irrelevant documents.
 %For our case example training dataset, we manually identified 320 randomly-selected pairs of comments and corresponding commit messages in Fig.
@@
 
-Our training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
+The model is a form of \emph{supervised classification} 
+\dan{need a reference for this}
+where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g.
+likelihood that a comment is useful given its similarity is greater than some threshold value.
+The training data is a small set of randomly-selected pairs of comments and the corresponding commit messages.
 These comments are manually assessed for usefulness.
@@
 For statistical purposes, at least 30 useful and 30 useless comments must be collected.
-The similarity and dissimilarity metrics are then computed for the data set.
+The similarity and dissimilarity metrics are then computed for the training data set.
 These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
@@
 We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
+\dan{need a reference for this}
 which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
-In this study, we used the F$_1$-measure, which equally prioritize precision and recall.
-Different weighting can be used by different F$_\beta$ measures depending on an application.
+In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
+Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.
 
-\subsection{Usefulness Classification Conditions} 
-Using those thresholds, we can classify the usefulness of comments for the rest of comments (as test data) in review history according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
+\subsection{Usefulness Classification Model} 
+Using thresholds derived from the training data as discussed above, we can classify the usefulness of comments for the entire review according to the classification model as follows: given a comment $c$ and a corresponding commit message $m$,
 \begin{itemize}
-\item \textbf{useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
-\item \textbf{useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
-\item \textbf{undetermined}: neither or both of the above conditions are $\True$.
+\item \textbf{Useful}: $\Theta(c,m,S_T,D_T) = \True$ iff $\Sim(m,c) \geq S_T$ and $\Dist(m,c) \leq D_T$.
+\item \textbf{Useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
+\item \textbf{undetermined}: neither (no condition holds) or both (overlap of conditions) of the above conditions are $\True$.
 % We also refer to them as \emph{neither} and \emph{overlap}.
@@
 Two metrics are used because they are independently generated and thus provides better discrimination for classification.
-We also found experimentally that using two metrics has higher performance than just one.
+We also found experimentally that using two metrics has higher performance than just one. We note again that ``undetermined" is not a meanigful classification in our model.
 
@@
 While our proposed approach is straightforward, empirically driven, and automatically adjusts to the quality of the data, it has a few drawbacks.
-We have to accept that some comments cannot be reliably or confidently classified.
-We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be assessed subjectively).
-Secondly, owing to the subjective assessment of usefulness, this representation fundamentally implies supervised classification requiring nontrivial training data to define representative classification sets.
+First, we must accept that some comments cannot be reliably or confidently classified.
+We denote these as \emph{undetermined} to differentiate them from comments whose usefulness is \emph{unclear} (i.e. cannot be subjectively assessed as useful or useless).
+Secondly, owing to the subjective assessment of usefulness and our need to represent this, not just any classification, this fundamentally implies performing supervised classification requiring nontrivial training data to define representative classification sets.
 

### 2014-08-03 sections/introduction.tex
added punctuations to the second sentence for disambiguation

@@
 Software code review is a well-established software quality management practice.
-Fundamentally the intent is to identify defects early and encourage quality development policy and practices such as adherence to coding standards and improving code readability.
-Traditionally code reviews were a highly structured activity.
-Nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects.
+Fundamentally, the intent is to identify defects early and encourage quality development policy and practices (such as adherence to coding standards and improving code readability).
+Traditionally, code reviews were a highly structured activity, but nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects.
 One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.

### 2014-08-03 sections/results.tex
done editing approach and results. Some additional examples may be needed

@@
 
-Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et.
+Our case study uses the Qt project review history from the Gerrit code review tool provided by Hamasaki et.
 al.
@@
 \subsection{Data Preparation}
-We used the commit messages and comments in the dataset.
+We use the commit messages and comments within Gerrit as our data set.
 Before classifying the usefulness of comments, we first processed the commit message and comments as follows:
 
-\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
+\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignore all messages that were automatically generated e.e. bot messages.
 %In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
-These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
+These automatic messages are generated by Gerrit, the continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
 \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples.
-In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
+In practice, they are not considered in a code review  and are not substantively relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
 
-To do so, we first ignore all comments written by bots (i.e.
-\emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}).
-Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression.
-This would leave us only human-written comments that will be used in further preprocessing.
+We first find and remove all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). These are easily detected by their automatically generated signature 
+e.g. XXX 
+\dan{good example here} 
+Next, we removed messages, including reviewers comments, with common useless patterns or occur frequently using regular expressions. Some example are XXX
+\dan{good example here} 
+This leaves us only human-written comments that cannot automatically be classified as useless.
 
@@
 \subsection{Manual Comment Usefulness Assessment}
-In this case study, three participants (the first two authors and one student) independently classified comments by giving a question, ``does this comment technically contribute to its change or not?''
+In this case study, three participants (the first two authors and one student) independently assessed comment usefulness by addressing the question, ``Is this comment directly useful for approving or modifying the change request?''
 Then, the participants gave a vote for \texttt{YES} if the comment is likely to be useful and \texttt{NO} otherwise.
-From the voting scores, we regarded that the comments with three \texttt{YES} votes are \emph{useful} comments and the comments with no \texttt{YES} votes (i.e.
+From the voting scores, we regarded comments with three \texttt{YES} votes as \emph{useful} comments, and comments with no \texttt{YES} votes (i.e.
 three \texttt{NO} votes) are \emph{useless} comments.
-For the comments with one and two \texttt{YES} votes, we defined them as unclear comments.
+For the comments with one and two \texttt{YES} votes, we defined them to have \emph{unclear} usefulness.
 
@@
 
-To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
-Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
-We also determined the effectiveness of our approach using bootstrapping cross validation.
+To answer this question, we randomly sampled 318 comments from our data set and manually assessd their usefulness.
+Then, we used these comments for both training and test data for our approach to determine its effectiveness.
+We also determined the confidence in the effectiveness estimates using bootstrapping cross validation to estimate variability in the performance measures due to using sample data.
 
@@
 
-To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
+To determine similarity and dissimilarity thresholds for our model, we iterated $S_t$ and $D_t$ values from every unique similarity and dissimilarity value in our data set.
 %Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
-We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
-The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.
+We selected the thresholds that best classify useful and useless comments based on maximizing the F1-measure score.
+The models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.
 
-\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85, 111, and 122 for useless set (\texttt{YES} = 0), unclear sets (\texttt{YES} = 1 or 2), and useful set (\texttt{YES} = 3), respectively.
-The precision and recall of the models were 0.701 and 0.787 for useful model and 0.648 and 0.824 for useless model.
+\textbf{Model Effectiveness Results:} From 318 samples, the comment sets from manual assessment were 85 were useless (\texttt{YES} = 0),  111 were unclear (\texttt{YES} = 1 or 2), and 122 were useful (\texttt{YES} = 3).
+The precision and recall were 0.701 and 0.787 for useful model, and 0.648 and 0.824 for useless model.
 
-Figure \ref{fig:scatter} shows the relationship between usefulness class from our classification model and comment sets from manual assessment. 
+Figure \ref{fig:scatter} shows the relationship between usefulness classes from our model and comment sets from manual assessment. 
 The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} classification model.
-The comments drawn in the green area are those satisfied condition of useful model, and the comments drawn in the red area are those satisfied condition of useless, while the comments drawn in the white area are those not satisfied any condition (i.e.
-\emph{undetermined}).
+The comments drawn in the green area are those that satisfied the condition for useful comments, and the comments drawn in the red area are those satisfied the useless condition, while the comments drawn in the white area are those not satisfied any condition (i.e.
+\emph{undetermined}) and hence remain unclassified.
 The total number of comments from this classification results is described in Table \ref{tb:classify_number}.
@@
 %%Interpret: comments & model%%%%
-Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set drawn in this area.
-Similarly, majority of comments drawn in the red area are comments from the useless set.
+Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set fall in this area.
+Similarly, the majority of comments drawn in the red area are comments from the useless set.
 It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
-Most comments from the useful set (\texttt{YES} = 3) adhere in the top left of the graph
+Most comments from the useful set (\texttt{YES} = 3) are in the top left of the graph
 while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
-However, the unclear set still spread out over the graph.
-Therefore, we cannot determine relationship between their similarity values.
+However, the unclear set still spread out over the similarity intervals and therefore we cannot determine 
+a relationship with their similarity values. That is, we have no evidence to support that the undetermined set corresponds unclear comments and hence undetermined is not a useful classification.
 
-There is an overlap section as shown in Fig. \ref{fig:scatter}.
-This is a conflict results between our two models where a comment received true outcome from both classification models.  
-This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification.
+There is an overlap section shown in Fig. \ref{fig:scatter}.
+This is a conflict between the two classification conditions where a comment satisfies both simultaneously.  
+This phenomenon can occur since similarity and dissimilarity threshold values of each group are ``fuzzy" and both models tend to maximize coverage of classification.
+Also similarity and dissimilarity are discreet and subject to some degree of granularity issues
 However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap).
-This means that the erroneous overlapping section is relatively small.
-Excluding the overlaping classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}.
+In more extended experiments, less than 2\% were in the overlap set and this contradictory classification is relatively small.
+Excluding the overlap classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}.
 Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area).
-These comments were not satisfied our models.
-This suggests us that other indicators are needed to investigate for usefulness classification.
+These comments were not satisfied our model suggesting that there are likely other indicators different from similarity that determine usefulness.
 
@@
 \textbf{Validation:}
-We validated our approach using bootstrapping cross validation.
+We validated our approach using bootstrapping cross validation. By validation be mean to estimate the variability in the estimate of the 
+performance measures from the training set to indicate how a accurate these are for the method in general.
 We randomly selected 90\% of 318 comments for training set and determine thresholds.
@@
 The precision, recall and F-measure scores are measured and recorded.
-This validation was repeated 300 times to give an average performance of our models.
-For a baseline, we also determined the performance of the random classifier using the same methods.
+This validation was repeated 300 times to give the average and standard deviation for these performance measures. Bootstrapping is 
+used because of concern about our relatively small sample size and possibly instability in using customary Jackknifing cross-validation.
+For a baseline comparison, we also determined the performance of a random classifier (i.e. places items in classes with equal probability) using the same methods.
 
@@
 The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
-In addition, our models also achieved higher results than the random models twice for both precision and recall.
+In addition, while we do not present hypothesis test results, it is clear that our model significantly outperforms the random model on all performance measures e.g.
+mean Precision for Useless is notably higher than Random with about the same standard deviation so it's clearly significant.
 
@@
 
-According to the results, we can answer RQ1 that \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random  classifier.}
+According to our results, we can answer RQ1 as follows: \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random classifier.}
 
@@
 
-Automatic systems are generally known for saving human effort and also reduce human errors.
+Automatic systems are generally known for saving human effort and also reduce errors.
 We analyze the results to determine the performance of our models.
-In addition, we also consider scalability of our models as it only validated in the small set of comments.
+In addition, we also consider scalability of our models as it only validated for small numbers of comments.
+The concern is that the model may behave poorly at larger scale possibly leaving more manual assessment effort than is saved through using the method.
 % \pick{Trying to explain why we considering this}
@@
 For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
-However, this time can be inaccurate since practitioners did not assess under the controlled environment.
+However, this time may be inaccurate since practitioners did not make assessments under a controlled environment.
 

### 2014-08-03 sections/discussion.tex
done with discussion

@@
 \section{Discussion}
-Our results have shown that using semantic similarity can classify the usefulness of comments
-and that our approach can also reduce human effort and error proneness of manual classification.
-Besides the results, we also found interesting findings in our case study.
-We discuss these findings as follows:
+Our results have shown that our semantic similarity is practical to assist in reducing effort and error proneness of manual assessment of comment usefulness.  
+Besides this result, we also found some noteworthy findings in our case study:
 
@@
 
-From the results of RQ1, we found that some comments were not determined by our models.
-Specifically, we were interested in comments with useful class (\texttt{YES} = 3) and useless class (\texttt{YES} = 0).
-To investigate the reason behind this, we observed these comments and the corresponding commit messages.
-We found that there were few common keywords between comments and commit messages and their length are relatively unequal.
-This makes low similarity values and low dissimilarity values as they shown in  bottom left white area in Fig. \ref{fig:scatter} which our models cannot determine.
+From the results of RQ1, we found that some comments were not determined by our model.
+Specifically, we were interested in why some manually assessed useful comments (\texttt{YES} = 3) and useless comments (\texttt{YES} = 0) were undetermined.
+To investigate the reason behind this, we reviewed these comments and the corresponding commit messages.
+We found that there were few common keywords between the comments and commit messages and their lengths are relatively unequal.
+This makes for low similarity values and low dissimilarity values as shown in bottom left white area in Fig. \ref{fig:scatter}. There simply isn't enough semantic information to determine anything.
 
@@
 This technique discovers topics for a given collection of documents.
-However, in MCR context, the documents generally are short descriptions and discussions, which makes it unsuitable for LDA.
-Nevertheless, we have tried applying Latent Dirichlet Allocation (LDA, a well-known topic modeling techniques) model on our data set.
-The topic modeling technique generated ambiguous topics with many unrelated keywords, since the content of the documents too short, and thus is insufficient for LDA to correctly determine the topic.
-Others techniques could be investigated in the future to improve the results.
+However, in MCR context, the documents generally are very short statements and discussions, which makes it unsuitable for LDA. 
+Nevertheless, we have tried applying Latent Dirichlet Allocation (LDA, a well-known topic modeling technique) model on our data set.
+As expected, LDA generated ambiguous topics with many unrelated keywords.
+Again, as discussed above, there is simply not enough information since the content of the documents are too short, and thus is insufficient for LDA to correctly determine the topic.
+Others techniques could be investigated in the future to improve results.
 
@@
 \subsection{What decisions are made during the manual classification?}
-During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes.
-We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters.
+During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments actually direct contribute to the proposed changes.
+We can summarize that most of reasons for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss specific technical matters.
 For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g.
@@
 
-In this study, we determined the similarity conditions using training set in Qt project and the results show that the conditions can classify usefulness of comments.
-However, to apply our approach on other projects, training set preparation is still required and it cost human effort.
-This limits the practicality of application to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
-To fully automate this approach, we have to investigate the use of similarity conditions for many other different projects. Thus, additional studies are needed to improve our approach.
+In this study, we determined the similarity conditions using a training set from the Qt project and the results show that the conditions can indeed classify usefulness of comments.
+However, we have no basis for believing that the threshold values obtained for one project would apply equally well for another project.
+To apply our approach on other projects, a new training set is still required which implies additional manual assessment.
+This limits the practicality of application our our method to projects with a large enough number of comments, where the classification effort saved overcomes the training costs.
+To fully automate this approach, we have to investigate the use of similarity conditions for many other different projects.
+Thus, additional studies are needed to improve our approach and potentially identify invariant conditions for similarly and usefulness.
 

### 2014-08-03 sections/approach.tex
done editing approach and results. Some additional examples may be needed
edit stuff a lot

@@
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-We calculate semantic similarity using the Vector Space Model (VSM) 
-\dan{need a reference for this}
+We calculate semantic similarity using the Vector Space Model (VSM) \cite{wiki:vdm}
 with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language.
@@
 
-The model is a form of \emph{supervised classification} 
-\dan{need a reference for this}
+The model is a form of \emph{supervised classification} \cite{wiki:supervised}
 where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g.
@@
 %Other likelihood functions could be used depending on precision, recall, or risk goals.
-We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure,
-\dan{need a reference for this}
+We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \cite{wiki:f},
 which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
@@
 \item \textbf{Useless}: $\Omega(c,m,S'_T,D'_T) = \True$ iff $\Sim(m,c) \leq  S'_T$ and $\Dist(m,c) \geq D'_T$.
-\item \textbf{undetermined}: neither (no condition holds) or both (overlap of conditions) of the above conditions are $\True$.
+\item \textbf{\emph{undetermined}}: neither (no condition holds) or both (overlap of conditions) of the above conditions are $\True$.
 % We also refer to them as \emph{neither} and \emph{overlap}.
@@
 Two metrics are used because they are independently generated and thus provides better discrimination for classification.
-We also found experimentally that using two metrics has higher performance than just one. We note again that ``undetermined" is not a meanigful classification in our model.
+We also found experimentally that using two metrics has higher performance than just one. We note again that ``undetermined" is not a meaningful classification in our model.
 

### 2014-08-03 sections/results.tex
edit stuff a lot

@@
 
-\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignore all messages that were automatically generated e.e. bot messages.
+\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignore all messages that were automatically generated. % (e.g. bot messages).
 %In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
-These automatic messages are generated by Gerrit, the continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
-\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples.
+These messages may be generated by Gerrit, the continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
+\textit{``Change has been successfully cherry-picked to the staging branch as ...''}, and \textit{`Sanity review passed'} are some examples.
 In practice, they are not considered in a code review  and are not substantively relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.
 
-We first find and remove all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}). These are easily detected by their automatically generated signature 
-e.g. XXX 
-\dan{good example here} 
-Next, we removed messages, including reviewers comments, with common useless patterns or occur frequently using regular expressions. Some example are XXX
-\dan{good example here} 
+We first find and remove all comments written by bots (i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}).
+Next, we removed messages, including reviewers comments, with common useless patterns or occur frequently using regular expressions. Some example are \textit{``Upload patch set 1.''}
 This leaves us only human-written comments that cannot automatically be classified as useless.
@@
 %%Interpret: comments & model%%%%
-Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set, and very few comments from useless set fall in this area.
+Corresponding to the precision and recall values, the figure shows that the majority of comments drawn in green area are comments from the useful set; very few comments from useless set fall in this area.
 Similarly, the majority of comments drawn in the red area are comments from the useless set.
 It also shows that the similarity and dissimilarity values of comments in each set are not different from other comments in the same set.
-Most comments from the useful set (\texttt{YES} = 3) are in the top left of the graph
-while those from the useless set (\texttt{YES} = 0) adhere in the bottom right of the graph.
-However, the unclear set still spread out over the similarity intervals and therefore we cannot determine 
-a relationship with their similarity values. That is, we have no evidence to support that the undetermined set corresponds unclear comments and hence undetermined is not a useful classification.
+Most comments from the useful set are in the top left of the graph
+while those from the useless set adhere in the bottom right of the graph.
+However, the unclear set still spread out over the similarity intervals and therefore we cannot determine  a relationship with their similarity values.
+That is, we have no evidence to support that the set of undetermined comments corresponds to the unclear set, and hence,	 undetermined is not a useful classification.
 
@@
 Excluding the overlap classification results, we can calculate precision and recall as described in Table \ref{tb:classify_number}.
-Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area).
-These comments were not satisfied our model suggesting that there are likely other indicators different from similarity that determine usefulness.
+Furthermore, 12 useless comments (14\%) and 21 useful comments (17\%) are still undetermined (drawn in white area).
+They were not satisfied by our model, thus suggesting that there are likely other indicators different from similarity that determine usefulness.
 
@@
 \textbf{Validation:}
-We validated our approach using bootstrapping cross validation. By validation be mean to estimate the variability in the estimate of the 
-performance measures from the training set to indicate how a accurate these are for the method in general.
+We validated our approach using bootstrapping cross validation.
+By validation, we mean to estimate the variability in the performance measure estimates from the training set to indicate how a accurate these are for the method in general.
 We randomly selected 90\% of 318 comments for training set and determine thresholds.
@@
 The precision, recall and F-measure scores are measured and recorded.
-This validation was repeated 300 times to give the average and standard deviation for these performance measures. Bootstrapping is 
-used because of concern about our relatively small sample size and possibly instability in using customary Jackknifing cross-validation.
+This validation was repeated 300 times to give the average and standard deviation for these performance measures.
+Bootstrapping is used because of concern about our relatively small sample size and possibly instability in using customary jackknifing cross-validation.
 For a baseline comparison, we also determined the performance of a random classifier (i.e. places items in classes with equal probability) using the same methods.
@@
 The results show that both of our models can achieve 60\% of precision and 75\% of recall, approximately.
-In addition, while we do not present hypothesis test results, it is clear that our model significantly outperforms the random model on all performance measures e.g.
-mean Precision for Useless is notably higher than Random with about the same standard deviation so it's clearly significant.
+In addition, while we do not present hypothesis test results, it is clear that our model significantly outperforms the random model on all performance measures (for example, the mean precision for $\Omega$ is notably higher than the random classifier with about the same standard deviation).
 
@@
 
-\textbf{Assurance:} In Table \ref{tb:classify_number}, there are 88\% of useful class have comments with \texttt{YES} = 2 and 3 voting scores.
-The classification of useless class also have similar proportion i.e.
-having high number of comment with \texttt{YES} = 0 and 1 voting scores.
+\textbf{Assurance:} In Table \ref{tb:classify_number},
+88\% of comments classified as useful received \texttt{YES} = 2 and 3 voting scores.
+The classification of the useless class also have similar proportion i.e. having high number of comment with \texttt{YES} = 0 and 1 voting scores.
 We conjecture that the unclear comments with \texttt{YES} = 2 might actually be useful comments and comments with \texttt{YES} = 1 might actually be useless.
@@
 
-\textbf{Scalability:} Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
+\textbf{Scalability:}
+Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
 As the table shows, the proportions are very similar in both the training dataset and all dataset.
 Indeed experiments for our case study using increasingly large random subsets of comments show the percentage of undetermined and overlap classification comments (and hence the manual effort required) is constant at about 23\%.
-While the percentage might vary for other projects, this result suggests that our method is scalable to very large numbers of comments.
-That is, the percentage of unclassified comments does not increase and hence we expect the method will reduce a substantial amount of manual assessment effort.
+While the percentage might vary for other projects, this result suggests that our method is scalable to very large numbers of comments---that is, the percentage of unclassified comments does not increase.
+% and hence we expect the method will reduce a substantial amount of manual assessment effort.
 This enables us to assess MCR comments for very large projects that currently are impractical to do without assistance. 
-\dan{can we find a suitable example project to get some numbers for the example below?}
-For example, OSS project XXX currently has YYY comments.
+%\dan{can we find a suitable example project to get some numbers for the example below?} No more space....
+%For example, OSS project XXX currently has YYY comments.
 Assuming constant effort and error rate (a dubious assumption), manual assessment effort for these would be estimated at ZZZ hours which is fundamentally impractical.

### 2014-08-03 sections/discussion.tex
shorten reference, and comment one subsection of discussion

--- 2014-07-31 sections/discussion.tex
@@
 \section{Discussion}
-Our results have shown that using semantic similarity can classify the usefulness of comments
-and that our approach can also reduce human effort and error proneness of manual classification.
-Besides the results, we also found interesting findings in our case study.
-We discuss these findings as follows:
+%Our results have shown that using semantic similarity can classify the usefulness of comments
+%and that our approach can also reduce human effort and error proneness of manual classification.
+%Besides the results, we also found interesting findings in our case study.
+%We discuss these findings as follows:
 
@@
 % reasons for classification as useful or not useful
-\subsection{What decisions are made during the manual classification?}
-During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes.
+
+%\subsection{What decisions are made during the manual classification?}
+%During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes.
 We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters.
@@
 Git and Gerrit).
+
 %During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

### 2014-08-03 sections/results.tex
shorten reference, and comment one subsection of discussion

@@
 
-According to our results, we can answer RQ1 as follows: \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random classifier.}
+%According to our results, we can answer RQ1 as follows: \emph{using semantic similarity values as indicators, our approach can successfully classify comment usefulness with precision of 0.64 and recall of 0.75 approximately, which is significantly better than a random classifier.}
 
@@
 We determined cost efficiency in terms of time use for manual assessment.
-For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
-However, this time may be inaccurate since practitioners did not make assessments under a controlled environment.
-
+%For 318 comments in RQ1, we found that the manual assessment took 7.42 person hours on average.
+%However, this time may be inaccurate since practitioners did not make assessments under a controlled environment.
 % nitty-gritty details
-To be more precise, we considered only the time interval between two votes that are not more than 10 minutes apart.
+%To be more precise, 
+We considered only the time interval between two votes that are not more than 10 minutes apart since  practitioners did not make assessments under a controlled environment.
 The average time interval between votes is 28 seconds.
@@
 we can imply that the manual assessment time would be 82.3 person hours.
-
 % how our model helps

### 2014-08-04 sections/approach.tex

@@
 Our approach is largely based on the assumption that usefulness is determined by the relevance a comment has to the proposed change (as documented within a MCR system).
-A primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}\cite{Davies2012}. 
+A primary factor in relevance is similarly, and so it is natural for us to consider classification using \emph{similarity conditions}. 
+%\cite{Davies2012}
 %\dan{can we find a reference for relevance and similarly?}
@@
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-We calculate semantic similarity using the Vector Space Model (VSM) \cite{wiki:vdm}
+We calculate semantic similarity using the Vector Space Model (VSM)% \cite{wiki:vdm}
 with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language.
@@
 
-The model is a form of \emph{supervised classification} \cite{wiki:supervised}
+The model is a form of \emph{supervised classification}% \cite{wiki:supervised}
 where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g.
@@
 %Other likelihood functions could be used depending on precision, recall, or risk goals.
-We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \cite{wiki:f},
+We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \footnote{\url{http://en.wikipedia.org/w/index.php?title=F1_score&oldid=608940880}},
 which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).

### 2014-09-07 sections/approach.tex
very minor fixes

@@
 That is, for some degree of similarity a comment is determined to be \emph{most likely useful}, and for some degree of dissimilarity it is \emph{most likely useless}.
-Because this is a liklihood model, it is possible that a classification cannot be determined (i.e.
+Because this is a likelihood model, it is possible that a classification cannot be determined (i.e.
 no classification is likely enough) or determined to be in multiple classifications (i.e.
 overlap in likelihood conditions).
-It's important to keep in mind that these last two outcomes are not actual classifications whose interpretation is difficult and perhaps unreliable.
+It is important to keep in mind that these last two outcomes are not actual classifications whose interpretation is difficult and perhaps unreliable.
 The key to our approach is to determine the classification conditions in a practical, assurable manner that also is effective to use for assessing comment usefulness.
@@
 % Thai sez: Cosine distance IS NOT cosine similarity. Cosine distance is defined as 1 - cosine similarity, and is not a proper distance metric, lacking triangle equality and stuff [Wikipedia].
-We calculate semantic similarity using the Vector Space Model (VSM)% \cite{wiki:vdm}
+We calculate semantic similarity using the Vector Space Model (VSM) % \cite{wiki:vdm}
 with the cosine similarity measure, which is a well-known technique for retrieving relevant documents written in unstructured natural language.
@@
 
-The model is a form of \emph{supervised classification}% \cite{wiki:supervised}
+The model is a form of \emph{supervised classification} % \cite{wiki:supervised}
 where a training set is used to empirically derive similarity and dissimilarity thresholds that optimize meaningful likelihoods e.g.
@@
 The similarity and dissimilarity metrics are then computed for the training data set.
-These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ for useless comments. 
+These are used to estimate the similarity and dissimilarity thresholds $S_T$ and $D_T$ that best discriminate useful comments and $S'_T$ and $D'_T$ from useless comments. 
 %Other likelihood functions could be used depending on precision, recall, or risk goals.

### 2014-09-07 sections/discussion.tex
fix merge conflicts

--- 2014-08-03 sections/discussion.tex
@@
 % reasons for classification as useful or not useful
-\subsection{What decisions are made during the manual classification?}
-During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments actually direct contribute to the proposed changes.
-We can summarize that most of reasons for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss specific technical matters.
+
+%\subsection{What decisions are made during the manual classification?}
+%During manual comment usefulness assessment, we recorded the participants' rationale to verify that the comments are actually technically or little direct contribute to the proposed changes.
+We can summarize that most of reason for \texttt{YES} voting are: the comments 1) contain new information 2) contain constructive suggestions, 3) discuss directly to the proposed changes, and 4) discuss the technical matters.
 For \texttt{NO} voting, we can summarize that the comments 1) are chatting (just communication), 2) talking about matters unrelated to the proposed changes, 3) discuss about process workflow and supporting system (e.g.
 Git and Gerrit).
+
 %During the training process, reasons for the judgment are recorded. Examples of reasons for positive comments include:

### 2014-09-17 sections/approach.tex
Add references and fit page length

@@
 \centering
-\includegraphics[scale=0.34, trim = 50 90 0 30, clip=true]{overview2}
+\includegraphics[scale=0.32, trim = 50 90 0 30, clip=true]{overview2}
 \caption{An overview of classification of comment usefulness using semantic similarity}
@@
 %This means that a comment will receive a score of 0, 1, 2, or 3.
-For statistical purposes, at least 30 useful and 30 useless comments must be collected.
+For statistical purposes, at least 30 useful and 30 useless comments must be collected\cite{Hogg2005}.
 The similarity and dissimilarity metrics are then computed for the training data set.
@@
 %Other likelihood functions could be used depending on precision, recall, or risk goals.
-We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \footnote{\url{http://en.wikipedia.org/w/index.php?title=F1_score&oldid=608940880}},
+We find these thresholds by selecting $s_t,d_t$ values that maximize the F-measure \cite{Prasetyo2012,Gottipati2011}
 which is a performance measure for a binary classification that compromises trade-offs in accuracy of classification (precision) and coverage of classification (recall).
-In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
-Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.
+%In this study, we used the F$_1$-measure, which equally prioritizes precision and recall.
+%Different weighting can be used by different F$_\beta$ measures depending on error tolerance for precision and recall.
 

### 2014-09-17 sections/background.tex
edit stuff a lot
Add references and fit page length

@@
 
-Ultimately our aim is to understand the impact of useful and useless comments on code quality.
+Ultimately, our aim is to understand the impact of useful and useless comments on code quality.
 Specifically, what degree of useful comments are needed to effect positive impact on quality.
@@
 \centering
-\includegraphics[scale=0.4, trim= 100 250 0 0, clip=true]{comment_examples}
+\includegraphics[scale=0.33, trim= 100 250 0 0, clip=true]{comment_examples}
 \caption{Examples of comment in code reviews of Qt project.}

### 2014-09-17 sections/introduction.tex
very minor fixes
Add references and fit page length

@@
 Traditionally, code reviews were a highly structured activity, but nowadays, less formal and lightweight code reviews such as Modern Code Review (MCR)\cite{Bacchelli2013a} are commonly used within both industry and OSS projects.
-One reason for this is that with MCR, unlike formal inspections \cite{Fagan:1976:DCI:1661010.1661012}, in-person meetings are not required.
+One reason for this is that with MCR, unlike formal inspections \cite{Beller}, in-person meetings are not required.
 Reviewers can find problems in proposed changes and hold discussions on them by adding comments through a code review tool or a mailing list.
@@
 %This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
-This is a concern because a low-degree of useful comments may degrade the overall effectiveness and perceived utility of MCR.
+This is a concern because a low-degree of useful comments may degrade the overall effectiveness \cite{Prasetyo2012,Gottipati2011} and perceived utility of MCR.
 
@@
 One reason for this may be that to assess the impact of discussion in MCR, an effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
-So while the data may be easy to access, MCR can produce a massive amounts of change requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
+So while the data may be easy to access, MCR can produce a massive amounts of change requests and comments\cite{Thongtanunam2014} and it is painstaking and time consuming to manually assess their usefulness.
 Moreover, given that comments in MCR are unstructured natural text, open to subjective judgment, contain tacit understanding, and possible misinterpretation, assessment errors are inevitable.
@@
 \centering
-\includegraphics[scale=0.35, trim= 100 110 50 80, clip=true]{review_process}
-\caption{An simplified version of MCR Process based on Gerrit system}
+\includegraphics[scale=0.28, trim= 100 110 50 80, clip=true]{review_process}
+\caption{A simplified version of MCR Process based on Gerrit system}
 \label{fig:process}
